### 2019-02-01 cse517/proposal/main.tex
Checking in paper stuff and updated gitignore to master. (#2)
* paper writing

* Starting 517 proposal.

* Woops we don't want all of it...

* Checking in files we care about and new gitignore.

%
% File acl2018.tex
%
%% Based on the style files for ACL-2017, with some changes, which were, in turn,
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2018}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{CSE 517: Project Proposal}

\author{
  Deric Pang \quad
  Joshua Bean \\
  Paul G. Allen School of Computer Science \& Engineering \\
  University of Washington \\
  Seattle, WA, USA \\
  {\tt \{dericp, jbean96\}@cs.washington.edu} \\
}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  Abstract.
\end{abstract}

\section{Introduction}

We propose improving natural language inference models by incorporating
syntactic or contextual features into existing models. At its time of
publication, the well-known decomposable attention neural network by
\citet{parikh2016decomposable} obtained state of the art results on the
SNLI dataset (Bowman et al.
2015) while using drastically fewer parameters than previous NLI models. We
want to extend this model and evaluate it on SNLI (Bowman et al. 2015), SNLI
hard (Gururangan et al. 2018), MultiNLI (Williams et al. 2017), MultiNLI hard
(Gururangan et al. 2018), and possibly even domain specific datasets like
Scitail (Khot et al. 2018).

\bibliographystyle{acl_natbib}
\bibliography{main}

\end{document}

### 2019-02-01 paper/main.tex
Checking in paper stuff and updated gitignore to master. (#2)
* paper writing

* Starting 517 proposal.

* Woops we don't want all of it...

* Checking in files we care about and new gitignore.

%
% File acl2018.tex
%
%% Based on the style files for ACL-2017, with some changes, which were, in turn,
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2018}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Title}

\author{
  Deric Pang \quad
  Lucy Lin \quad
  Noah A. Smith \\
  Paul G. Allen of Computer Science \& Engineering \\
  University of Washington \\
  Seattle, WA, USA \\
  {\tt \{dericp, lucylin, nasmith\}@cs.washington.edu} \\
}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of ACL 2018. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions for earlier ACL
and NAACL proceedings, including those for ACL 2017 by Dan Gildea and
Min-Yen Kan, NAACL 2017 by Margaret Mitchell, ACL 2012 by Maggie Li
and Michael White, those from ACL 2010 by Jing-Shing Chang and Philipp
Koehn, those for ACL 2008 by Johanna D. Moore, Simone Teufel, James
Allan, and Sadaoki Furui, those for ACL 2005 by Hwee Tou Ng and Kemal
Oflazer, those for ACL 2002 by Eugene Charniak and Dekang Lin, and
earlier ACL and EACL formats. Those versions were written by several
people, including John Chen, Henry S. Thompson and Donald
Walker. Additional elements were taken from the formatting
instructions of the {\em International Joint Conference on Artificial
  Intelligence} and the \emph{Conference on Computer Vision and
  Pattern Recognition}.

\section{Introduction}

The following instructions are directed to authors of papers submitted
to ACL 2018 or accepted for publication in its proceedings. All
authors are required to adhere to these specifications. Authors are
required to provide a Portable Document Format (PDF) version of their
papers. \textbf{The proceedings are designed for printing on A4
paper.}

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, authors' names and complete
addresses, which must be centered at the top of the first page, and
any full-width figures or tables (see the guidelines in
Subsection~\ref{ssec:first}). \textbf{Type single-spaced.}  Start all
pages directly under the top margin. See the guidelines later
regarding formatting the first page.  The manuscript should be
printed single-sided and its length
should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages are numbered for  initial submission. However, \textbf{do not number the pages in the camera-ready version}.

By uncommenting {\verb|\aclfinalcopy|} at the top of this 
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.  When you first create your submission on softconf, please fill in your submitted paper ID where {\verb|***|} appears in the {\verb|\def\aclpaperid{***}|} definition at the top.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.  The ACL 2018 \LaTeX\ style will create a titlebox space of 6.35 cm for you when {\verb|\aclfinalcopy|} is commented out.

\subsection{The Ruler}
The ACL 2018 style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document without the provided
style files, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\verb|\aclfinalcopy|} command in the document preamble.)

\textbf{Reviewers}: note that the ruler measurements do not align well with
lines in the paper -- this turns out to be very difficult to do well
when the paper contains many figures and equations, and, when done,
looks ugly. In most cases one would expect that the approximate
location will be adequate, although you can also use fractional
references ({\em e.g.}, the first paragraph on this page ends at mark $117.5$).

\subsection{Electronically-available resources}

ACL provides this description in \LaTeX2e{} ({\small\tt acl2018.tex}) and PDF
format ({\small\tt acl2018.pdf}), along with the \LaTeX2e{} style file used to
format it ({\small\tt acl2018.sty}) and an ACL bibliography style ({\small\tt acl\_natbib.bst})
and example bibliography ({\small\tt acl2018.bib}).
These files are all available at
\url{http://acl2018.org/downloads/acl18-latex.zip}.

A Microsoft Word template file ({\small\tt acl18-word.docx}) and example submission pdf ({\small\tt acl18-word.pdf})
is available at
\url{http://acl2018.org/downloads/acl18-word.zip}.
We strongly recommend the use of these style files, which have been
appropriately tailored for the ACL 2018 proceedings.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). PDF files are usually produced from
\LaTeX\ using the \textit{pdflatex} command. If your version of
\LaTeX\ produces Postscript files, you can convert these into PDF
using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
Adobe Distiller to generate PDF.

Please make sure that your PDF file includes all the necessary fonts
(especially tree diagrams, symbols, and fonts with Asian
characters). When you print or create the PDF file, there is usually
an option in your printer setup to include none, all or just
non-standard fonts.  Please make sure that you select the option of
including ALL the fonts. \textbf{Before sending it, test your PDF by
  printing it from a computer different from the one where it was
  created.} Moreover, some word processors may generate very large PDF
files, where each page is rendered as an image. Such images may
reproduce poorly. In this case, try alternative ways to obtain the
PDF. One way on some systems is to install a driver for a postscript
printer, send your document to the printer specifying ``Output to a
file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm
x 29.7 cm) when formatting the paper. When working with
{\tt dvips}, for instance, one should specify {\tt -t a4}.
Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
preamble (directly below the \verb|\usepackage| commands). Then using 
{\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version. If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on A4
paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
 If you cannot meet the above requirements about the production of 
 your electronic submission, please contact the publication chairs 
 above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's \textbf{Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use \textbf{Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[t!]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
subsection titles & 11 pt & bold \\
document text & 11 pt  &\\
captions & 11 pt & \\
abstract text & 11 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author name(s), and affiliation(s) across both
columns (or, for the initial submission, \textbf{Anonymous ACL submission} for names and affiliations). Do not use footnotes for affiliations. 
Include the paper ID number assigned during the submission process in the header. 
Use the two-column format only when you begin the abstract.

\textbf{Title}: Place the title centered at the top of the first page, in
a 15-point bold font. (For a complete guide to font sizes and styles,
see Table~\ref{font-table}) Long titles should be typed on two lines
without a blank line intervening. Approximately, put the title at 2.5
cm from the top of the page, followed by a blank line, then the
author name(s), and the affiliation(s) on the following line. Do not
use only initials for given names (middle initials are allowed). Do
not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
``MITCHELL'').  Do not format title and section headings in all
capitals as well except for proper names (such as ``BLEU'') that are
conventionally in all capitals.  The affiliation should contain the
author's complete address, and if possible, an electronic mail
address. Start the body of the first page 7.5 cm from the top of the
page.

The title, author names and addresses should be completely identical
to those entered to the electronic paper submission website in order
to maintain the consistency of author information among all
publications of the conference. If they are different, the publication
chairs may resolve the difference without consulting with you; so it
is in your own interest to double-check that the information is
consistent.

\textbf{Abstract}: Type the abstract at the beginning of the first
column. The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.6 cm on each side. Center the word \textbf{Abstract} above the body of the abstract using the font size and style shown in Table~\ref{font-table}. The abstract should be a concise
summary of the general thesis and conclusions of the paper. It should
be no longer than 200 words. The font size of the abstract text should be as shown in Table~\ref{font-table}.

\textbf{Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in 
the present document. 
Do not include page numbers in the final version.

\textbf{Indent}: Indent when starting a new paragraph, about 0.4 cm.

%Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.

\begin{table}
\centering
\small
\begin{tabular}{cc}
\begin{tabular}{|l|l|}
\hline
\textbf{Command} & \textbf{Output}\\\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular} & 
\begin{tabular}{|l|l|}
\hline
\textbf{Command} & \textbf{ Output}\\\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\\hline
\end{tabular}
\end{tabular}
\caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\subsection{Sections}

\textbf{Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot, in Arabic numerals. 
Do not number subsubsections ({\em i.e.}, use \verb|\subsubsection*| instead of \verb|\subsubsection|).

\begin{table*}
\centering
\begin{tabular}{lll}
  output & natbib & previous ACL style files\\
  \hline
  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
\end{tabular}
\caption{Citation commands supported by the style file.
  The citation style is based on the natbib package and
  supports all natbib citation commands.
  It also supports commands defined in previous ACL style files
  for compatibility.
  }
\end{table*}

\textbf{Citations}: Citations within the text appear in parentheses
as~\cite{Gusfield:97} or, if the author's name appears in the text
itself, as Gusfield~\shortcite{Gusfield:97}.
Using the provided \LaTeX\ style, the former is accomplished using
{\verb|\cite|} and the latter with {\verb|\shortcite|} or {\verb|\newcite|}.
Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\verb|\cite|} command, {\em e.g.}, {\verb|\cite{Gusfield:97,Aho:72}|}.  
Append lowercase letters to the year in cases of ambiguities.  
 Treat double authors as
in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
authors are involved. 
%Collapse multiple citations as
%in~\cite{Gusfield:97,Aho:72}.

Also refrain from using full citations
as sentence constituents.
%\penalty -5000
We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\citet| (cite in text)
to get ``author (year)'' citations.

You can use the command \verb|\citealp| (alternative cite without 
parentheses) to get ``author year'' citations (which is useful for 
using citations within parentheses, as in \citealp{Gusfield:97}).

If the Bib\TeX{} file contains DOI fields, the paper
title in the references section will appear as a hyperlink
to the DOI, using the hyperref \LaTeX{} package.
To disable the hyperref package, load the style file
with the \verb|nohyperref| option:
\verb|\usepackage[nohyperref]{acl2018}|.

\textbf{Compilation Issues}: Some of you might encounter the following error during compilation:

``{\em \verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.}''

This happens when \verb|pdflatex| is used and a citation splits across a page boundary. To fix this, disable the \verb|hyperref| package (see above), recompile and see the problematic citation.
Next rewrite that sentence containing the citation. (See, {\em e.g.}, {\small\tt http://tug.org/errors.html})

\textbf{Digital Object Identifiers}:  As part of our work to make ACL
materials more widely used and cited outside of our discipline, ACL
has registered as a CrossRef member, as a registrant of Digital Object
Identifiers (DOIs), the standard for registering permanent URNs for
referencing scholarly materials. We are requiring all
camera-ready references to contain the appropriate DOIs (or as a
second resort, the hyperlinked ACL Anthology Identifier) to all cited
works.  Thus, please ensure that you use Bib\TeX\ records that contain
DOI or URLs for any of the ACL materials that you reference.
Appropriate records should be found for most materials in the current
ACL Anthology at \url{http://aclanthology.info/}.

As examples, we cite \cite{P16-1001} to show you how papers with a DOI
will appear in the bibliography.  We cite \cite{C14-1001} to show how
papers without a DOI but with an ACL Anthology Identifier will appear
in the bibliography.

As reviewing will be double-blind, the submitted version of the papers
should not include the authors' names and affiliations. Furthermore,
self-references that reveal the author's identity, {\em e.g.},
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''  
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

\textbf{Please do not use anonymous citations} and do not include
acknowledgments when submitting your papers. Papers that do not
conform to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading \textbf{References}. 
Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the 
{\em Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}.  Use of full names for
authors rather than initials is preferred.
A list of abbreviations for common computer science journals can be found in the ACM {\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations, 
short citations and multiple citations as described above.

\subsection{Footnotes}

\textbf{Footnotes}: Put footnotes at the bottom of the page and use the footnote font size shown in Table~\ref{font-table}. They may be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the line
separating the footnotes from the text.}

\subsection{Figures and Tables}

%\textbf{Placement}: Place figures and tables in the
%paper near where they are first discussed if
%possible.  
%Wide figures and tables may run across both columns and should be placed at the top of a page.

\textbf{Placement}: Place figures and tables in the paper near where they are first discussed, as close as possible to the top of their respective column.

%Color illustrations are discouraged, unless you have verified that  
%they will be understandable when printed in black ink.

\textbf{Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1: Caption of the Figure.'' ``Table 1:
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using the caption font size shown in Table~\ref{font-table}.

\subsection{Equation}
\label{ssec:eqn}

An example equation is shown below:
\begin{equation}
A=\pi r^2
\end{equation}

The numbering (if any) and alignment of the equations will be done automatically (using \verb|align| or \verb|equation|).

\subsection{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate the color-blind (as well as those printing
to paper), grayscale readability for all accepted papers will be
encouraged.  Color is not forbidden, but authors should ensure that
tables and figures do not rely solely on color to convey critical
distinctions.
A simple criterion: All curves and points in your figures should be clearly distinguishable without color.
%Here we give a simple criterion on your colored figures, if your paper has to be printed in black and white, then you must assure that every curves or points in your figures can be still clearly distinguished.

% Min: no longer used as of ACL 2017, following ACL exec's decision to
% remove this extra workflow that was not executed much.
% BEGIN: remove
%% \section{XML conversion and supported \LaTeX\ packages}

%% Following ACL 2014 we will also we will attempt to automatically convert 
%% your \LaTeX\ source files to publish papers in machine-readable 
%% XML with semantic markup in the ACL Anthology, in addition to the 
%% traditional PDF format.  This will allow us to create, over the next 
%% few years, a growing corpus of scientific text for our own future research, 
%% and picks up on recent initiatives on converting ACL papers from earlier 
%% years to XML.

%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
%% with the camera-ready version of your paper. We will then convert them
%% to XML automatically, using the LaTeXML tool
%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
%% a number of \LaTeX\ packages, including the ACL 2017 stylefile. These
%% bindings allow LaTeXML to render the commands from these packages
%% correctly in XML. For best results, we encourage you to use the
%% packages that are officially supported by LaTeXML, listed at
%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
% END: remove

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

The ACL 2018 main conference accepts submissions of long papers and
short papers.
 Long papers may consist of up to eight (8) pages of
content plus unlimited pages for references. Upon acceptance, final
versions of long papers will be given one additional page -- up to nine (9)
pages of content plus unlimited pages for references -- so that reviewers' comments
can be taken into account. Short papers may consist of up to four (4)
pages of content, plus unlimited pages for references. Upon
acceptance, short papers will be given five (5) pages in the
proceedings and unlimited pages for references.

For both long and short papers, all illustrations and tables that are part
of the main text must be accommodated within these page limits, observing
the formatting instructions given in the present document. 
Papers that do not conform to the specified length and 
formatting requirements are subject to be rejected without
review.

Workshop chairs may have different rules for allowed length and
whether supplementary material is welcome. As always, the respective
call for papers is the authoritative source.

\section{Supplementary Material}
\label{sec:supplemental}
ACL 2018 also encourages the submission of supplementary material
to report preprocessing decisions, model parameters, and other details
necessary for the replication of the experiments reported in the 
paper. Seemingly small preprocessing decisions can sometimes make
a large difference in performance, so it is crucial to record such
decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather
than central) to the paper. \textbf{Submissions that misuse the supplementary 
material may be rejected without review.}
Essentially, supplementary material may include explanations or details
of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system,
pseudo-code or source code, and data.

The paper should not rely on the supplementary material: while the paper
may refer to and cite the supplementary material and the supplementary material will be available to the
reviewers, they will not be asked to review the
supplementary material.

The supplementary material does not form part of the paper, does not count towards the page limit, and should not be included in an ``Appendix'' section following the references in this template. The ``container'' for supplementary materials is a separate document, and such materials should be submitted separately from the paper using the appropriate fields on the review form and the camera-ready upload form.

\section*{Acknowledgments}

The acknowledgments should go immediately before the references.  Do not number the acknowledgments section ({\em i.e.}, use \verb|\section*| instead of \verb|\section|). Do not include this section when submitting your paper for review.

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2018}
\bibliography{acl2018}
\bibliographystyle{acl_natbib}

\end{document}

### 2019-02-01 cse517/proposal/main.tex
First draft of project proposal.

@@
 \usepackage{latexsym}
-
 \usepackage{url}
+\usepackage{graphicx}
+\usepackage{booktabs}
 
@@
 
-We propose improving natural language inference models by incorporating
-syntactic or contextual features into existing models. At its time of
-publication, the well-known decomposable attention neural network by
-\citet{parikh2016decomposable} obtained state of the art results on the
-SNLI dataset (Bowman et al.
-2015) while using drastically fewer parameters than previous NLI models. We
-want to extend this model and evaluate it on SNLI (Bowman et al. 2015), SNLI
-hard (Gururangan et al. 2018), MultiNLI (Williams et al. 2017), MultiNLI hard
-(Gururangan et al. 2018), and possibly even domain specific datasets like
-Scitail (Khot et al. 2018).
+Natural language inference (NLI) is the task of characterizing entailment and
+contradiction relationships between texts.
+We seek to improve NLI models by adding syntactic
+features into existing models. The well-known decomposable attention (DA)
+neural network \citep{Parikh2016-em} obtained state of the art results on the
+SNLI \citep{Bowman2015-is} dataset at its time of publication while using
+drastically fewer parameters than previous NLI models.
+
+We intend to extend this
+model and evaluate it on SNLI, MultiNLI \citep{Williams2017-uh}, the SNLI and
+MultiNLI hard splits \citep{Gururangan2018-lj}, and smaller domain specific
+datasets like Scitail \citep{Khot2018-th}.
+
+\section{Previous Work}
+
+Our project will build on previous work done by \citet{Pang2018-syntail}.
+
+In previous work, we created the syntail-v1 model whose architecture is
+shown in figure \ref{figure:v1}.
+We have obtained mixed results as shown in table \ref{table:v1-accuracies} when
+naively incorporating syntactic information
+into the DA model.
+
+Wihthout ELMo, syntail-v1 improves an impressive 8.4\% in test accuracy over
+the baseline decomposable attention model on the SciTail dataset. However,
+once ELMo is added to the model, almost the exact happens. Adding syntactic
+information decreases test accuracy by 6.7\%.
+
+\begin{table}[h]
+  \resizebox{0.45\textwidth}{!}{
+  \begin{tabular}{c c c c}
+    \toprule
+    Model & Embedding & Train Acc. & Test Acc. \\
+    \midrule
+    DA & GLoVe 6b 300d & 89.4\% & 70.1\% \\
+    \textbf{Syntail-v1} & \textbf{GLoVe 6b 300d} & \textbf{92.1\%} & \textbf{78.5\%} \\
+    \textbf{DA} & \textbf{ELMo} & \textbf{98.4\%} & \textbf{78.0\%} \\
+    Syntail-v1 & ELMo & 88.8\% & 71.3\% \\
+    \bottomrule
+  \end{tabular}}
+  \caption{Syntail-v1 and DA model accuracies on the SciTail dataset.}
+\label{table:v1-accuracies}
+\end{table}
+
+\section{Proposed Methods}
+\label{methods}
+
+We plan to use state-of-the-art constituency \citep{Stern2017-co} and
+dependency \citep{Dozat2016-gs} parsers to investigate if incorporating
+syntactic features improves the performance of the decomposable attention
+network. Additionally, we hope to understand how syntactic features interact
+with contextual
+word embeddings like ELMo \citep{Peters2018-fz} and BERT \citep{Devlin2018-qc}
+in a task like NLI.
+
+We will first investigate different ways of incorporating syntactic
+information. \citet{Pang2018-syntail} use a constituency parser to obtain an
+encoding of the premise and hypothesis that is used when characterizing their
+relationship. We believe that incorporating syntactic features earlier in the
+pipeline, especially before the premise and hypothesis are attended over one
+another, should improve performance.
+
+We will then investigate different model architectures under a multi-task
+training objective where the jointly learns to both parse and predict
+entailment relationships.
+
+\begin{figure}[h]
+  \includegraphics[width=0.45\textwidth]{v1}
+  \caption{A simple method of incorporating syntax into the decomposable
+    attention model.}
+\label{figure:v1}
+\end{figure}
+
+\section{Expected Outcomes}
+
+We will compare our models to the DA model as well as syntail-v1. We hope to
+evaluate our models on many diverse datasets as stated in section
+~\ref{methods}.
+
+We expect that one of our modeling ideas will produce results that improve on
+the DA and syntail-v1 models. In the best case, we will show that syntax is
+crucial to building an accurate NLI system.
+
+\section{Challenges}
+
+The first challenge involved in our project will be to modify syntail-v1
+so that syntactic information is incorporated much earlier. It will also take
+significant time to investigate the best parsers to use for our model.
+After, we will write a new model under a multi-task training setup, which we
+anticipate will be a significant implementation challenge.
+
+We expect to require significant compute power and time to adequately fine-tune
+and evaluate our models. Contextual word embeddings are especially costly to
+train, and the mixing ratio in a multi-task setup is well-known to be
+difficult to tune.
 

### 2019-02-05 scripts/train-se.sh
Merging v3 (#3)
* Removing commented out import.

* Removing previous model needs to be off by default.

* Fixing config of SE with elmo.

* Training constituency parser separately available now.

@@ -16,6 +16,6 @@ DATASET="$1"
 SERIALIZATION_DIR="./models/se-$DATASET$ELMO"
 CONFIG="config/se-$DATASET$ELMO.jsonnet"
 
-rm -rf "$SERIALIZATION_DIR"
+#rm -rf "$SERIALIZATION_DIR"
 echo "Training $CONFIG. Saving model to $SERIALIZATION_DIR."
 allennlp train "$CONFIG" --serialization-dir "$SERIALIZATION_DIR" --include-package syntactic_entailment

### 2019-02-05 syntactic_entailment/models/syntactic_entailment.py

@@ -8,7 +8,6 @@ from allennlp.data import Vocabulary
 from allennlp.models.model import Model
 from allennlp.modules import FeedForward
 from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
-#from allennlp.modules.matrix_attention.legacy_matrix_attention import LegacyMatrixAttention
 from allennlp.nn import InitializerApplicator, RegularizerApplicator
 from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
 from allennlp.training.metrics import CategoricalAccuracy

### 2019-02-05 syntactic_entailment/models/constituency_parser.py
Merging v3 (#3)
* Removing commented out import.

* Removing previous model needs to be off by default.

* Fixing config of SE with elmo.

* Training constituency parser separately available now.

@@ -115,7 +115,6 @@ class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
         span_labels : ``torch.LongTensor``, optional (default = None)
             A torch tensor representing the integer gold class labels for all possible
             spans, of shape ``(batch_size, num_spans)``.
-
         Returns
         -------
         An output dictionary consisting of:
@@ -155,15 +154,39 @@ class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
         num_spans = get_lengths_from_binary_sequence_mask(span_mask)
 
         encoded_text = self.encoder(embedded_text_input, mask)
-        #encoder_final_state = get_final_encoder_states(encoded_text, mask)
 
-        #output_dict = {
-        #        "encoder_final_state": encoder_final_state
-        #}
+        span_representations = self.span_extractor(encoded_text, spans, mask, span_mask)
+
+        if self.feedforward_layer is not None:
+            span_representations = self.feedforward_layer(span_representations)
+
+        logits = self.tag_projection_layer(span_representations)
+        class_probabilities = masked_softmax(logits, span_mask.unsqueeze(-1))
 
         output_dict = {
-                "encoded_text": encoded_text
+                "class_probabilities": class_probabilities,
+                "spans": spans,
+                "tokens": [meta["tokens"] for meta in metadata],
+                "pos_tags": [meta.get("pos_tags") for meta in metadata],
+                "num_spans": num_spans
         }
+        if span_labels is not None:
+            loss = sequence_cross_entropy_with_logits(logits, span_labels, span_mask)
+            self.tag_accuracy(class_probabilities, span_labels, span_mask)
+            output_dict["loss"] = loss
+
+        # The evalb score is expensive to compute, so we only compute
+        # it for the validation and test sets.
+        batch_gold_trees = [meta.get("gold_tree") for meta in metadata]
+        if all(batch_gold_trees) and self._evalb_score is not None and not self.training:
+            gold_pos_tags: List[List[str]] = [list(zip(*tree.pos()))[1]
+                                              for tree in batch_gold_trees]
+            predicted_trees = self.construct_trees(class_probabilities.cpu().data,
+                                                   spans.cpu().data,
+                                                   num_spans.data,
+                                                   output_dict["tokens"],
+                                                   gold_pos_tags)
+            self._evalb_score(predicted_trees, batch_gold_trees)
 
[…]

### 2019-02-05 syntactic_entailment/models/syntactic_entailment.py
Starting to train the constituency parser separately.

@@ -98,7 +98,7 @@ class SyntacticEntailment(Model):
         self._loss = torch.nn.CrossEntropyLoss()
 
         self._predictor = Predictor.from_path(
-                "models/elmo-constituency-parser/model.tgz",
+                "models/se-constituency_parser-nelson-data/model.tar.gz",
                 predictor_name="syntactic-entailment-constituency-parser")
 
         self._device = torch.device("cuda:0" if torch.cuda.is_available()

### 2019-02-05 syntactic_entailment/models/constituency_parser.py
Putting back encoded text output that I accidentally took out.

@@ -164,6 +164,7 @@ class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
         class_probabilities = masked_softmax(logits, span_mask.unsqueeze(-1))
 
         output_dict = {
+                "encoded_text": encoded_text,
                 "class_probabilities": class_probabilities,
                 "spans": spans,
                 "tokens": [meta["tokens"] for meta in metadata],

### 2019-02-06 syntactic_entailment/models/syntactic_entailment.py
Constituency parser file now specified in config.

@@ -69,6 +69,8 @@ class SyntacticEntailment(Model):
                  similarity_function: SimilarityFunction,
                  compare_feedforward: FeedForward,
                  aggregate_feedforward: FeedForward,
+                 parser_model_path: str,
+                 predictor_name: str,
                  premise_encoder: Optional[Seq2SeqEncoder] = None,
                  hypothesis_encoder: Optional[Seq2SeqEncoder] = None,
                  initializer: InitializerApplicator = InitializerApplicator(),
@@ -97,9 +99,8 @@ class SyntacticEntailment(Model):
         self._accuracy = CategoricalAccuracy()
         self._loss = torch.nn.CrossEntropyLoss()
 
-        self._predictor = Predictor.from_path(
-                "models/se-constituency_parser-nelson-data/model.tar.gz",
-                predictor_name="syntactic-entailment-constituency-parser")
+        self._predictor = Predictor.from_path(parser_model_path,
+                predictor_name=predictor_name)
 
         self._device = torch.device("cuda:0" if torch.cuda.is_available()
                                              else "cpu")

### 2019-02-08 paper/main.tex
Moving proposal content to paper.

@@
 %
-% File acl2018.tex
+% File emnlp2018.tex
 %
-%% Based on the style files for ACL-2017, with some changes, which were, in turn,
+%% Based on the style files for EMNLP 2018, which were
+%% Based on the style files for ACL 2018, which were
 %% Based on the style files for ACL-2015, with some improvements
@@
 \documentclass[11pt,a4paper]{article}
-\usepackage[hyperref]{acl2018}
+\usepackage[hyperref]{emnlp2018}
 \usepackage{times}
@@
 
-%\aclfinalcopy % Uncomment this line for the final submission
-%\def\aclpaperid{***} %  Enter the acl Paper ID here
+% user packages
+\usepackage{graphicx}
+\graphicspath{{figures/}}
+\usepackage{booktabs}
+
+\aclfinalcopy % Uncomment this line for the final submission
 
@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+\newcommand\confname{EMNLP 2018}
+\newcommand\conforg{SIGDAT}
 
-\title{Title}
+\title{Instructions for \confname{} Proceedings}
 
-\author{
-  Deric Pang \quad
-  Lucy Lin \quad
-  Noah A. Smith \\
-  Paul G. Allen of Computer Science \& Engineering \\
-  University of Washington \\
-  Seattle, WA, USA \\
-  {\tt \{dericp, lucylin, nasmith\}@cs.washington.edu} \\
-}
+\author{First Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\\And
+  Second Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\}
 
@@
 \begin{abstract}
-  This document contains the instructions for preparing a camera-ready
-  manuscript for the proceedings of ACL 2018. The document itself
-  conforms to its own specifications, and is therefore an example of
-  what your manuscript should look like. These instructions should be
-  used for both papers submitted for review and for final versions of
-  accepted papers.  Authors are asked to conform to all the directions
-  reported in this document.
+  Abstract.
 \end{abstract}
+
+\section{Introduction}
+
+Natural language inference (NLI) is the task of characterizing entailment and
+contradiction relationships between texts.  We seek to improve models which
+perform NLI by adding syntactic features into existing models. In particular,
+we will primarily investigate the well-known decomposable attention (DA) neural
+network \citep{Parikh2016-em} which obtained state of the art results on the
+SNLI \citep{Bowman2015-is} dataset at its time of publication while using
+drastically fewer parameters than previous NLI models.
+
+We intend to extend the DA model and evaluate new models on SNLI, MultiNLI
+\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
+\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
+\citep{Khot2018-th}.
+
+In general, most NLI tasks are formulated as characterizing the relationship
+between a pair of sequences---a premise and a hypothesis. An NLI model should
+predict whether the hyothesis is entailed by the premise, contradicts the
+premise, or is neutral to the premise.
+
+\section{Previous Work}
+
+Our project will build on previous work done by \citet{Pang2018-syntail}.
+
+In previous work, we created the syntail-v1 model whose architecture is shown
+in figure~\ref{figure:v1}.  We have obtained mixed results as shown in
+table~\ref{table:v1-accuracies} when naively incorporating syntactic
+information into the DA model.
+
+Without ELMo, syntail-v1 improves an impressive 8.4\% in test accuracy over the
+baseline decomposable attention model on the SciTail dataset. However, once
+ELMo is added to the model, almost the exact opposite occurs. Adding syntactic
+information decreases test accuracy by 6.7\% with ELMo.
+
+\begin{table}[h]
+  \resizebox{0.45\textwidth}{!}{
+  \begin{tabular}{c c c c}
+    \toprule
+    Model & Embedding & Train Acc. & Test Acc. \\
+    \midrule
+    DA & GLoVe 6b 300d & 89.4\% & 70.1\% \\
+    \textbf{Syntail-v1} & \textbf{GLoVe 6b 300d} & \textbf{92.1\%}
+                        & \textbf{78.5\%} \\
+    DA & ELMo & 98.4\% & 78.0\% \\
+    \textbf{Syntail-v1} & \textbf{ELMo} & \textbf{88.8\%} & \textbf{71.3\%} \\
+    \bottomrule
+  \end{tabular}}
+  \caption{Syntail-v1 and DA model accuracies on the SciTail dataset.}
+\label{table:v1-accuracies}
+\end{table}
+
+\section{Proposed Methods}
+\label{methods}
+
+We plan to use state-of-the-art constituency \citep{Stern2017-co} and
+dependency \citep{Dozat2016-gs} parsers to investigate if incorporating
+syntactic features improves the performance of the DA model. Additionally, we
+hope to understand how syntactic features interact with contextual word
+embeddings like ELMo \citep{Peters2018-fz} and BERT \citep{Devlin2018-qc} in a
+task like NLI. It is unclear from previous work whether contextual word
+embeddings benefit from additional syntactic information or if something like
+ELMo can already adequately capture this information.
+
+We will first investigate different ways of incorporating syntactic
+information. \citet{Pang2018-syntail} use a constituency parser to obtain an
+encoding of the premise and hypothesis that is in the final fully-connected
+layer of the DA model. We believe that incorporating syntactic features earlier
+in the pipeline, especially before the premise and hypothesis are attended over
+one another, should improve performance.
+
+We will then investigate different model architectures under a multi-task
+training objective where the jointly learns to both parse and predict
+entailment relationships.
+
+\begin{figure}[h]
+  \includegraphics[width=0.45\textwidth]{v1}
+  \caption{A simple method of incorporating syntax into the decomposable
+    attention model.}
+\label{figure:v1}
+\end{figure}
+
+\section{Expected Outcomes}
+
+We will compare our models to the DA model as well as syntail-v1. We hope to
+evaluate our models on many diverse datasets as stated in section
+~\ref{methods}.
+
+We expect that one of our modeling ideas will produce results that improve on
+the DA and syntail-v1 models. In the best case, we will show that syntax is
+crucial to building an accurate NLI system.
+
+\section{Challenges}
+
+The first challenge involved in our project will be to modify syntail-v1
+so that syntactic information is incorporated much earlier. It will also take
+significant time to investigate the best parsers to use for our model.
+After, we will write a new model under a multi-task training setup, which we
+anticipate will be a significant implementation challenge.
+
+We expect to require significant compute power and time to adequately fine-tune
+and evaluate our models. Contextual word embeddings are especially costly to
+train, and the mixing ratio in a multi-task setup is well-known to be
+difficult to tune.
 
@@
 
-This document has been adapted from the instructions for earlier ACL
-and NAACL proceedings, including those for ACL 2017 by Dan Gildea and
-Min-Yen Kan, NAACL 2017 by Margaret Mitchell, ACL 2012 by Maggie Li
-and Michael White, those from ACL 2010 by Jing-Shing Chang and Philipp
-Koehn, those for ACL 2008 by Johanna D. Moore, Simone Teufel, James
-Allan, and Sadaoki Furui, those for ACL 2005 by Hwee Tou Ng and Kemal
-Oflazer, those for ACL 2002 by Eugene Charniak and Dekang Lin, and
-earlier ACL and EACL formats. Those versions were written by several
-people, including John Chen, Henry S. Thompson and Donald
-Walker. Additional elements were taken from the formatting
-instructions of the {\em International Joint Conference on Artificial
-  Intelligence} and the \emph{Conference on Computer Vision and
-  Pattern Recognition}.
-
-\section{Introduction}
-
-The following instructions are directed to authors of papers submitted
-to ACL 2018 or accepted for publication in its proceedings. All
-authors are required to adhere to these specifications. Authors are
-required to provide a Portable Document Format (PDF) version of their
-papers. \textbf{The proceedings are designed for printing on A4
-paper.}
-
-\section{General Instructions}
-
-Manuscripts must be in two-column format.  Exceptions to the
-two-column format include the title, authors' names and complete
-addresses, which must be centered at the top of the first page, and
-any full-width figures or tables (see the guidelines in
-Subsection~\ref{ssec:first}). \textbf{Type single-spaced.}  Start all
-pages directly under the top margin. See the guidelines later
-regarding formatting the first page.  The manuscript should be
-printed single-sided and its length
-should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Pages are numbered for  initial submission. However, \textbf{do not number the pages in the camera-ready version}.
-
-By uncommenting {\verb|\aclfinalcopy|} at the top of this 
- document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.
-When you first create your submission on softconf, please fill in your submitted paper ID where {\verb|***|} appears in the {\verb|\def\aclpaperid{***}|} definition at the top.
-
-The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
-However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.
-The ACL 2018 \LaTeX\ style will create a titlebox space of 6.35 cm for you when {\verb|\aclfinalcopy|} is commented out.
-
-\subsection{The Ruler}
-The ACL 2018 style defines a printed ruler which should be present in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document without the provided
-style files, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\verb|\aclfinalcopy|} command in the document preamble.)
-
-\textbf{Reviewers}: note that the ruler measurements do not align well with
-lines in the paper -- this turns out to be very difficult to do well
-when the paper contains many figures and equations, and, when done,
-looks ugly. In most cases one would expect that the approximate
-location will be adequate, although you can also use fractional
-references ({\em e.g.}, the first paragraph on this page ends at mark $117.5$).
-
-\subsection{Electronically-available resources}
-
-ACL provides this description in \LaTeX2e{} ({\small\tt acl2018.tex}) and PDF
-format ({\small\tt acl2018.pdf}), along with the \LaTeX2e{} style file used to
-format it ({\small\tt acl2018.sty}) and an ACL bibliography style ({\small\tt acl\_natbib.bst})
-and example bibliography ({\small\tt acl2018.bib}).
-These files are all available at
-\url{http://acl2018.org/downloads/acl18-latex.zip}.
-
-A Microsoft Word template file ({\small\tt acl18-word.docx}) and example submission pdf ({\small\tt acl18-word.pdf})
-is available at
-\url{http://acl2018.org/downloads/acl18-word.zip}.
-We strongly recommend the use of these style files, which have been
-appropriately tailored for the ACL 2018 proceedings.
-
-\subsection{Format of Electronic Manuscript}
-\label{sect:pdf}
-
-For the production of the electronic manuscript you must use Adobe's
-Portable Document Format (PDF). PDF files are usually produced from
-\LaTeX\ using the \textit{pdflatex} command. If your version of
-\LaTeX\ produces Postscript files, you can convert these into PDF
-using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
-Adobe Distiller to generate PDF.
-
-Please make sure that your PDF file includes all the necessary fonts
-(especially tree diagrams, symbols, and fonts with Asian
-characters). When you print or create the PDF file, there is usually
-an option in your printer setup to include none, all or just
-non-standard fonts.  Please make sure that you select the option of
-including ALL the fonts. \textbf{Before sending it, test your PDF by
-  printing it from a computer different from the one where it was
-  created.} Moreover, some word processors may generate very large PDF
-files, where each page is rendered as an image. Such images may
-reproduce poorly. In this case, try alternative ways to obtain the
-PDF. One way on some systems is to install a driver for a postscript
-printer, send your document to the printer specifying ``Output to a
-file'', then convert the file to PDF.
-
-It is of utmost importance to specify the \textbf{A4 format} (21 cm
-x 29.7 cm) when formatting the paper. When working with
-{\tt dvips}, for instance, one should specify {\tt -t a4}.
-Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
-preamble (directly below the \verb|\usepackage| commands). Then using 
-{\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.
-
-Print-outs of the PDF file on A4 paper should be identical to the
-hardcopy version. If you cannot meet the above requirements about the
-production of your electronic submission, please contact the
-publication chairs as soon as possible.
-
-\subsection{Layout}
-\label{ssec:layout}
-
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted. The exact dimensions for a page on A4
-paper are:
-
-\begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
-\end{itemize}
-
-\noindent Papers should not be submitted on any other paper size.
- If you cannot meet the above requirements about the production of 
- your electronic submission, please contact the publication chairs 
- above as soon as possible.
-
-\subsection{Fonts}
-
-For reasons of uniformity, Adobe's \textbf{Times Roman} font should be
-used. In \LaTeX2e{} this is accomplished by putting
-
-\begin{quote}
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
-in the preamble. If Times Roman is unavailable, use \textbf{Computer
-  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
-  10\% less dense than Adobe's Times Roman font.
-
-\begin{table}[t!]
-\begin{center}
-\begin{tabular}{|l|rl|}
-\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-subsection titles & 11 pt & bold \\
-document text & 11 pt  &\\
-captions & 11 pt & \\
-abstract text & 11 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
-\hline
-\end{tabular}
-\end{center}
-\caption{\label{font-table} Font guide. }
-\end{table}
-
-\subsection{The First Page}
-\label{ssec:first}
-
-Center the title, author name(s), and affiliation(s) across both
-columns (or, for the initial submission, \textbf{Anonymous ACL submission} for names and affiliations). Do not use footnotes for affiliations. 
-Include the paper ID number assigned during the submission process in the header. 
-Use the two-column format only when you begin the abstract.
-
-\textbf{Title}: Place the title centered at the top of the first page, in
-a 15-point bold font. (For a complete guide to font sizes and styles,
-see Table~\ref{font-table}) Long titles should be typed on two lines
-without a blank line intervening. Approximately, put the title at 2.5
-cm from the top of the page, followed by a blank line, then the
-author name(s), and the affiliation(s) on the following line. Do not
-use only initials for given names (middle initials are allowed). Do
-not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
-``MITCHELL'').  Do not format title and section headings in all
-capitals as well except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.  The affiliation should contain the
-author's complete address, and if possible, an electronic mail
-address. Start the body of the first page 7.5 cm from the top of the
-page.
-
-The title, author names and addresses should be completely identical
-to those entered to the electronic paper submission website in order
-to maintain the consistency of author information among all
-publications of the conference. If they are different, the publication
-chairs may resolve the difference without consulting with you; so it
-is in your own interest to double-check that the information is
-consistent.
-
-\textbf{Abstract}: Type the abstract at the beginning of the first
-column. The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by about
-0.6 cm on each side. Center the word \textbf{Abstract} above the body of the abstract using the font size and style shown in Table~\ref{font-table}. The abstract should be a concise
-summary of the general thesis and conclusions of the paper. It should
-be no longer than 200 words. The font size of the abstract text should be as shown in Table~\ref{font-table}.
-
-\textbf{Text}: Begin typing the main body of the text immediately after
-the abstract, observing the two-column format as shown in 
-the present document. 
-Do not include page numbers in the final version.
-
-\textbf{Indent}: Indent when starting a new paragraph, about 0.4 cm.
-
-%Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.
-
-\begin{table}
-\centering
-\small
-\begin{tabular}{cc}
-\begin{tabular}{|l|l|}
-\hline
-\textbf{Command} & \textbf{Output}\\\hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\ 
-\verb|{\.I}| & {\.I} \\ 
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\ 
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular} & 
-\begin{tabular}{|l|l|}
-\hline
-\textbf{Command} & \textbf{ Output}\\\hline
-\verb|{\c c}| & {\c c} \\ 
-\verb|{\u g}| & {\u g} \\ 
-\verb|{\l}| & {\l} \\ 
-\verb|{\~n}| & {\~n} \\ 
-\verb|{\H o}| & {\H o} \\ 
-\verb|{\v r}| & {\v r} \\ 
-\verb|{\ss}| & {\ss} \\\hline
-\end{tabular}
-\end{tabular}
-\caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
-\end{table}
-
-\subsection{Sections}
-
-\textbf{Headings}: Type and label section and subsection headings in the
-style shown on the present document.  Use numbered sections (Arabic
-numerals) in order to facilitate cross references. Number subsections
-with the section number and the subsection number separated by a dot, in Arabic numerals. 
-Do not number subsubsections ({\em i.e.}, use \verb|\subsubsection*| instead of \verb|\subsubsection|).
-
-\begin{table*}
-\centering
-\begin{tabular}{lll}
-  output & natbib & previous ACL style files\\
-  \hline
-  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
-  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
-  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
-\end{tabular}
-\caption{Citation commands supported by the style file.
-  The citation style is based on the natbib package and
-  supports all natbib citation commands.
-  It also supports commands defined in previous ACL style files
-  for compatibility.
-  }
-\end{table*}
-
-\textbf{Citations}: Citations within the text appear in parentheses
-as~\cite{Gusfield:97} or, if the author's name appears in the text
-itself, as Gusfield~\shortcite{Gusfield:97}.
-Using the provided \LaTeX\ style, the former is accomplished using
-{\verb|\cite|} and the latter with {\verb|\shortcite|} or {\verb|\newcite|}.
-Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\verb|\cite|} command, {\em e.g.}, {\verb|\cite{Gusfield:97,Aho:72}|}.
-Append lowercase letters to the year in cases of ambiguities.  
- Treat double authors as
-in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
-authors are involved. 
-%Collapse multiple citations as
-%in~\cite{Gusfield:97,Aho:72}.
-
-Also refrain from using full citations
-as sentence constituents.
-%\penalty -5000
-We suggest that instead of
-\begin{quote}
-  ``\cite{Gusfield:97} showed that ...''
-\end{quote}
-you use
-\begin{quote}
-``Gusfield \shortcite{Gusfield:97}   showed that ...''
-\end{quote}
-
-If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
-can use the command \verb|\citet| (cite in text)
-to get ``author (year)'' citations.
-
-You can use the command \verb|\citealp| (alternative cite without 
-parentheses) to get ``author year'' citations (which is useful for 
-using citations within parentheses, as in \citealp{Gusfield:97}).
-
-If the Bib\TeX{} file contains DOI fields, the paper
-title in the references section will appear as a hyperlink
-to the DOI, using the hyperref \LaTeX{} package.
-To disable the hyperref package, load the style file
-with the \verb|nohyperref| option:
-\verb|\usepackage[nohyperref]{acl2018}|.
-
-\textbf{Compilation Issues}: Some of you might encounter the following error during compilation:
-
-``{\em \verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.}''
-
-This happens when \verb|pdflatex| is used and a citation splits across a page boundary. To fix this, disable the \verb|hyperref| package (see above), recompile and see the problematic citation.
-Next rewrite that sentence containing the citation. (See, {\em e.g.}, {\small\tt http://tug.org/errors.html})
-
-\textbf{Digital Object Identifiers}:  As part of our work to make ACL
-materials more widely used and cited outside of our discipline, ACL
-has registered as a CrossRef member, as a registrant of Digital Object
-Identifiers (DOIs), the standard for registering permanent URNs for
-referencing scholarly materials. We are requiring all
-camera-ready references to contain the appropriate DOIs (or as a
-second resort, the hyperlinked ACL Anthology Identifier) to all cited
-works.  Thus, please ensure that you use Bib\TeX\ records that contain
-DOI or URLs for any of the ACL materials that you reference.
-Appropriate records should be found for most materials in the current
-ACL Anthology at \url{http://aclanthology.info/}.
-
-As examples, we cite \cite{P16-1001} to show you how papers with a DOI
-will appear in the bibliography.  We cite \cite{C14-1001} to show how
-papers without a DOI but with an ACL Anthology Identifier will appear
-in the bibliography.
-
-As reviewing will be double-blind, the submitted version of the papers
-should not include the authors' names and affiliations. Furthermore,
-self-references that reveal the author's identity, {\em e.g.},
-\begin{quote}
-``We previously showed \cite{Gusfield:97} ...''  
-\end{quote}
-should be avoided. Instead, use citations such as 
-\begin{quote}
-``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
-previously showed ... ''
-\end{quote}
-
-\textbf{Please do not use anonymous citations} and do not include
-acknowledgments when submitting your papers. Papers that do not
-conform to these requirements may be rejected without review.
-
-\textbf{References}: Gather the full set of references together under
-the heading \textbf{References}. 
-Arrange the references alphabetically
-by first author, rather than by order of occurrence in the text.
-Provide as complete a citation as possible, using a consistent format,
-such as the one for {\em Computational Linguistics\/} or the one in the 
-{\em Publication Manual of the American 
-Psychological Association\/}~\cite{APA:83}.  Use of full names for
-authors rather than initials is preferred.
-A list of abbreviations for common computer science journals can be found in the ACM {\em Computing Reviews\/}~\cite{ACM:83}.
-
-The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
-American Psychological Association format, allowing regular citations, 
-short citations and multiple citations as described above.
-
-\subsection{Footnotes}
-
-\textbf{Footnotes}: Put footnotes at the bottom of the page and use the footnote font size shown in Table~\ref{font-table}. They may be numbered or referred to by asterisks or other
-symbols.\footnote{This is how a footnote should appear.} Footnotes
-should be separated from the text by a line.\footnote{Note the line
-separating the footnotes from the text.}
-
-\subsection{Figures and Tables}
-
-%\textbf{Placement}: Place figures and tables in the
-%paper near where they are first discussed if
-%possible.  
-%Wide figures and tables may run across both columns and should be placed at the top of a page.
-
-\textbf{Placement}: Place figures and tables in the paper near where they are first discussed, as close as possible to the top of their respective column.
-
-%Color illustrations are discouraged, unless you have verified that  
-%they will be understandable when printed in black ink.
-
-\textbf{Captions}: Provide a caption for every illustration; number each one
-sequentially in the form:  ``Figure 1: Caption of the Figure.'' ``Table 1:
-Caption of the Table.''  Type the captions of the figures and 
-tables below the body, using the caption font size shown in Table~\ref{font-table}.
-
-\subsection{Equation}
-\label{ssec:eqn}
-
-An example equation is shown below:
-\begin{equation}
-A=\pi r^2
-\end{equation}
-
-The numbering (if any) and alignment of the equations will be done automatically (using \verb|align| or \verb|equation|).
-
-\subsection{Accessibility}
-\label{ssec:accessibility}
-
-In an effort to accommodate the color-blind (as well as those printing
-to paper), grayscale readability for all accepted papers will be
-encouraged.  Color is not forbidden, but authors should ensure that
-tables and figures do not rely solely on color to convey critical
-distinctions.
-A simple criterion: All curves and points in your figures should be clearly distinguishable without color.
-%Here we give a simple criterion on your colored figures, if your paper has to be printed in black and white, then you must assure that every curves or points in your figures can be still clearly distinguished.
-
-% Min: no longer used as of ACL 2017, following ACL exec's decision to
-% remove this extra workflow that was not executed much.
-% BEGIN: remove
-%% \section{XML conversion and supported \LaTeX\ packages}
-
-%% Following ACL 2014 we will also we will attempt to automatically convert 
-%% your \LaTeX\ source files to publish papers in machine-readable 
-%% XML with semantic markup in the ACL Anthology, in addition to the 
-%% traditional PDF format.  This will allow us to create, over the next 
-%% few years, a growing corpus of scientific text for our own future research, 
-%% and picks up on recent initiatives on converting ACL papers from earlier 
-%% years to XML.
-
-%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
-%% with the camera-ready version of your paper. We will then convert them
-%% to XML automatically, using the LaTeXML tool
-%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
-%% a number of \LaTeX\ packages, including the ACL 2017 stylefile. These
-%% bindings allow LaTeXML to render the commands from these packages
-%% correctly in XML. For best results, we encourage you to use the
-%% packages that are officially supported by LaTeXML, listed at
-%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
-% END: remove
-
-\section{Translation of non-English Terms}
-
-It is also advised to supplement non-English characters and terms
-with appropriate transliterations and/or translations
-since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in
-the order of: original-form transliteration ``translation''.
-
-\section{Length of Submission}
-\label{sec:length}
-
-The ACL 2018 main conference accepts submissions of long papers and
-short papers.
- Long papers may consist of up to eight (8) pages of
-content plus unlimited pages for references. Upon acceptance, final
-versions of long papers will be given one additional page -- up to nine (9)
-pages of content plus unlimited pages for references -- so that reviewers' comments
-can be taken into account. Short papers may consist of up to four (4)
-pages of content, plus unlimited pages for references. Upon
-acceptance, short papers will be given five (5) pages in the
-proceedings and unlimited pages for references.
-
-For both long and short papers, all illustrations and tables that are part
-of the main text must be accommodated within these page limits, observing
-the formatting instructions given in the present document. 
-Papers that do not conform to the specified length and 
-formatting requirements are subject to be rejected without
-review.
-
-Workshop chairs may have different rules for allowed length and
-whether supplementary material is welcome. As always, the respective
-call for papers is the authoritative source.
-
-\section{Supplementary Material}
-\label{sec:supplemental}
-ACL 2018 also encourages the submission of supplementary material
-to report preprocessing decisions, model parameters, and other details
-necessary for the replication of the experiments reported in the 
-paper. Seemingly small preprocessing decisions can sometimes make
-a large difference in performance, so it is crucial to record such
-decisions to precisely characterize state-of-the-art methods.
-
-Nonetheless, supplementary material should be supplementary (rather
-than central) to the paper. \textbf{Submissions that misuse the supplementary 
-material may be rejected without review.}
-Essentially, supplementary material may include explanations or details
-of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system,
-pseudo-code or source code, and data.
-
-The paper should not rely on the supplementary material: while the paper
-may refer to and cite the supplementary material and the supplementary material will be available to the
-reviewers, they will not be asked to review the
-supplementary material.
-
-The supplementary material does not form part of the paper, does not count towards the page limit, and should not be included in an ``Appendix'' section following the references in this template.
-The ``container'' for supplementary materials is a separate document, and such materials should be submitted separately from the paper using the appropriate fields on the review form and the camera-ready upload form.
-
-\section*{Acknowledgments}
-
-The acknowledgments should go immediately before the references.
-Do not number the acknowledgments section ({\em i.e.}, use \verb|\section*| instead of \verb|\section|).
-Do not include this section when submitting your paper for review.
-
-% include your own bib file like this:
-%\bibliographystyle{acl}
-%\bibliography{acl2018}
-\bibliography{acl2018}
-\bibliographystyle{acl_natbib}
+\bibliography{references}
+\bibliographystyle{acl_natbib_nourl}
 

### 2019-02-09 syntactic_entailment/models/syntactic_entailment.py
Merging v4 into develop (#6)
* Starting to train the constituency parser separately.

* Constituency parser file now specified in config.

* Adjusting config to match v4.

@@ -69,6 +69,8 @@ class SyntacticEntailment(Model):
                  similarity_function: SimilarityFunction,
                  compare_feedforward: FeedForward,
                  aggregate_feedforward: FeedForward,
+                 parser_model_path: str,
+                 predictor_name: str,
                  premise_encoder: Optional[Seq2SeqEncoder] = None,
                  hypothesis_encoder: Optional[Seq2SeqEncoder] = None,
                  initializer: InitializerApplicator = InitializerApplicator(),
@@ -97,9 +99,8 @@ class SyntacticEntailment(Model):
         self._accuracy = CategoricalAccuracy()
         self._loss = torch.nn.CrossEntropyLoss()
 
-        self._predictor = Predictor.from_path(
-                "models/elmo-constituency-parser/model.tgz",
-                predictor_name="syntactic-entailment-constituency-parser")
+        self._predictor = Predictor.from_path(parser_model_path,
+                predictor_name=predictor_name)
 
         self._device = torch.device("cuda:0" if torch.cuda.is_available()
                                              else "cpu")

### 2019-02-09 scripts/flatten_ptb.py
Merging v4 into develop (#6)
* Starting to train the constituency parser separately.

* Constituency parser file now specified in config.

* Adjusting config to match v4.

@@ -1,0 +1,48 @@
+#!/usr/bin/env python3
+
+import os
+import glob
+import argparse
+
+
+def main(args):
+    if not os.path.isdir(args.directory):
+        print(args.directory, '''is not a directory. Please enter a valid path
+            to a directory.''')
+        sys.exit(1)
+
+    train = open(args.out + '/train.ptb', 'w')
+    dev = open(args.out + '/dev.ptb', 'w')
+    test = open(args.out + '/test.ptb', 'w')
+
+    for filename in glob.iglob(args.directory + '/data/penntree/**',
+            recursive=True):
+        if os.path.isfile(filename):
+            split_num = int(filename.split(os.sep)[-2])
+            with open(filename) as f:
+                for line in f:
+                    if split_num < 23:
+                        print(line, end='', file=train)
+                    elif split_num == 23:
+                        print(line, end='', file=test)
+                    elif split_num == 24:
+                        print(line, end='', file=dev)
+
+    train.close()
+    dev.close()
+    test.close()
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description='''Flatten PTB-revised data
+            into train, dev, and test files.''')
+
+    parser.add_argument('directory', help='''The directory of the
+            PTB-revised data.''')
+    parser.add_argument('--out', '-o', dest='out', help='''The directory of
+            where the output should be saved.''')
+
+
+    args = parser.parse_args()
+
+    main(args)

### 2019-02-09 syntactic_entailment/data/dataset_readers/se_ptb.py

@@ -1,0 +1,232 @@
+
+from typing import Dict, List, Tuple
+import logging
+import os
+
+from overrides import overrides
+# NLTK is so performance orientated (ha ha) that they have lazy imports. Why? Who knows.
+from nltk.corpus.reader.bracket_parse import BracketParseCorpusReader # pylint: disable=no-name-in-module
+from nltk.tree import Tree
+
+from allennlp.common.file_utils import cached_path
+from allennlp.data.dataset_readers.dataset_reader import DatasetReader
+from allennlp.data.fields import TextField, SpanField, SequenceLabelField, ListField, MetadataField, Field
+from allennlp.data.instance import Instance
+from allennlp.data.token_indexers import TokenIndexer, SingleIdTokenIndexer
+from allennlp.data.tokenizers import Token
+from allennlp.data.dataset_readers.dataset_utils.span_utils import enumerate_spans
+from allennlp.common.checks import ConfigurationError
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+
+@DatasetReader.register("se_ptb_trees")
+class PennTreeBankConstituencySpanDatasetReader(DatasetReader):
+    """
+    Reads constituency parses from the WSJ part of the Penn Tree Bank from the LDC.
+    This ``DatasetReader`` is designed for use with a span labelling model, so
+    it enumerates all possible spans in the sentence and returns them, along with gold
+    labels for the relevant spans present in a gold tree, if provided.
+
+    Parameters
+    ----------
+    token_indexers : ``Dict[str, TokenIndexer]``, optional (default=``{"tokens": SingleIdTokenIndexer()}``)
+        We use this to define the input representation for the text.  See :class:`TokenIndexer`.
+        Note that the `output` tags will always correspond to single token IDs based on how they
+        are pre-tokenised in the data file.
+    use_pos_tags : ``bool``, optional, (default = ``True``)
+        Whether or not the instance should contain gold POS tags
+        as a field.
+    lazy : ``bool``, optional, (default = ``False``)
+        Whether or not instances can be consumed lazily.
+    label_namespace_prefix : ``str``, optional, (default = ``""``)
+        Prefix used for the label namespace.  The ``span_labels`` will use
+        namespace ``label_namespace_prefix + 'labels'``, and if using POS
+        tags their namespace is ``label_namespace_prefix + pos_label_namespace``.
+    pos_label_namespace : ``str``, optional, (default = ``"pos"``)
[…]

### 2019-02-09 syntactic_entailment/models/syntactic_entailment.py
Adding back in legacy matrix attention.

@@ -8,11 +8,12 @@ from allennlp.data import Vocabulary
 from allennlp.models.model import Model
 from allennlp.modules import FeedForward
 from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
+from allennlp.modules.matrix_attention.legacy_matrix_attention import LegacyMatrixAttention
 from allennlp.nn import InitializerApplicator, RegularizerApplicator
 from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
 from allennlp.training.metrics import CategoricalAccuracy
 
-from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
+#from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
 from syntactic_entailment.predictors.constituency_parser import SyntacticEntailmentConstituencyParserPredictor
 
 
@@ -79,7 +80,7 @@ class SyntacticEntailment(Model):
 
         self._text_field_embedder = text_field_embedder
         self._attend_feedforward = TimeDistributed(attend_feedforward)
-        self._matrix_attention = SyntacticMatrixAttention(similarity_function)
+        self._matrix_attention = LegacyMatrixAttention(similarity_function)
         self._compare_feedforward = TimeDistributed(compare_feedforward)
         self._aggregate_feedforward = aggregate_feedforward
         self._premise_encoder = premise_encoder
@@ -169,9 +170,11 @@ class SyntacticEntailment(Model):
         projected_hypothesis = self._attend_feedforward(embedded_hypothesis)
         # Shape: (batch_size, premise_length, hypothesis_length)
         similarity_matrix = self._matrix_attention(projected_premise,
-                                                   projected_hypothesis,
-                                                   p_encoded_parse,
-                                                   h_encoded_parse)
+                                                   projected_hypothesis)
+        #similarity_matrix = self._matrix_attention(projected_premise,
+        #                                           projected_hypothesis,
+        #                                           p_encoded_parse,
+        #                                           h_encoded_parse)
 
         # Shape: (batch_size, premise_length, hypothesis_length)
         p2h_attention = masked_softmax(similarity_matrix, hypothesis_mask)

### 2019-02-09 syntactic_entailment/models/syntactic_entailment.py
Cleaning up configs.

@@ -88,10 +88,10 @@ class SyntacticEntailment(Model):
 
         self._num_labels = vocab.get_vocab_size(namespace="labels")
 
-        check_dimensions_match(text_field_embedder.get_output_dim(),
-                               attend_feedforward.get_input_dim(),
-                               "text field embedding dim",
-                               "attend feedforward input dim")
+        #check_dimensions_match(text_field_embedder.get_output_dim(),
+        #                       attend_feedforward.get_input_dim(),
+        #                       "text field embedding dim",
+        #                       "attend feedforward input dim")
         check_dimensions_match(aggregate_feedforward.get_output_dim(),
                                self._num_labels,
                                "final output dimension",
@@ -166,8 +166,16 @@ class SyntacticEntailment(Model):
         if self._hypothesis_encoder:
             embedded_hypothesis = self._hypothesis_encoder(embedded_hypothesis, hypothesis_mask)
 
-        projected_premise = self._attend_feedforward(embedded_premise)
-        projected_hypothesis = self._attend_feedforward(embedded_hypothesis)
+        #print('premise shape before attention', embedded_premise.shape)
+        #print('concatenating shit')
+        syntax_premise = torch.cat((embedded_premise, p_encoded_parse), 2)
+        #print('shape after concat', embedded_premise.shape)
+        projected_premise = self._attend_feedforward(syntax_premise)
+        #print('premise shape after attention', syntax_premise.shape)
+        #exit(1)
+        syntax_hypothesis = torch.cat((embedded_hypothesis, h_encoded_parse), 2)
+        projected_hypothesis = self._attend_feedforward(syntax_hypothesis)
+        #print('hypothesis shape after attention', syntax_hypothesis.shape)
         # Shape: (batch_size, premise_length, hypothesis_length)
         similarity_matrix = self._matrix_attention(projected_premise,
                                                    projected_hypothesis)

### 2019-02-09 syntactic_entailment/models/syntactic_entailment.py
Cleaning up model file.

@@ -13,7 +13,6 @@ from allennlp.nn import InitializerApplicator, RegularizerApplicator
 from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
 from allennlp.training.metrics import CategoricalAccuracy
 
-#from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
 from syntactic_entailment.predictors.constituency_parser import SyntacticEntailmentConstituencyParserPredictor
 
 
@@ -88,6 +87,7 @@ class SyntacticEntailment(Model):
 
         self._num_labels = vocab.get_vocab_size(namespace="labels")
 
+        # this check doesn't work anymore since we attend w/ syntax
         #check_dimensions_match(text_field_embedder.get_output_dim(),
         #                       attend_feedforward.get_input_dim(),
         #                       "text field embedding dim",
@@ -166,23 +166,17 @@ class SyntacticEntailment(Model):
         if self._hypothesis_encoder:
             embedded_hypothesis = self._hypothesis_encoder(embedded_hypothesis, hypothesis_mask)
 
-        #print('premise shape before attention', embedded_premise.shape)
-        #print('concatenating shit')
+        # concat syntax
         syntax_premise = torch.cat((embedded_premise, p_encoded_parse), 2)
-        #print('shape after concat', embedded_premise.shape)
         projected_premise = self._attend_feedforward(syntax_premise)
-        #print('premise shape after attention', syntax_premise.shape)
-        #exit(1)
+
+        # concat syntax
         syntax_hypothesis = torch.cat((embedded_hypothesis, h_encoded_parse), 2)
         projected_hypothesis = self._attend_feedforward(syntax_hypothesis)
-        #print('hypothesis shape after attention', syntax_hypothesis.shape)
+
         # Shape: (batch_size, premise_length, hypothesis_length)
         similarity_matrix = self._matrix_attention(projected_premise,
                                                    projected_hypothesis)
-        #similarity_matrix = self._matrix_attention(projected_premise,
-        #                                           projected_hypothesis,
-        #                                           p_encoded_parse,
-        #                                           h_encoded_parse)
 
         # Shape: (batch_size, premise_length, hypothesis_length)
         p2h_attention = masked_softmax(similarity_matrix, hypothesis_mask)

### 2019-02-09 paper/main.tex
Procrastinating by adding random text to paper.

@@
 
-\aclfinalcopy % Uncomment this line for the final submission
+%\aclfinalcopy % Uncomment this line for the final submission
 
@@
 
-\title{Instructions for \confname{} Proceedings}
+\title{Title}
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+\author{
+  Deric Pang$^\heartsuit$ \quad
+  Author 2 \quad
+  Author 3 \quad
+  Author 4 \\
+  $^\heartsuit$Paul G. Allen of Computer Science \& Engineering,
+    University of Washington,
+    Seattle, WA, USA \\
+  $^\diamondsuit$Allen Institute for Artificial Intelligence, Seattle, WA,
+    USA \\
+  {\tt \{dericp, author2, author3, author4\}@cs.washington.edu} \\
+}
 
@@
 \begin{abstract}
-  Abstract.
+  We show that syntactic information is important when performing natural
+  language inference (NLI). We describe new modeling techniques for NLI that
+  improve upon previous baselines by adding minimal amounts of syntactic
+  information.
 \end{abstract}
@@
 Natural language inference (NLI) is the task of characterizing entailment and
-contradiction relationships between texts.  We seek to improve models which
-perform NLI by adding syntactic features into existing models. In particular,
-we will primarily investigate the well-known decomposable attention (DA) neural
-network \citep{Parikh2016-em} which obtained state of the art results on the
-SNLI \citep{Bowman2015-is} dataset at its time of publication while using
-drastically fewer parameters than previous NLI models.
-
-We intend to extend the DA model and evaluate new models on SNLI, MultiNLI
-\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
-\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
-\citep{Khot2018-th}.
-
+contradiction relationships between texts.
 In general, most NLI tasks are formulated as characterizing the relationship
@@
 premise, or is neutral to the premise.
+
+We seek to improve models which
+perform NLI by adding syntactic features into existing models. In particular,
+we investigate the well-known decomposable attention (DA) neural network
+\citep{Parikh2016-em} which obtained state of the art results on the
+SNLI \citep{Bowman2015-is} dataset at its time of publication while using
+drastically fewer parameters than previous NLI models.
+
+We extend the DA model and evaluate new models on SNLI, MultiNLI
+\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
+\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
+\citep{Khot2018-th}.
 

### 2019-03-17 cse517/report/main.tex
Starting report.

--- 2019-02-08 paper/main.tex
@@
 %
-% File emnlp2018.tex
+% File acl2018.tex
 %
-%% Based on the style files for EMNLP 2018, which were
-%% Based on the style files for ACL 2018, which were
+%% Based on the style files for ACL-2017, with some changes, which were, in turn,
 %% Based on the style files for ACL-2015, with some improvements
@@
 \documentclass[11pt,a4paper]{article}
-\usepackage[hyperref]{emnlp2018}
+\usepackage[hyperref]{acl2019}
 \usepackage{times}
 \usepackage{latexsym}
-
 \usepackage{url}
-
-% user packages
 \usepackage{graphicx}
-\graphicspath{{figures/}}
 \usepackage{booktabs}
@@
 \aclfinalcopy % Uncomment this line for the final submission
+%\def\aclpaperid{***} %  Enter the acl Paper ID here
 
@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
-\newcommand\confname{EMNLP 2018}
-\newcommand\conforg{SIGDAT}
 
-\title{Instructions for \confname{} Proceedings}
+\title{CSE 517: Project Proposal}
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+\author{
+  Deric Pang \quad
+  Joshua Bean \\
+  Paul G. Allen School of Computer Science \& Engineering \\
+  University of Washington \\
+  Seattle, WA, USA \\
+  {\tt \{dericp, jbean96\}@cs.washington.edu} \\
+}
 
@@
 \maketitle
-\begin{abstract}
-  Abstract.
-\end{abstract}
 
@@
 
-\section{Credits}
-
-\bibliography{references}
-\bibliographystyle{acl_natbib_nourl}
+\bibliographystyle{acl_natbib}
+\bibliography{main}
 

### 2019-03-18 cse517/report/main.tex
Updating report

@@
 
-\title{CSE 517: Project Proposal}
+\newcommand{\dpcomment}[1]{\textcolor{green}{[#1 --deric]}}
+\newcommand{\jbcomment}[1]{\textcolor{orange}{[#1 --josh]}}
+
+\title{Syntactically Informed Natural Language Inference}
 
@@
 \maketitle
+\begin{abstract}
+  Abstract.
+\end{abstract}
 
@@
 
-We intend to extend the DA model and evaluate new models on SNLI, MultiNLI
-\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
-\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
-\citep{Khot2018-th}.
-
 In general, most NLI tasks are formulated as characterizing the relationship
@@
 
-\section{Previous Work}
+We extend the DA model by encorporating syntactic features.
+\dpcomment{Include brief summary of constributions here.}
+We primarily
+evaluate on the domain specific Scitail \citep{Khot2018-th} for both its
+smaller size and lack of annotation artifacts when compared to SNLI
+\citep{Gururangan2018-lj}.
+
+\section{Syntactic Entailment}
 

### 2019-03-18 syntactic_entailment/models/syntactic_entailment_v3.py
Develop v6 (#13)
* Added dependency parser predictor

* Added dependency parser

* checking in dependency marser model

* Added dependency parsing stuff

* Fixed dependency parser

* Added dep parse training script

* Added dependency parser predictor

* Added dependency parser

* checking in dependency marser model

* Added dependency parsing stuff

* Fixed dependency parser

* Added dep parse training script

* Moving these configs back to using GPU.

* Moving dep parser config to config directory.

* Added stuff to scripts

* Removed unnecessary train-se-dep.sh script

* Fixing dimensions.

@@ -1,0 +1,222 @@
+from typing import Dict, Optional, List, Any
+
+import torch
+
+from allennlp.predictors.predictor import Predictor
+from allennlp.common.checks import check_dimensions_match
+from allennlp.data import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import FeedForward
+from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
+from allennlp.nn import InitializerApplicator, RegularizerApplicator
+from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
+from allennlp.training.metrics import CategoricalAccuracy
+
+from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
+from syntactic_entailment.predictors.constituency_parser import SyntacticEntailmentConstituencyParserPredictor
+
+
+@Model.register("syntactic_entailment_v3")
+class SyntacticEntailment(Model):
+    """
+    This ``Model`` implements the Decomposable Attention model described in `"A Decomposable
+    Attention Model for Natural Language Inference"
+    <https://www.semanticscholar.org/paper/A-Decomposable-Attention-Model-for-Natural-Languag-Parikh-T%C3%A4ckstr%C3%B6m/07a9478e87a8304fc3267fa16e83e9f3bbd98b27>`_
+    by Parikh et al., 2016, with some optional enhancements before the decomposable attention
+    actually happens.  Parikh's original model allowed for computing an "intra-sentence" attention
+    before doing the decomposable entailment step.  We generalize this to any
+    :class:`Seq2SeqEncoder` that can be applied to the premise and/or the hypothesis before
+    computing entailment.
+
+    The basic outline of this model is to get an embedded representation of each word in the
+    premise and hypothesis, align words between the two, compare the aligned phrases, and make a
+    final entailment decision based on this aggregated comparison.  Each step in this process uses
+    a feedforward network to modify the representation.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``
+    text_field_embedder : ``TextFieldEmbedder``
+        Used to embed the ``premise`` and ``hypothesis`` ``TextFields`` we get as input to the
+        model.
+    attend_feedforward : ``FeedForward``
+        This feedforward network is applied to the encoded sentence representations before the
+        similarity matrix is computed between words in the premise and words in the hypothesis.
+    similarity_function : ``SimilarityFunction``
[…]

### 2019-03-18 scripts/test-se.sh
Develop v6 (#13)
* Added dependency parser predictor

* Added dependency parser

* checking in dependency marser model

* Added dependency parsing stuff

* Fixed dependency parser

* Added dep parse training script

* Added dependency parser predictor

* Added dependency parser

* checking in dependency marser model

* Added dependency parsing stuff

* Fixed dependency parser

* Added dep parse training script

* Moving these configs back to using GPU.

* Moving dep parser config to config directory.

* Added stuff to scripts

* Removed unnecessary train-se-dep.sh script

* Fixing dimensions.

@@ -1,8 +1,16 @@
 ELMO=""
-while getopts ":e" opt; do
+DEP_PARSER=""
+CUDA_DEVICE=""
+while getopts ":edc" opt; do
     case $opt in
         e)
             ELMO="-elmo"
+            ;;
+        d)
+            DEP_PARSER="-dependency-parser"
+            ;;
+        c)
+            CUDA_DEVICE="--cuda-device 0"
             ;;
         \?)
             echo "Invalid option: -$OPTARG" >&2
@@ -14,7 +22,7 @@ shift $(( OPTIND-1 ))
 
 DATASET="$1"
 TEST_PATH="$2"
-SERIALIZATION_DIR="./models/se-$DATASET$ELMO"
+SERIALIZATION_DIR="./models/se-$DATASET$ELMO$DEP_PARSER"
 
 echo "Evaluating model at $SERIALIZATION_DIR with $TEST_PATH."
-allennlp evaluate "$SERIALIZATION_DIR"/model.tar.gz $TEST_PATH --include-package syntactic_entailment
+allennlp evaluate "$SERIALIZATION_DIR"/model.tar.gz $TEST_PATH --include-package syntactic_entailment $CUDA_DEVICE

### 2019-03-18 scripts/train-se.sh

@@ -1,8 +1,12 @@
 ELMO=""
-while getopts ":e" opt; do
+DEP_PARSER=""
+while getopts ":ed" opt; do
     case $opt in
         e)
             ELMO="-elmo"
+            ;;
+        d)
+            DEP_PARSER="-dependency-parser"
             ;;
         \?)
             echo "Invalid option: -$OPTARG" >&2
@@ -13,8 +17,8 @@ done
 shift $(( OPTIND-1 ))
 
 DATASET="$1"
-SERIALIZATION_DIR="./models/se-$DATASET$ELMO"
-CONFIG="config/se-$DATASET$ELMO.jsonnet"
+SERIALIZATION_DIR="./models/se-$DATASET$ELMO$DEP_PARSER"
+CONFIG="config/se-$DATASET$ELMO$DEP_PARSER.jsonnet"
 
 #rm -rf "$SERIALIZATION_DIR"
 echo "Training $CONFIG. Saving model to $SERIALIZATION_DIR."

### 2019-03-18 syntactic_entailment/models/dependency_parser.py

@@ -1,0 +1,567 @@
+from typing import Dict, Optional, Tuple, Any, List
+import logging
+import copy
+
+from overrides import overrides
+import torch
+import torch.nn.functional as F
+from torch.nn.modules import Dropout
+import numpy
+
+from allennlp.common.checks import check_dimensions_match, ConfigurationError
+from allennlp.data import Vocabulary
+from allennlp.modules import Seq2SeqEncoder, TextFieldEmbedder, Embedding, InputVariationalDropout
+from allennlp.modules.matrix_attention.bilinear_matrix_attention import BilinearMatrixAttention
+from allennlp.modules import FeedForward
+from allennlp.models.model import Model
+from allennlp.nn import InitializerApplicator, RegularizerApplicator, Activation
+from allennlp.nn.util import get_text_field_mask, get_range_vector
+from allennlp.nn.util import get_device_of, masked_log_softmax, get_lengths_from_binary_sequence_mask
+from allennlp.nn.chu_liu_edmonds import decode_mst
+from allennlp.training.metrics import AttachmentScores
+
+from allennlp.models.biaffine_dependency_parser import BiaffineDependencyParser
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+POS_TO_IGNORE = {'``', "''", ':', ',', '.', 'PU', 'PUNCT', 'SYM'}
+
+@Model.register("syntactic_entailment_dependency_parser")
+class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
+    """
+    This dependency parser follows the model of
+    ` Deep Biaffine Attention for Neural Dependency Parsing (Dozat and Manning, 2016)
+    <https://arxiv.org/abs/1611.01734>`_ .
+
+    Word representations are generated using a bidirectional LSTM,
+    followed by separate biaffine classifiers for pairs of words,
+    predicting whether a directed arc exists between the two words
+    and the dependency label the arc should have. Decoding can either
+    be done greedily, or the optimal Minimum Spanning Tree can be
+    decoded using Edmond's algorithm by viewing the dependency tree as
+    a MST on a fully connected graph, where nodes are words and edges
+    are scored dependency arcs.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``, required
+        A Vocabulary, required in order to compute sizes for input/output projections.
+    text_field_embedder : ``TextFieldEmbedder``, required
+        Used to embed the ``tokens`` ``TextField`` we get as input to the model.
[…]

### 2019-03-18 syntactic_entailment/predictors/dependency_parser.py

@@ -1,0 +1,60 @@
+from typing import Dict, Any, List, Tuple
+
+from overrides import overrides
+
+from allennlp.common.util import JsonDict, sanitize
+from allennlp.data import DatasetReader, Instance
+from allennlp.models import Model
+from allennlp.predictors.predictor import Predictor
+from allennlp.predictors.biaffine_dependency_parser import BiaffineDependencyParserPredictor
+from allennlp.data.tokenizers.word_splitter import SpacyWordSplitter
+
+@Predictor.register('syntactic-entailment-dependency-parser')
+class SyntacticEntailmentDependencyParserPredictor(BiaffineDependencyParserPredictor):
+    """
+    Predictor for the :class:`~allennlp.models.BiaffineDependencyParser` model.
+    """
+    def __init__(self, model: Model, dataset_reader: DatasetReader, language: str = 'en_core_web_sm') -> None:
+        super().__init__(model, dataset_reader)
+        # TODO(Mark) Make the language configurable and based on a model attribute.
+        self._tokenizer = SpacyWordSplitter(language=language, pos_tags=True)
+
+    def predict(self, sentence: str) -> JsonDict:
+        """
+        Predict a dependency parse for the given sentence.
+        Parameters
+        ----------
+        sentence The sentence to parse.
+
+        Returns
+        -------
+        A dictionary representation of the dependency tree.
+        """
+        return self.predict_json({"sentence" : sentence})
+
+    @overrides
+    def _json_to_instance(self, json_dict: JsonDict) -> Instance:
+        """
+        Expects JSON that looks like ``{"sentence": "..."}``.
+        """
+        # spacy_tokens = self._tokenizer.split_words(json_dict["sentence"])
+        # sentence_text = [token.text for token in spacy_tokens]
+        # if self._dataset_reader.use_language_specific_pos: # type: ignore
+        #     # fine-grained part of speech
+        #     pos_tags = [token.tag_ for token in spacy_tokens]
+        # else:
+        #     # coarse-grained part of speech (Universal Depdendencies format)
+        #     pos_tags = [token.pos_ for token in spacy_tokens]
+        sentence_text = json_dict["sentence"]
+        pos_tags = json_dict["tags"]
+        return self._dataset_reader.text_to_instance(sentence_text, pos_tags)
+
+    @overrides
+    def predict_instance(self, instance: Instance) -> JsonDict:
+        outputs = self._model.forward_on_instance(instance)
[…]

### 2019-03-18 cse517/proposal/main.tex
Develop paper (#14)
* First draft of project proposal.

* Ready to submit.

* Switching to emnlp template.

* Moving proposal content to paper.

* Adding figures.

* Procrastinating by adding random text to paper.

* Starting report.

* Updating report

@@
 Natural language inference (NLI) is the task of characterizing entailment and
-contradiction relationships between texts.
-We seek to improve NLI models by adding syntactic
-features into existing models. The well-known decomposable attention (DA)
-neural network \citep{Parikh2016-em} obtained state of the art results on the
+contradiction relationships between texts.  We seek to improve models which
+perform NLI by adding syntactic features into existing models. In particular,
+we will primarily investigate the well-known decomposable attention (DA) neural
+network \citep{Parikh2016-em} which obtained state of the art results on the
 SNLI \citep{Bowman2015-is} dataset at its time of publication while using
@@
 
-We intend to extend this
-model and evaluate it on SNLI, MultiNLI \citep{Williams2017-uh}, the SNLI and
-MultiNLI hard splits \citep{Gururangan2018-lj}, and smaller domain specific
-datasets like Scitail \citep{Khot2018-th}.
+We intend to extend the DA model and evaluate new models on SNLI, MultiNLI
+\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
+\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
+\citep{Khot2018-th}.
+
+In general, most NLI tasks are formulated as characterizing the relationship
+between a pair of sequences---a premise and a hypothesis. An NLI model should
+predict whether the hyothesis is entailed by the premise, contradicts the
+premise, or is neutral to the premise.
 
@@
 
-In previous work, we created the syntail-v1 model whose architecture is
-shown in figure \ref{figure:v1}.
-We have obtained mixed results as shown in table \ref{table:v1-accuracies} when
-naively incorporating syntactic information
-into the DA model.
+In previous work, we created the syntail-v1 model whose architecture is shown
+in figure~\ref{figure:v1}.  We have obtained mixed results as shown in
+table~\ref{table:v1-accuracies} when naively incorporating syntactic
+information into the DA model.
 
-Wihthout ELMo, syntail-v1 improves an impressive 8.4\% in test accuracy over
-the baseline decomposable attention model on the SciTail dataset. However,
-once ELMo is added to the model, almost the exact happens. Adding syntactic
-information decreases test accuracy by 6.7\%.
+Without ELMo, syntail-v1 improves an impressive 8.4\% in test accuracy over the
+baseline decomposable attention model on the SciTail dataset. However, once
+ELMo is added to the model, almost the exact opposite occurs. Adding syntactic
+information decreases test accuracy by 6.7\% with ELMo.
 
@@
     DA & GLoVe 6b 300d & 89.4\% & 70.1\% \\
-    \textbf{Syntail-v1} & \textbf{GLoVe 6b 300d} & \textbf{92.1\%} & \textbf{78.5\%} \\
-    \textbf{DA} & \textbf{ELMo} & \textbf{98.4\%} & \textbf{78.0\%} \\
-    Syntail-v1 & ELMo & 88.8\% & 71.3\% \\
+    \textbf{Syntail-v1} & \textbf{GLoVe 6b 300d} & \textbf{92.1\%}
+                        & \textbf{78.5\%} \\
+    DA & ELMo & 98.4\% & 78.0\% \\
+    \textbf{Syntail-v1} & \textbf{ELMo} & \textbf{88.8\%} & \textbf{71.3\%} \\
     \bottomrule
@@
 dependency \citep{Dozat2016-gs} parsers to investigate if incorporating
-syntactic features improves the performance of the decomposable attention
-network. Additionally, we hope to understand how syntactic features interact
-with contextual
-word embeddings like ELMo \citep{Peters2018-fz} and BERT \citep{Devlin2018-qc}
-in a task like NLI.
+syntactic features improves the performance of the DA model. Additionally, we
+hope to understand how syntactic features interact with contextual word
+embeddings like ELMo \citep{Peters2018-fz} and BERT \citep{Devlin2018-qc} in a
+task like NLI. It is unclear from previous work whether contextual word
+embeddings benefit from additional syntactic information or if something like
+ELMo can already adequately capture this information.
 
@@
 information. \citet{Pang2018-syntail} use a constituency parser to obtain an
-encoding of the premise and hypothesis that is used when characterizing their
-relationship. We believe that incorporating syntactic features earlier in the
-pipeline, especially before the premise and hypothesis are attended over one
-another, should improve performance.
+encoding of the premise and hypothesis that is in the final fully-connected
+layer of the DA model. We believe that incorporating syntactic features earlier
+in the pipeline, especially before the premise and hypothesis are attended over
+one another, should improve performance.
 

### 2019-03-18 syntactic_entailment/models/syntactic_entailment.py
Deleting unnecessary imports.

@@ -14,7 +14,6 @@ from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
 from allennlp.training.metrics import CategoricalAccuracy
 
 from syntactic_entailment.predictors.constituency_parser import SyntacticEntailmentConstituencyParserPredictor
-from syntactic_entailment.predictors.dependency_parser import SyntacticEntailmentDependencyParserPredictor
 
 
 @Model.register("syntactic_entailment")

### 2019-03-18 syntactic_entailment/models/syntactic_entailment_v3.py
Deleting unnecessary imports.

@@ -13,7 +13,6 @@ from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
 from allennlp.training.metrics import CategoricalAccuracy
 
 from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
-from syntactic_entailment.predictors.constituency_parser import SyntacticEntailmentConstituencyParserPredictor
 
 
 @Model.register("syntactic_entailment_v3")

### 2019-03-18 syntactic_entailment/models/syntactic_entailment_v3.py
Fixing namings.

@@ -15,7 +15,7 @@ from allennlp.training.metrics import CategoricalAccuracy
 from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
 
 
-@Model.register("syntactic_entailment_v3")
+@Model.register("syntactic-entailment-v3")
 class SyntacticEntailment(Model):
     """
     This ``Model`` implements the Decomposable Attention model described in `"A Decomposable

### 2019-03-18 syntactic_entailment/models/syntactic_entailment_v5.py
Fixing namings.

@@ -16,7 +16,7 @@ from allennlp.training.metrics import CategoricalAccuracy
 from syntactic_entailment.predictors.constituency_parser import SyntacticEntailmentConstituencyParserPredictor
 
 
-@Model.register("syntactic_entailment")
+@Model.register("syntactic-entailment-v5")
 class SyntacticEntailment(Model):
     """
     This ``Model`` implements the Decomposable Attention model described in `"A Decomposable

### 2019-03-18 syntactic_entailment/modules/matrix_attention/syntactic_matrix_attention.py
Cleaning up matrix attention.

@@ -23,23 +23,15 @@ class SyntacticMatrixAttention(MatrixAttention):
     @overrides
     def forward(self, matrix_1: torch.Tensor, matrix_2: torch.Tensor,
                 syntax_1: torch.Tensor, syntax_2: torch.Tensor) -> torch.Tensor:
-        #print('syntax_1', syntax_1.is_cuda, syntax_1.shape)
-        #print('matrix_1', matrix_1.is_cuda, matrix_1.shape)
         matrix_1 = torch.cat((matrix_1, syntax_1), 2)
         matrix_2 = torch.cat((matrix_2, syntax_2), 2)
-        #print('catted matrix_1', matrix_1.shape)
         tiled_matrix_1 = matrix_1.unsqueeze(2).expand(matrix_1.size()[0],
                                                       matrix_1.size()[1],
                                                       matrix_2.size()[1],
                                                       matrix_1.size()[2])
-        #print('tiled_matrix_1', tiled_matrix_1.shape)
-        #print('syntax_2', syntax_2.shape)
-        #print('matrix_2', matrix_2.shape)
         tiled_matrix_2 = matrix_2.unsqueeze(1).expand(matrix_2.size()[0],
                                                       matrix_1.size()[1],
                                                       matrix_2.size()[1],
                                                       matrix_2.size()[2])
-        #print('tiled_matrix_2', tiled_matrix_2.shape)
         ret = self._similarity_function(tiled_matrix_1, tiled_matrix_2)
-        #print('ret', ret.shape)
         return ret

### 2019-03-18 cse517/report/main.tex
Making some changes.

@@
 
+\section{Models}
+
+The syntactic entailment model is derived from the decomposable attention model for natural language inference described in \href{https://arxiv.org/pdf/1606.01933.pdf}{this paper}.
+In the initial iteration, syntax was not incorporated into the neural network until the very last feed-forward layer.
+This means that during the attention steps between the premise and the hypothesis, the syntax was not taken into account.
+We speculated that by introducing syntax to the network prior to calculating attention we would see better results due to the syntax of the two statements influencing the attention computations.
+
+In the ``V3" model, we performed the same initial step of embedding the premise and hypothesis and expanding their dimensions (through a fully-connected layer) prior to attention.
+However, instead of calculating our similarity matrix using solely the embedded hypothesis and premise vectors as input, we also provide the .
+The grouping of these vectors was then used when calculating attention whose influence was then propagated down to the comparison and summary layers further down the network.
+
+With the “V5” model we shifted the incorporation of syntax into the model even earlier.
+After getting the word embeddings for the premise and hypothesis, we actually pass them to an additional feed-forward layer to expand their dimensions for future inputs.
+For the “V5” model we actually introduced the syntax side-by-side with the embedded words through this feed-forward layer.
+The resulting tensors which incorporated the syntax were then passed all the way through the rest of the network.
+
+An addition to these variations on the decomposable attention model were variations using different versions of the syntax parser.
+We ret-rained the constituency parser on the Penn Treebank dataset and incorporated that into the model as well as replaced the constituency parser with a dependency parser.
+
 \section{Proposed Methods}

### 2019-03-18 syntactic_entailment/models/syntactic_entailment_v7.py
Trying out v7.

@@ -1,0 +1,225 @@
+from typing import Dict, Optional, List, Any
+
+import torch
+
+from allennlp.predictors.predictor import Predictor
+from allennlp.common.checks import check_dimensions_match
+from allennlp.data import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import FeedForward
+from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
+from allennlp.nn import InitializerApplicator, RegularizerApplicator
+from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
+from allennlp.training.metrics import CategoricalAccuracy
+
+from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
+
+
+@Model.register("syntactic-entailment-v7")
+class SyntacticEntailment(Model):
+    """
+    This ``Model`` implements the Decomposable Attention model described in `"A Decomposable
+    Attention Model for Natural Language Inference"
+    <https://www.semanticscholar.org/paper/A-Decomposable-Attention-Model-for-Natural-Languag-Parikh-T%C3%A4ckstr%C3%B6m/07a9478e87a8304fc3267fa16e83e9f3bbd98b27>`_
+    by Parikh et al., 2016, with some optional enhancements before the decomposable attention
+    actually happens.  Parikh's original model allowed for computing an "intra-sentence" attention
+    before doing the decomposable entailment step.  We generalize this to any
+    :class:`Seq2SeqEncoder` that can be applied to the premise and/or the hypothesis before
+    computing entailment.
+
+    The basic outline of this model is to get an embedded representation of each word in the
+    premise and hypothesis, align words between the two, compare the aligned phrases, and make a
+    final entailment decision based on this aggregated comparison.  Each step in this process uses
+    a feedforward network to modify the representation.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``
+    text_field_embedder : ``TextFieldEmbedder``
+        Used to embed the ``premise`` and ``hypothesis`` ``TextFields`` we get as input to the
+        model.
+    attend_feedforward : ``FeedForward``
+        This feedforward network is applied to the encoded sentence representations before the
+        similarity matrix is computed between words in the premise and words in the hypothesis.
+    similarity_function : ``SimilarityFunction``
+        This is the similarity function used when computing the similarity matrix between words in
[…]

### 2019-03-19 syntactic_entailment/models/syntactic_entailment_v2.py
Checking in v2.

@@ -1,0 +1,222 @@
+from typing import Dict, Optional, List, Any
+
+import torch
+
+from allennlp.predictors.predictor import Predictor
+from allennlp.common.checks import check_dimensions_match
+from allennlp.data import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import FeedForward
+from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
+from allennlp.modules.matrix_attention.legacy_matrix_attention import LegacyMatrixAttention
+from allennlp.nn import InitializerApplicator, RegularizerApplicator
+from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
+from allennlp.training.metrics import CategoricalAccuracy
+
+
+@Model.register("syntactic-entailment-v2")
+class SyntacticEntailment(Model):
+    """
+    This ``Model`` implements the Decomposable Attention model described in `"A Decomposable
+    Attention Model for Natural Language Inference"
+    <https://www.semanticscholar.org/paper/A-Decomposable-Attention-Model-for-Natural-Languag-Parikh-T%C3%A4ckstr%C3%B6m/07a9478e87a8304fc3267fa16e83e9f3bbd98b27>`_
+    by Parikh et al., 2016, with some optional enhancements before the decomposable attention
+    actually happens.  Parikh's original model allowed for computing an "intra-sentence" attention
+    before doing the decomposable entailment step.  We generalize this to any
+    :class:`Seq2SeqEncoder` that can be applied to the premise and/or the hypothesis before
+    computing entailment.
+
+    The basic outline of this model is to get an embedded representation of each word in the
+    premise and hypothesis, align words between the two, compare the aligned phrases, and make a
+    final entailment decision based on this aggregated comparison.  Each step in this process uses
+    a feedforward network to modify the representation.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``
+    text_field_embedder : ``TextFieldEmbedder``
+        Used to embed the ``premise`` and ``hypothesis`` ``TextFields`` we get as input to the
+        model.
+    attend_feedforward : ``FeedForward``
+        This feedforward network is applied to the encoded sentence representations before the
+        similarity matrix is computed between words in the premise and words in the hypothesis.
+    similarity_function : ``SimilarityFunction``
+        This is the similarity function used when computing the similarity matrix between words in
[…]

### 2019-03-19 cse517/report/main.tex
Added model changes

--- 2019-03-18 cse517/report/main.tex
@@
 \begin{abstract}
-  Abstract.
+This project explores methods for improving performance on the task of natural language inference by incorporating syntactic information.
+Specifically we modify the decomposable attention neural network \citep{Parikh2016-em} by incorporating encoded syntax parses of the input statements at different layers of the network.
+We supplement these experiments by using different syntax parsers including pre-trained constituency and dependency parsers as well as a constituency parser trained separately for this task.
 \end{abstract}
@@
 Natural language inference (NLI) is the task of characterizing entailment and
-contradiction relationships between texts. We seek to improve models which
-perform NLI by adding syntactic features into existing models. In particular,
-we will primarily investigate the well-known decomposable attention (DA) neural
-network \citep{Parikh2016-em} which obtained state of the art results on the
-SNLI \citep{Bowman2015-is} dataset at its time of publication while using
-drastically fewer parameters than previous NLI models.
+contradiction relationships between texts. We improve NLI models by adding syntactic
+features into existing models.
+We will primarily investigate the well-known decomposable attention (DA) neural
+network \citep{Parikh2016-em}
 
@@
 
-We extend the DA model by encorporating syntactic features.
-\dpcomment{Include brief summary of constributions here.}
+We extend the decomposable attention (DA) model by \citet{Parikh2016-em}
+incorporating syntactic features.
+\dpcomment{Include brief summary of contributions here.}
+The DA model obtained state-of-the-art results on the
+SNLI \citep{Bowman2015-is} dataset at its time of publication while using
+drastically fewer parameters than previous NLI models.
 We primarily
@@
 \section{Syntactic Entailment}
-
-Our project will build on previous work done by \citet{Pang2018-syntail}.
 
@@
 \end{table}
+
+\section{Models}
+
+The syntactic entailment model is derived from the decomposable attention model for natural language inference described by \citet{Parikh2016-em}.
+In the initial iteration of the network, syntax is not incorporated until the very last feed-forward layer.
+This means that syntax is not considered when calculating attention between the premise and the hypothesis.
+We speculated that by introducing syntax to the network prior to calculating attention we would see better results as the syntax would help influence the attention calculations and reveal the most important phrases of each input statement.
+
+In the ``V3" model, we perform the same initial step of embedding the premise and hypothesis and expanding their dimensions (through a fully-connected layer) prior to attention.
+However, instead of calculating our similarity matrix using solely the embedded hypothesis and premise vectors as input, we also provide the encoded syntax parses of both inputs.
+The concatenation of these four vectors is used to derive the similarity matrix which is then utilized in the attention computations between the premise and hypothesis.
+
+With the ``V5" model we tried to incorporate the computed syntax of the inputs even earlier.
+Instead of concatenating the encoded syntax parses with the embedded inputs and using that as input for the computation of the similarity matrix, we concatenated the syntax parses with their respective inputs and passed that through the first fully-connected layer.
+The two resulting vectors representing the embedded inputs with syntactic information are then used to compute the similarity matrix.
+
+Our ``V7" model took an additional step of learning weights for the encoded syntax parses by passing the vectors through an additional fully-connected layer before introducing them into the rest of the network.
+This model was built on top of the ``V3" model such that the weighted syntax parses are concatenated with the embedded premise and hypothesis statements when deriving the similarity matrix.
+
+Supplemental variations were done on top of these restructures of the network.
+One of the variations that we introduced was a retrained constituency parser.
+By retraining the constituency parser on the Penn Treebank dataset \citep{marcus1993building} we could change the dimensions of the encoded syntax vectors to better fit with our models.
+Additionally, we experimented with training our models using the dependency parser model derived by \citet{dozat2016deep} to see if the different types of encoded parses influenced the performance of the network.
 

### 2019-03-19 syntactic_entailment/models/dependency_parser_v2.py
Added dependency parser with encoded final state in new files, except for v2/se-scitail-dp.jsonnet

@@ -1,0 +1,569 @@
+from typing import Dict, Optional, Tuple, Any, List
+import logging
+import copy
+
+from overrides import overrides
+import torch
+import torch.nn.functional as F
+from torch.nn.modules import Dropout
+import numpy
+
+from allennlp.common.checks import check_dimensions_match, ConfigurationError
+from allennlp.data import Vocabulary
+from allennlp.modules import Seq2SeqEncoder, TextFieldEmbedder, Embedding, InputVariationalDropout
+from allennlp.modules.matrix_attention.bilinear_matrix_attention import BilinearMatrixAttention
+from allennlp.modules import FeedForward
+from allennlp.models.model import Model
+from allennlp.nn import InitializerApplicator, RegularizerApplicator, Activation
+from allennlp.nn.util import get_text_field_mask, get_range_vector, get_final_encoder_states
+from allennlp.nn.util import get_device_of, masked_log_softmax, get_lengths_from_binary_sequence_mask
+from allennlp.nn.chu_liu_edmonds import decode_mst
+from allennlp.training.metrics import AttachmentScores
+
+from allennlp.models.biaffine_dependency_parser import BiaffineDependencyParser
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+POS_TO_IGNORE = {'``', "''", ':', ',', '.', 'PU', 'PUNCT', 'SYM'}
+
+@Model.register("syntactic_entailment_dependency_parser_v2")
+class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
+    """
+    This dependency parser follows the model of
+    ` Deep Biaffine Attention for Neural Dependency Parsing (Dozat and Manning, 2016)
+    <https://arxiv.org/abs/1611.01734>`_ .
+
+    Word representations are generated using a bidirectional LSTM,
+    followed by separate biaffine classifiers for pairs of words,
+    predicting whether a directed arc exists between the two words
+    and the dependency label the arc should have. Decoding can either
+    be done greedily, or the optimal Minimum Spanning Tree can be
+    decoded using Edmond's algorithm by viewing the dependency tree as
+    a MST on a fully connected graph, where nodes are words and edges
+    are scored dependency arcs.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``, required
+        A Vocabulary, required in order to compute sizes for input/output projections.
+    text_field_embedder : ``TextFieldEmbedder``, required
[…]

### 2019-03-19 scripts/train-se.sh
Fixed some minor issues but getting size mismatch on line 200 in syntactic_entailment_v2.py

@@ -6,7 +6,7 @@ while getopts ":ed" opt; do
             ELMO="-elmo"
             ;;
         d)
-            DEP_PARSER="-dependency-parser"
+            DEP_PARSER="-dp"
             ;;
         \?)
             echo "Invalid option: -$OPTARG" >&2
@@ -18,7 +18,7 @@ shift $(( OPTIND-1 ))
 
 DATASET="$1"
 SERIALIZATION_DIR="./models/se-$DATASET$ELMO$DEP_PARSER"
-CONFIG="config/se-$DATASET$ELMO$DEP_PARSER.jsonnet"
+CONFIG="config/v2/se-$DATASET$ELMO$DEP_PARSER.jsonnet"
 
 #rm -rf "$SERIALIZATION_DIR"
 echo "Training $CONFIG. Saving model to $SERIALIZATION_DIR."

### 2019-03-19 syntactic_entailment/models/dependency_parser_v2.py
Fixed some minor issues but getting size mismatch on line 200 in syntactic_entailment_v2.py

@@ -165,7 +165,7 @@ class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
         embedded_text_input = self._input_dropout(embedded_text_input)
         encoded_text_orig = self.encoder(embedded_text_input, mask)
 
-        encoded_final_state = get_final_encoder_states(encoded_text_orig, mask)
+        encoder_final_state = get_final_encoder_states(encoded_text_orig, mask)
 
         batch_size, _, encoding_dim = encoded_text_orig.size()
 
@@ -234,7 +234,7 @@ class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
             loss = arc_nll + tag_nll
 
         output_dict = {
-                "encoded_text" : encoded_final_state,
+                "encoder_final_state": encoder_final_state,
                 "heads": predicted_heads,
                 "head_tags": predicted_head_tags,
                 "arc_loss": arc_nll,

### 2019-03-19 syntactic_entailment/models/constituency_parser_v2.py
Added files for runnning constituency parser tests

@@ -1,0 +1,411 @@
+from typing import Dict, Tuple, List, Optional, NamedTuple, Any
+from overrides import overrides
+
+import torch
+from torch.nn.modules.linear import Linear
+from nltk import Tree
+
+from allennlp.common.checks import check_dimensions_match
+from allennlp.data import Vocabulary
+from allennlp.modules import Seq2SeqEncoder, TimeDistributed, TextFieldEmbedder, FeedForward
+from allennlp.modules.token_embedders import Embedding
+from allennlp.modules.span_extractors.span_extractor import SpanExtractor
+from allennlp.models.model import Model
+from allennlp.nn import InitializerApplicator, RegularizerApplicator
+from allennlp.nn.util import get_text_field_mask, sequence_cross_entropy_with_logits
+from allennlp.nn.util import masked_softmax, get_lengths_from_binary_sequence_mask
+from allennlp.nn.util import get_final_encoder_states
+from allennlp.training.metrics import CategoricalAccuracy
+from allennlp.training.metrics import EvalbBracketingScorer, DEFAULT_EVALB_DIR
+from allennlp.common.checks import ConfigurationError
+
+from allennlp.models.constituency_parser import SpanConstituencyParser
+from allennlp.models.constituency_parser import SpanInformation
+
+@Model.register("syntactic_entailment_constituency_parser_v2")
+class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
+    """
+    This ``SpanConstituencyParser`` simply encodes a sequence of text
+    with a stacked ``Seq2SeqEncoder``, extracts span representations using a
+    ``SpanExtractor``, and then predicts a label for each span in the sequence.
+    These labels are non-terminal nodes in a constituency parse tree, which we then
+    greedily reconstruct.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``, required
+        A Vocabulary, required in order to compute sizes for input/output projections.
+    text_field_embedder : ``TextFieldEmbedder``, required
+        Used to embed the ``tokens`` ``TextField`` we get as input to the model.
+    span_extractor : ``SpanExtractor``, required.
+        The method used to extract the spans from the encoded sequence.
+    encoder : ``Seq2SeqEncoder``, required.
+        The encoder that we will use in between embedding tokens and
+        generating span representations.
+    feedforward : ``FeedForward``, required.
+        The FeedForward layer that we will use in between the encoder and the linear
[…]

### 2019-03-20 syntactic_entailment/models/syntactic_entailment_v8.py
Trying multinli.

@@ -1,0 +1,227 @@
+from typing import Dict, Optional, List, Any
+
+import torch
+
+from allennlp.predictors.predictor import Predictor
+from allennlp.common.checks import check_dimensions_match
+from allennlp.data import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import FeedForward
+from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
+from allennlp.modules.matrix_attention.legacy_matrix_attention import LegacyMatrixAttention
+from allennlp.nn import InitializerApplicator, RegularizerApplicator
+from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
+from allennlp.training.metrics import CategoricalAccuracy
+
+
+@Model.register("syntactic-entailment-v8")
+class SyntacticEntailment(Model):
+    """
+    This ``Model`` implements the Decomposable Attention model described in `"A Decomposable
+    Attention Model for Natural Language Inference"
+    <https://www.semanticscholar.org/paper/A-Decomposable-Attention-Model-for-Natural-Languag-Parikh-T%C3%A4ckstr%C3%B6m/07a9478e87a8304fc3267fa16e83e9f3bbd98b27>`_
+    by Parikh et al., 2016, with some optional enhancements before the decomposable attention
+    actually happens.  Parikh's original model allowed for computing an "intra-sentence" attention
+    before doing the decomposable entailment step.  We generalize this to any
+    :class:`Seq2SeqEncoder` that can be applied to the premise and/or the hypothesis before
+    computing entailment.
+
+    The basic outline of this model is to get an embedded representation of each word in the
+    premise and hypothesis, align words between the two, compare the aligned phrases, and make a
+    final entailment decision based on this aggregated comparison.  Each step in this process uses
+    a feedforward network to modify the representation.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``
+    text_field_embedder : ``TextFieldEmbedder``
+        Used to embed the ``premise`` and ``hypothesis`` ``TextFields`` we get as input to the
+        model.
+    attend_feedforward : ``FeedForward``
+        This feedforward network is applied to the encoded sentence representations before the
+        similarity matrix is computed between words in the premise and words in the hypothesis.
+    similarity_function : ``SimilarityFunction``
+        This is the similarity function used when computing the similarity matrix between words in
[…]

### 2019-03-20 syntactic_entailment/models/constituency_parser_v2.py
Cleaning up parser namings.

@@ -22,7 +22,7 @@ from allennlp.common.checks import ConfigurationError
 from allennlp.models.constituency_parser import SpanConstituencyParser
 from allennlp.models.constituency_parser import SpanInformation
 
-@Model.register("syntactic_entailment_constituency_parser_v2")
+@Model.register("syntactic-entailment-constituency-parser-v2")
 class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
     """
     This ``SpanConstituencyParser`` simply encodes a sequence of text

### 2019-03-20 syntactic_entailment/models/dependency_parser_v2.py

@@ -26,7 +26,7 @@ logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
 
 POS_TO_IGNORE = {'``', "''", ':', ',', '.', 'PU', 'PUNCT', 'SYM'}
 
-@Model.register("syntactic_entailment_dependency_parser_v2")
+@Model.register("syntactic-entailment-dependency-parser-v2")
 class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
     """
     This dependency parser follows the model of

### 2019-03-20 syntactic_entailment/models/constituency_parser_v4.py
Cleaning up parser namings.

@@ -22,7 +22,7 @@ from allennlp.common.checks import ConfigurationError
 from allennlp.models.constituency_parser import SpanConstituencyParser
 from allennlp.models.constituency_parser import SpanInformation
 
-@Model.register("syntactic_entailment_constituency_parser")
+@Model.register("syntactic-entailment-constituency-parser-v4")
 class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
     """
     This ``SpanConstituencyParser`` simply encodes a sequence of text

### 2019-03-20 syntactic_entailment/models/dependency_parser_v6.py
Cleaning up parser namings.

@@ -26,7 +26,7 @@ logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
 
 POS_TO_IGNORE = {'``', "''", ':', ',', '.', 'PU', 'PUNCT', 'SYM'}
 
-@Model.register("syntactic_entailment_dependency_parser")
+@Model.register("syntactic-entailment-dependency-parser-v6")
 class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
     """
     This dependency parser follows the model of

### 2019-03-21 cse517/report/main.tex
Finished DA section.

@@
 \usepackage{booktabs}
+\usepackage{bm}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 \begin{abstract}
-This project explores methods for improving performance on the task of natural language inference by incorporating syntactic information.
-Specifically we modify the decomposable attention neural network \citep{Parikh2016-em} by incorporating encoded syntax parses of the input statements at different layers of the network.
-We supplement these experiments by using different syntax parsers including pre-trained constituency and dependency parsers as well as a constituency parser trained separately for this task.
+We demonstrate the importance of syntactic information in semantic models by extending the
+decomposable attention model \citep{Parikh2016-em} for natural language inference
+to use syntactic features.
+By pipelining the hidden states of a neural syntax parser into the decomposable
+attention model, we achieve greater performance on the SciTail dataset
+\citep{Khot2018-th} than what is gained by
+using contextual embeddings like ELMo \citep{Peters2018-fz}.
 \end{abstract}
@@
 features into existing models.
-We will primarily investigate the well-known decomposable attention (DA) neural
-network \citep{Parikh2016-em}
 
@@
 between a pair of sequences---a premise and a hypothesis. An NLI model should
-predict whether the hyothesis is entailed by the premise, contradicts the
+predict whether the hypothesis is entailed by the premise, contradicts the
 premise, or is neutral to the premise.
@@
 We primarily
-evaluate on the domain specific Scitail \citep{Khot2018-th} for both its
-smaller size and lack of annotation artifacts when compared to SNLI
+evaluate on the domain specific Scitail dataset \citep{Khot2018-th}
+for both its smaller size and lack of annotation artifacts when compared to SNLI
 \citep{Gururangan2018-lj}.
 
-\section{Syntactic Entailment}
+Our model, \textbf{syntail}, achieves \dpcomment{add number here} better 
+test accuracy than the vanilla
+DA model and \dpcomment{add number here} better test accuracy than DA with ELMo all
+while maintaining the core DA architecture.
 
-In previous work, we created the syntail-v1 model whose architecture is shown
-in figure~\ref{figure:v1}.  We have obtained mixed results as shown in
-table~\ref{table:v1-accuracies} when naively incorporating syntactic
-information into the DA model.
+\section{Decomposable Attention Model}
 
-Without ELMo, syntail-v1 improves an impressive 8.4\% in test accuracy over the
-baseline decomposable attention model on the SciTail dataset. However, once
-ELMo is added to the model, almost the exact opposite occurs. Adding syntactic
-information decreases test accuracy by 6.7\% with ELMo.
+The DA model is a simple and easily parallelizable approach to NLI.
+We summarize it in this section so we can build upon it later.
+The model
+decomposes into attend, compare, and aggregate steps.
 
-\begin{table}[h]
-  \resizebox{0.45\textwidth}{!}{
-  \begin{tabular}{c c c c}
-    \toprule
-    Model & Embedding & Train Acc. & Test Acc. \\
-    \midrule
-    DA & GLoVe 6b 300d & 89.4\% & 70.1\% \\
-    \textbf{Syntail-v1} & \textbf{GLoVe 6b 300d} & \textbf{92.1\%}
-                        & \textbf{78.5\%} \\
-    DA & ELMo & 98.4\% & 78.0\% \\
-    \textbf{Syntail-v1} & \textbf{ELMo} & \textbf{88.8\%} & \textbf{71.3\%} \\
-    \bottomrule
-  \end{tabular}}
-  \caption{Syntail-v1 and DA model accuracies on the SciTail dataset.}
-\label{table:v1-accuracies}
-\end{table}
+Let
+$\bm{p} = \langle p_1, \dots, p_{\ell_p} \rangle$ and
+$\bm{h} = \langle h_1, \dots, h_{\ell_h} \rangle$ where each $p_i, h_i \in \mathbb{R}^d$
+is a $d$ dimensional word embedding vector.
 
-\section{Models}
+\paragraph{Attend.} Compute unnormalized attention weights $e_{ij}$ with
+a feed-forward neural network $F$:
+\begin{align}
+    e_{ij} := F(\bm{p})^\mathsf{T} F(\bm{h}).
+\end{align}
+Compute the aligned subphrases $\bm{H}i$ and $\bm{P}_j$:
+\begin{align}
+    \bm{H}_i &:= \sum_{j=1}^{\ell_h}\frac{\exp{(e_{ij})}}
+                                        {\sum_{k=1}^{\ell_h}\exp{(e_{ik})}}h_j\,, \notag \\
+    \bm{P}_j &:= \sum_{i=1}^{\ell_p}\frac{\exp{(e_{ij})}}
+                                        {\sum_{k=1}^{\ell_h}\exp{(e_{ik})}}p_i\
+\end{align}
+where $\bm{H}_i$ is the weighted sum over $\bm{h}$ that aligns to $p_i$ and vice versa
+for $\bm{P}_j$.
 
-The syntactic entailment model is derived from the decomposable attention model for natural language inference described by \citet{Parikh2016-em}.
-In the initial iteration of the network, syntax is not incorporated until the very last feed-forward layer.
-This means that syntax is not considered when calculating attention between the premise and the hypothesis.
-We speculated that by introducing syntax to the network prior to calculating attention we would see better results as the syntax would help influence the attention calculations and reveal the most important phrases of each input statement.
+\paragraph{Compare.} Compare each $(p_i, \bm{H}_i)$ and $(h_j, \bm{P_}j)$ pairs
+with another feed-forward neural network $G$:
+\begin{align}
+    \bm{v}_{1,i} &:= G([p_i, \bm{H}_i])\quad \forall i \in [1,\ldots, \ell_p]\,, \notag \\
+    \bm{v}_{2,j} &:= G([h_j, \bm{P}_j])\quad \forall j \in [1,\ldots, \ell_h]\,.
+\end{align}
 
-In the ``V3" model, we perform the same initial step of embedding the premise and hypothesis and expanding their dimensions (through a fully-connected layer) prior to attention.
-However, instead of calculating our similarity matrix using solely the embedded hypothesis and premise vectors as input, we also provide the encoded syntax parses of both inputs.
-The concatenation of these four vectors is used to derive the similarity matrix which is then utilized in the attention computations between the premise and hypothesis.
+\paragraph{Aggregate.} Aggregate each set of comparison vectors:
+\begin{align}
+\bm{v}_{1} = \sum_{i=1}^{\ell_p} \bm{v}_{1,i} \qquad\,, \qquad
+\bm{v}_{2} = \sum_{j=1}^{\ell_h}  \bm{v}_{2,j}\,.
+\end{align}
+and make a prediction with a final feed-forward layer $H$:
+\begin{align}
+    \hat{\bm{y}} = H([\bm{v}_1, \bm{v}_2]).
+\end{align}
 
-With the ``V5" model we tried to incorporate the computed syntax of the inputs even earlier.
-Instead of concatenating the encoded syntax parses with the embedded inputs and using that as input for the computation of the similarity matrix, we concatenated the syntax parses with their respective inputs and passed that through the first fully-connected layer.
-The two resulting vectors representing the embedded inputs with syntactic information are then used to compute the similarity matrix.
+\section{Our Model}
 
-Our ``V7" model took an additional step of learning weights for the encoded syntax parses by passing the vectors through an additional fully-connected layer before introducing them into the rest of the network.
-This model was built on top of the ``V3" model such that the weighted syntax parses are concatenated with the embedded premise and hypothesis statements when deriving the similarity matrix.
+The motivation for incorporating syntactic information in an NLI model
+can be demonstrated with a simple example. Consider the premise ``Adrian is running
+and Alex is swimming." If we present the DA model trained on SNLI with the
+hypothesis ``Adrian is swimming," it will confidently predict that this
+blatantly incorrect hypothesis is entailed by the premise. Observing
+any syntactic parse of
+the premise will make it obvious that Adrian is in fact running.
 
-Supplemental variations were done on top of these restructures of the network.
-One of the variations that we introduced was a retrained constituency parser.
-By retraining the constituency parser on the Penn Treebank dataset \citep{marcus1993building} we could change the dimensions of the encoded syntax vectors to better fit with our models.
-Additionally, we experimented with training our models using the dependency parser model derived by \citet{dozat2016deep} to see if the different types of encoded parses influenced the performance of the network.
+Incorporating syntactic information in semantic tasks has been investigated
+before by \dpcomment{add references and discussion}.
 
-\section{Proposed Methods}
-\label{methods}
+Our model, \textbf{syntail}, extends the DA model.
+We experiment with features generated by two syntax parsers---the
+minimal span-based neural constituency parser \citep{Stern2017-co} and
+the deep biaffine attention model for dependency parsing \citep{Dozat2016-gs}. We also experiment
+with different methods of incorporating the syntactic features extracted
+from these parsers.
 
-We plan to use state-of-the-art constituency \citep{Stern2017-co} and
-dependency \citep{Dozat2016-gs} parsers to investigate if incorporating
-syntactic features improves the performance of the DA model. Additionally, we
-hope to understand how syntactic features interact with contextual word
-embeddings like ELMo \citep{Peters2018-fz} and BERT \citep{Devlin2018-qc} in a
-task like NLI. It is unclear from previous work whether contextual word
-embeddings benefit from additional syntactic information or if something like
-ELMo can already adequately capture this information.
+\subsection{Extracting Syntactic Information}
 
-We will first investigate different ways of incorporating syntactic
-information. \citet{Pang2018-syntail} use a constituency parser to obtain an
-encoding of the premise and hypothesis that is in the final fully-connected
-layer of the DA model. We believe that incorporating syntactic features earlier
-in the pipeline, especially before the premise and hypothesis are attended over
-one another, should improve performance.
+The minimal span-based neural constituency parser and the deep biaffine attention
+model for dependency parsing both encode the input sequence with an LSTM. Using
+this LSTM, we obtain
+syntactic features $\bm{s}_i$ for each index $i$ of the input. $\bm{s}_i$ is either
+the final hidden state $\bm{r}_i$ of the LSTM at index $i$ or a projected
+representation of $\bm{r}_i$.
 
-We will then investigate different model architectures under a multi-task
-training objective where the jointly learns to both parse and predict
-entailment relationships.
+In the initial 
+iteration of the network, syntax is not incorporated until the very last feed-forward 
+layer. This means that syntax is not considered when calculating attention between 
+the premise and the hypothesis. We speculated that by introducing syntax to the 
+network prior to calculating attention we would see better results as the syntax 
+would help influence the attention calculations and reveal the most important phrases 
+of each input statement.
 
-\begin{figure}[h]
-  \includegraphics[width=0.45\textwidth]{v1}
-  \caption{A simple method of incorporating syntax into the decomposable
-    attention model.}
-\label{figure:v1}
-\end{figure}
+In the ``V3" model, we perform the same initial step of embedding the premise and 
+hypothesis and expanding their dimensions (through a fully-connected layer) prior to 
+attention. However, instead of calculating our similarity matrix using solely the 
+embedded hypothesis and premise vectors as input, we also provide the encoded syntax 
+parses of both inputs. The concatenation of these four vectors is used to derive the 
+similarity matrix which is then utilized in the attention computations between the 
+premise and hypothesis. \jbcomment{Insert V3.jpg here?}
 
-\section{Expected Outcomes}
+With the ``V5" model we tried to incorporate the computed syntax of the inputs even 
+earlier. Instead of concatenating the encoded syntax parses with the embedded inputs 
+and using that as input for the computation of the similarity matrix, we concatenated 
+the syntax parses with their respective inputs and passed that through the first 
+fully-connected layer. The two resulting vectors representing the embedded inputs 
+with syntactic information are then used to compute the similarity matrix. \jbcomment{Insert V5.jpg here?}
 
-We will compare our models to the DA model as well as syntail-v1. We hope to
-evaluate our models on many diverse datasets as stated in section
-~\ref{methods}.
+Our ``V7" model took an additional step of learning weights for the encoded syntax 
+parses by passing the vectors through an additional fully-connected layer before 
+introducing them into the rest of the network. This model was built on top of the 
+``V3" model such that the weighted syntax parses are concatenated with the embedded 
+premise and hypothesis statements when deriving the similarity matrix. \jbcomment{Insert V7.jpg here?}
 
-We expect that one of our modeling ideas will produce results that improve on
-the DA and syntail-v1 models. In the best case, we will show that syntax is
-crucial to building an accurate NLI system.
+\jbcomment{If we're only using data from the dependency parser we should probably 
+remove the section following this comment}
+Supplemental variations were done on top of these restructures of the network. One 
+of the variations that we introduced was a retrained constituency parser. By 
+retraining the constituency parser on the Penn Treebank dataset \citep{marcus1993building} 
+we could change the dimensions of the encoded syntax vectors to better fit with our models. 
+Additionally, we experimented with training our models using the dependency parser model 
+derived by \citet{dozat2016deep} to see if the different types of encoded parses influenced 
+the performance of the network.
 
-\section{Challenges}
+\section{Experiments}
 
-The first challenge involved in our project will be to modify syntail-v1
-so that syntactic information is incorporated much earlier. It will also take
-significant time to investigate the best parsers to use for our model.
-After, we will write a new model under a multi-task training setup, which we
-anticipate will be a significant implementation challenge.
+% \begin{figure}[h]
+%   \includegraphics[width=0.45\textwidth]{v1}
+%   \caption{A simple method of incorporating syntax into the decomposable
+%     attention model.}
+% \label{figure:v1}
+% \end{figure}
 
-We expect to require significant compute power and time to adequately fine-tune
-and evaluate our models. Contextual word embeddings are especially costly to
-train, and the mixing ratio in a multi-task setup is well-known to be
-difficult to tune.
+\section{Related Work}
+
+\section{Conclusion}
 

### 2019-03-21 cse517/report/main.tex
v1 done

@@
 \begin{align}
-    \bm{v}_{1,i} &:= G([p_i, \bm{H}_i])\quad \forall i \in [1,\ldots, \ell_p]\,, \notag \\
-    \bm{v}_{2,j} &:= G([h_j, \bm{P}_j])\quad \forall j \in [1,\ldots, \ell_h]\,.
+    \bm{v}^p_i &:= G([p_i, \bm{H}_i])\quad \forall i \in [1,\ldots, \ell_p]\,, \notag \\
+    \bm{v}^h_j &:= G([h_j, \bm{P}_j])\quad \forall j \in [1,\ldots, \ell_h]\,.
 \end{align}
@@
 \begin{align}
-\bm{v}_{1} = \sum_{i=1}^{\ell_p} \bm{v}_{1,i} \qquad\,, \qquad
-\bm{v}_{2} = \sum_{j=1}^{\ell_h}  \bm{v}_{2,j}\,.
+\bm{v}^p = \sum_{i=1}^{\ell_p} \bm{v}^p_i \qquad\,, \qquad
+\bm{v}^h = \sum_{j=1}^{\ell_h}  \bm{v}^h_j\,.
 \end{align}
 and make a prediction with a final feed-forward layer $H$:
-\begin{align}
-    \hat{\bm{y}} = H([\bm{v}_1, \bm{v}_2]).
+\begin{align}\label{eq:predict}
+    \hat{\bm{y}} = H([\bm{v}^p, \bm{v}^h]).
 \end{align}
@@
 this LSTM, we obtain
-syntactic features $\bm{s}_i$ for each index $i$ of the input. $\bm{s}_i$ is either
+syntactic features $\bm{s}^p = \langle s^p_1, \dots, s^p_{\ell_p} \rangle$ and
+$\bm{s}^h = \langle s^h_1, \dots, s^h_{\ell_h} \rangle$ from the premise and hypothesis,
+respectively. An $s_i$ is either
 the final hidden state $\bm{r}_i$ of the LSTM at index $i$ or a projected
@@
 
-In the initial 
-iteration of the network, syntax is not incorporated until the very last feed-forward 
-layer. This means that syntax is not considered when calculating attention between 
-the premise and the hypothesis. We speculated that by introducing syntax to the 
-network prior to calculating attention we would see better results as the syntax 
-would help influence the attention calculations and reveal the most important phrases 
-of each input statement.
+\subsection{Syntail Architectures}
 
+We will now describe the different model architectures we experimented with.
+In general, as the version number increases the complexity of the model will increase.
+
+\paragraph{v1: Naive late fusion of syntactic features.}
+The simplest way to incorporate $\bm{s}$ is to concatenate its final representation to
+$\bm{v}^p$ and $\bm{v}^h$ as shown in figure~\ref{fig:v1}.
+The prediction step in equation~\ref{eq:predict} then becomes:
+\begin{align}
+    \hat{\bm{y}} = H([\bm{v}^p, s^p_{\ell_p}, \bm{v}^h, s^h_{\ell_h}]).
+\end{align}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/v1.png}
+    \caption{Syntail v1 architecture.}
+\label{fig:v1}
+\end{figure}
+
+\paragraph{v2: Using syntactic features to attend.}
 In the ``V3" model, we perform the same initial step of embedding the premise and 
@@
 Additionally, we experimented with training our models using the dependency parser model 
-derived by \citet{dozat2016deep} to see if the different types of encoded parses influenced 
+derived by \citet{Dozat2016-gs} to see if the different types of encoded parses influenced 
 the performance of the network.

### 2019-03-21 cse517/report/main.tex
Starting experiments section.

@@
 \usepackage{amsmath}
+\usepackage{multirow}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 The DA model is a simple and easily parallelizable approach to NLI.
-We summarize it in this section so we can build upon it later.
+We summarize it here so we can build upon it later.
 The model
@@
 a feed-forward neural network $F$:
-\begin{align}
-    e_{ij} := F(\bm{p})^\mathsf{T} F(\bm{h}).
+\begin{align}\label{eq:attend}
+    e_{ij} := F(p_i)^\mathsf{T} F(h_j).
 \end{align}
@@
 We will now describe the different model architectures we experimented with.
-In general, as the version number increases the complexity of the model will increase.
+In general, as the version number increases, the complexity of the model increases.
 
@@
 $\bm{v}^p$ and $\bm{v}^h$ as shown in figure~\ref{fig:v1}.
-The prediction step in equation~\ref{eq:predict} then becomes:
-\begin{align}
-    \hat{\bm{y}} = H([\bm{v}^p, s^p_{\ell_p}, \bm{v}^h, s^h_{\ell_h}]).
-\end{align}
 
@@
 
+The prediction step in equation~\ref{eq:predict} then becomes:
+\begin{align}
+    \hat{\bm{y}} = H([\bm{v}^p, s^p_{\ell_p}, \bm{v}^h, s^h_{\ell_h}])
+\end{align}
+where we concatenate the final hidden representation of the premise and hypothesis
+when passed through the neural syntax parser with the aggregrated comparision vectors.
+Everything else is identical to the DA model.
+
 \paragraph{v2: Using syntactic features to attend.}
-In the ``V3" model, we perform the same initial step of embedding the premise and 
-hypothesis and expanding their dimensions (through a fully-connected layer) prior to 
-attention. However, instead of calculating our similarity matrix using solely the 
-embedded hypothesis and premise vectors as input, we also provide the encoded syntax 
-parses of both inputs. The concatenation of these four vectors is used to derive the 
-similarity matrix which is then utilized in the attention computations between the 
-premise and hypothesis. \jbcomment{Insert V3.jpg here?}
+We wanted to experiment with incorporating syntactic features earlier in the model.
+Instead of learning weights on the syntactic features, it is possible to
+concatenate them to the projected input representations as show in figure~\ref{fig:v2}.
 
-With the ``V5" model we tried to incorporate the computed syntax of the inputs even 
-earlier. Instead of concatenating the encoded syntax parses with the embedded inputs 
-and using that as input for the computation of the similarity matrix, we concatenated 
-the syntax parses with their respective inputs and passed that through the first 
-fully-connected layer. The two resulting vectors representing the embedded inputs 
-with syntactic information are then used to compute the similarity matrix. \jbcomment{Insert V5.jpg here?}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/v2.png}
+    \caption{Syntail v2 architecture.}
+\label{fig:v2}
+\end{figure}
 
-Our ``V7" model took an additional step of learning weights for the encoded syntax 
-parses by passing the vectors through an additional fully-connected layer before 
-introducing them into the rest of the network. This model was built on top of the 
-``V3" model such that the weighted syntax parses are concatenated with the embedded 
-premise and hypothesis statements when deriving the similarity matrix. \jbcomment{Insert V7.jpg here?}
+Computing the
+unnormalized attention weights in equation~\ref{eq:attend} then becomes:
+\begin{align}
+    e_{ij} := [F(p_i), s^p_i]^\mathsf{T} [F(h_j), s^h_i]
+\end{align}
+where instead of calculating the alignment using only the 
+projected hypothesis and premise vectors, we now also use final hidden states of
+the premise and hypothesis when passed through the neural syntax parser.
+This seems rather naive since this model will not
+learn any weights on the syntactic features, but in practice this model
+performs very well. Everything else is identical to the DA model.
 
-\jbcomment{If we're only using data from the dependency parser we should probably 
-remove the section following this comment}
-Supplemental variations were done on top of these restructures of the network. One 
-of the variations that we introduced was a retrained constituency parser. By 
-retraining the constituency parser on the Penn Treebank dataset \citep{marcus1993building} 
-we could change the dimensions of the encoded syntax vectors to better fit with our models. 
-Additionally, we experimented with training our models using the dependency parser model 
-derived by \citet{Dozat2016-gs} to see if the different types of encoded parses influenced 
-the performance of the network.
+\paragraph{v3: Using syntactic features to project the premise and hypothesis.}
+We decided to try incorporating the syntactic features even earlier in the model.
+Instead of concatenating the final hidden states of the parsed premise and hypothesis
+with the projected inputs, we concatenate the final hidden states of the parsed
+premise and hypothesis with in the inputs immediately before projecting them. This
+architecture is shown in figure~\ref{fig:v3}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/v3.png}
+    \caption{Syntail v3 architecture.}
+\label{fig:v3}
+\end{figure}
+
+Computing the unnormalized attention weights in equation~\ref{eq:attend} then becomes:
+\begin{align}
+    e_{ij} := F([p_i, s^p_i])^\mathsf{T} F([h_j, s^h_j]).
+\end{align}
+Everything else is identical to the DA model.
+
+\paragraph{v4: Projecting the syntactic features before computing attention.}
+After noticing a drop in performance from v2 to v3, we hypothesized that it was
+due to not allowing our model to transform the syntactic features enough before
+calculating attention.
+We decided to learn weights to project the final hidden states of the parsed
+premise and hypothesis by passing them through an additional fully-connected layer before 
+concatenating them to the inputs. This architecture is shown in figure~\ref{fig:v4}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/v4.png}
+    \caption{Syntail v4 architecture.}
+\label{fig:v4}
+\end{figure}
+
+Computing the unnormalized attention weights in equation~\ref{eq:attend} then becomes:
+\begin{align}
+    e_{ij} := F([p_i, J(s^p_i)])^\mathsf{T} F([h_j, J(s^h_j)])
+\end{align}
+where $J$ is a feed-forward neural network.
+Everything else is identical to the DA model.
+
+% \jbcomment{If we're only using data from the dependency parser we should probably 
+% remove the section following this comment}
+% Supplemental variations were done on top of these restructures of the network. One 
+% of the variations that we introduced was a retrained constituency parser. By 
+% retraining the constituency parser on the Penn Treebank dataset \citep{marcus1993building} 
+% we could change the dimensions of the encoded syntax vectors to better fit with our models. 
+% Additionally, we experimented with training our models using the dependency parser model 
+% derived by \citet{Dozat2016-gs} to see if the different types of encoded parses influenced 
+% the performance of the network.
+
+\subsection{Implementation Details}
+\dpcomment{Add some hyper-parameter stuff here.}
 
@@
 
-% \begin{figure}[h]
-%   \includegraphics[width=0.45\textwidth]{v1}
-%   \caption{A simple method of incorporating syntax into the decomposable
-%     attention model.}
-% \label{figure:v1}
-% \end{figure}
+We compare our model's performance to the decomposable attention model
+\citep{Parikh2016-em} and the ESIM model \citep{Chen2016-wl}.
+
+\begin{table}[h]
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{cccccc} 
+\toprule
+Model          & Embeddings      & Dev. Acc. & Test Acc.  \\ 
+\midrule
+Majority Class & n/a             & 63.3      & 60.3       \\
+N-Gram         & n/a             & 65.0      & 70.6       \\
+ESIM           & GloVe 840B 300d & 70.5      & 70.6       \\
+DA             & GloVe 6B 300d   & 70.4      & 72.6       \\
+DA             & ELMo            & 79.1      & 75.5       \\
+\midrule
+Syntail v2     & GloVe 6B 300d   & 79.3      & ?          \\
+Syntail v3     & GloVe 6B 300d   & 82.3      & 77.4       \\
+Syntail v5     & GloVe 6B 300d   & ?         & ?          \\
+Syntail v7     & GloVe 6B 300d   & 81.3      & 77.0       \\
+\bottomrule
+\end{tabular}}
+\label{table:experiments}
+\caption{\dpcomment{think of a good caption, fix the version numbers}}
+\end{table}
+
+\subsection{Datasets}
+For practical reasons, we only ran experiments on the SciTail dataset. SciTail (27k pairs) is
+significantly smaller than SNLI (570k pairs) \citep{Bowman2015-is} or MultiNLI (433k pairs)
+\citep{Williams2017-uh} which made it feasible to try many different architectures given
+our limited resources.
+
+Additionally, \citet{Gururangan2018-lj} showed that SNLI and MultiNLI
+have significant annotation artifacts whereas SciTail is the first entailment set to be
+completely derived from sentences that exist ``in the wild.''
+
+\subsection{Baselines}
+
+We list baseline performance reported by \citet{Khot2018-th} of a majority class predictor,
+n-gram model, and ESIM \citep{Chen2016-wl} in table~\ref{table:experiments}. We reimplemented
+and retrained the DA model and obtained similar test accuracies as reported by \citep{Chen2016-wl}.
+Adding ELMo to the DA model improved test accuracy performance by approximately 3\%.
 

### 2019-03-22 scripts/visualize_attention.py
Neat little script.

@@ -1,0 +1,97 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+# sphinx_gallery_thumbnail_number = 2
+
+premise = ['The', 'continental', 'crust', 'is', 'less', 'dense', 'than', 'the',
+           'mantle', 'but', 'the', 'oceanic', 'crust', 'is', 'not', '.']
+hypothesis = ['The', 'oceanic', 'crust', 'is', 'more', 'dense', 'than', 'the',
+              'mantle', '.']
+
+da_h_to_p_attention = np.array([[4.82274487170619e-31, 0.0, 0.0, 0.5, 0.0, 0.0, 2.249963411057046e-33, 4.82274487170619e-31, 0.0, 1.2182965674626343e-25, 4.82274487170619e-31, 0.0, 0.0, 0.5, 2.07386546381683e-23, 3.14171115701624e-42, 0.0], [1.0864135219890159e-05, 1.192428933372014e-10, 5.1575903270428824e-11, 0.4999181032180786, 1.2316784259169822e-09, 1.4314088803146774e-10, 3.3572175652807346e-06, 1.0864135219890159e-05, 1.2702144024101525e-12, 5.9762784076156095e-05, 1.0864135219890159e-05, 2.6359754765233057e-13, 5.1575903270428824e-11, 0.4999181032180786, 6.79257937008515e-05, 1.4062736397590925e-07, 1.7427893472170362e-16], [1.3339535639284028e-12, 1.2797187566573396e-25, 7.008032219919717e-25, 0.5, 3.403934174939942e-23, 1.3878776018275426e-24, 6.238813549705024e-15, 1.3339535639284028e-12, 9.828032543270217e-30, 2.5479462290034505e-12, 1.3339535639284028e-12, 6.576626291827393e-35, 7.008032219919717e-25, 0.5, 2.915791913471466e-11, 6.513164308551193e-19, 6.25976279076082e-39], [0.0, 0.0, 0.0, 0.5, 0.0, 0.0, 0.0, 0.0, 0.0, 3.1974458416169094e-37, 0.0, 0.0, 0.0, 0.5, 1.3212126713120492e-33, 0.0, 0.0], [7.996040537217079e-32, 0.0, 0.0, 0.5, 0.0, 0.0, 2.457502595761284e-30, 7.996040537217079e-32, 0.0, 2.5083161554355187e-22, 7.996040537217079e-32, 0.0, 
[…]

### 2019-03-22 cse517/report/main.tex
Submitting!

@@
 We demonstrate the importance of syntactic information in semantic models by extending the
-decomposable attention model \citep{Parikh2016-em} for natural language inference
-to use syntactic features.
+decomposable attention model for natural language inference.
 By pipelining the hidden states of a neural syntax parser into the decomposable
 attention model, we achieve greater performance on the SciTail dataset
-\citep{Khot2018-th} than what is gained by
-using contextual embeddings like ELMo \citep{Peters2018-fz}.
+than the ESIM model and DA + ELMo.
 \end{abstract}
@@
 Natural language inference (NLI) is the task of characterizing entailment and
-contradiction relationships between texts. We improve NLI models by adding syntactic
-features into existing models.
-
+contradiction relationships between texts.
 In general, most NLI tasks are formulated as characterizing the relationship
@@
 incorporating syntactic features.
-\dpcomment{Include brief summary of contributions here.}
 The DA model obtained state-of-the-art results on the
@@
 We primarily
-evaluate on the domain specific Scitail dataset \citep{Khot2018-th}
+evaluate on the domain-specific SciTail dataset \citep{Khot2018-th}
 for both its smaller size and lack of annotation artifacts when compared to SNLI
@@
 
-Our model, \textbf{syntail}, achieves \dpcomment{add number here} better 
+Our model, \texttt{syntail}, achieves 4.8\% better 
 test accuracy than the vanilla
-DA model and \dpcomment{add number here} better test accuracy than DA with ELMo all
-while maintaining the core DA architecture.
+DA model and 1.9\% better test accuracy than DA with ELMo \citep{Peters2018-fz}
+all while maintaining the core DA architecture.
 
@@
 $\bm{p} = \langle p_1, \dots, p_{\ell_p} \rangle$ and
-$\bm{h} = \langle h_1, \dots, h_{\ell_h} \rangle$ where each $p_i, h_i \in \mathbb{R}^d$
-is a $d$ dimensional word embedding vector.
+$\bm{h} = \langle h_1, \dots, h_{\ell_h} \rangle$ where each $p_i, h_j \in \mathbb{R}^d$
+is a $d$-dimensional word embedding vector.
 
@@
 
-Incorporating syntactic information in semantic tasks has been investigated
-before by \dpcomment{add references and discussion}.
-
-Our model, \textbf{syntail}, extends the DA model.
-We experiment with features generated by two syntax parsers---the
+We experiment with features produced by two syntax parsers---the
 minimal span-based neural constituency parser \citep{Stern2017-co} and
@@
 where instead of calculating the alignment using only the 
-projected hypothesis and premise vectors, we now also use final hidden states of
+projected hypothesis and premise vectors, we now also use the final hidden states of
 the premise and hypothesis when passed through the neural syntax parser.
@@
 with the projected inputs, we concatenate the final hidden states of the parsed
-premise and hypothesis with in the inputs immediately before projecting them. This
+premise and hypothesis with the inputs immediately before projecting them. This
 architecture is shown in figure~\ref{fig:v3}.
@@
 \subsection{Implementation Details}
-\dpcomment{Add some hyper-parameter stuff here.}
+
+\subsubsection{Word Embeddings}
+
+Due to resource constraints, we limited our models to only use 300-dimensional
+6B GloVe word embeddings \citep{Pennington2014-uo}.
+Additionally, contextual embeddings are known to capture syntax in some capacity,
+so limiting our models to only use GloVe vectors
+made it easier to experiment with the syntactic features in isolation.
+
+\subsubsection{Neural Syntax Parser}
+
+We initially used a constituency parser in syntail. However,
+after some experimentation, we found that we were achieving better results
+with a dependency parser.
+For this reason, we only report results using the deep biaffine attention
+model for dependency parsing.
+Dependency parsers focus on encoding the
+the relationships between words as opposed to determining constituents.
+Intuitively, if we consider our example sentence, ``Adrian is running and Alex is swimming,''
+the dependency arcs will be more informative of who is doing what.
+
+\subsection{Hyper-parameters}
+
+We use 200-dimensional projections of the word embeddings. Our feed-forward neural
+networks are 2 layered and have hidden dimensions of 200. We train with both
+Adam \citep{kingma2014adam} and Adagrad \citep{duchi2011adaptive} and report the
+better result.
 
@@
 \citep{Parikh2016-em} and the ESIM model \citep{Chen2016-wl}.
+Early on in our experiments, we noticed that features from a dependency
+parser seemed to perform better than those from a constituency parser.
+Therefore, all of our models use the deep biaffine attention model for
+dependency parsing \citep{Dozat2016-gs}.
+
+\paragraph{Datasets.}
+For practical reasons, we only experiment on the SciTail dataset. SciTail (27k pairs) is
+significantly smaller than SNLI (570k pairs) \citep{Bowman2015-is} or MultiNLI (433k pairs)
+\citep{Williams2017-uh} which makes it feasible to try many different
+architectures given limited resources.
+
+Additionally, \citet{Gururangan2018-lj} showed that SNLI and MultiNLI
+have significant annotation artifacts whereas SciTail is the first entailment set to be
+completely derived from sentences that exist ``in the wild.''
+
+\paragraph{Baselines.}
+We list baseline performance reported by \citet{Khot2018-th} of a majority class predictor,
+n-gram model, and ESIM \citep{Chen2016-wl} in table~\ref{table:experiments}. We reimplemented
+and retrained the DA model and obtained similar test accuracies as reported by \citet{Chen2016-wl}.
+Adding ELMo to the DA model improved test accuracy performance by approximately 3\%.
+
+\subsection{Results}
 
@@
 \midrule
-Syntail v2     & GloVe 6B 300d   & 79.3      & ?          \\
-Syntail v3     & GloVe 6B 300d   & 82.3      & 77.4       \\
-Syntail v5     & GloVe 6B 300d   & ?         & ?          \\
-Syntail v7     & GloVe 6B 300d   & 81.3      & 77.0       \\
+Syntail v1     & GloVe 6B 300d   & 78.4      & \textbf{77.4}       \\
+Syntail v2     & GloVe 6B 300d   & \textbf{82.3}      & \textbf{77.4}       \\
+Syntail v3     & GloVe 6B 300d   & 79.0         & 76.1          \\
+Syntail v4     & GloVe 6B 300d   & 81.3      & 77.0       \\
 \bottomrule
 \end{tabular}}
+\caption{Dev and test accuracies on SciTail.}
 \label{table:experiments}
-\caption{\dpcomment{think of a good caption, fix the version numbers}}
 \end{table}
 
-\subsection{Datasets}
-For practical reasons, we only ran experiments on the SciTail dataset. SciTail (27k pairs) is
-significantly smaller than SNLI (570k pairs) \citep{Bowman2015-is} or MultiNLI (433k pairs)
-\citep{Williams2017-uh} which made it feasible to try many different architectures given
-our limited resources.
+Our experimental results can be found in table~\ref{table:experiments}.
+All of our syntail models
+achieve better test accuracy than the baseline models. This demonstrates
+that the syntax parser is providing features that are both useful for
+determining entailment relationships and difficult for the baseline
+models to learn on their own.
 
-Additionally, \citet{Gururangan2018-lj} showed that SNLI and MultiNLI
-have significant annotation artifacts whereas SciTail is the first entailment set to be
-completely derived from sentences that exist ``in the wild.''
+We were surprised that the simpler v1 and v2 models outperformed the
+more complicated v3 and v4 models. This is likely due to the syntactic
+information being fused later in v1 and v2. The later the features are
+fused, the closer they are to the loss function and the more the model
+can learn to use them.
 
-\subsection{Baselines}
+It is also interesting that adding and additional transformation
+on the syntactic features in v4 decreases performance.
+Again, this is likely due to the early fusion problem.
+The additional power of the model is overwhelmed by the detrimental
+effects of the vanishing gradient problem.
+It is also possible that the randomly initialized weights 
+of the feed-forward neural network struggle to learn how to
+summarize the syntactic features.
 
-We list baseline performance reported by \citet{Khot2018-th} of a majority class predictor,
-n-gram model, and ESIM \citep{Chen2016-wl} in table~\ref{table:experiments}. We reimplemented
-and retrained the DA model and obtained similar test accuracies as reported by \citep{Chen2016-wl}.
-Adding ELMo to the DA model improved test accuracy performance by approximately 3\%.
+One downside of using a pretrained syntax parser is that the data SciTail is
+created from (science exam questions) is in a very different domain than
+the data used to create the Penn Treebank (news articles)
+\citep{marcus1993building}.
+This likely significantly reduces the accuracy of the syntax parser on
+SciTail. Retraining the syntax parser on in-domain data
+should produce better syntactic features
+and further improve 
+the performance of our model.
+
+\subsection{Analysis of Syntactic Features}
+
+We discuss a specific in-domain input example shown in table~\ref{table:example}
+to better understand the effects of syntactic features. The predictions on this
+input made by the DA and
+syntail v1 models are shown in table~\ref{table:pred-example}.
+
+\begin{table*}[t]
+    \centering
+    \resizebox{\linewidth}{!}{
+    \begin{tabular}{c c}
+    \toprule
+    Premise & Hypothesis \\
+    \midrule
+    The continental crust is less dense than the mantle but the oceanic crust is not.
+        & The oceanic crust is more dense than the mantle. \\
+    \bottomrule
+    \end{tabular}}
+    \caption{A pair of sentences where syntail performs particularly well. The hypothesis is
+             entailed by the premise.}
+\label{table:example}
+\end{table*}
+
+\begin{table}[h]
+    \centering
+    \begin{tabular}{c c c}
+        \toprule
+         Model & Entails (correct) \\
+         \midrule
+         DA & 29.5\% \\
+         Syntail v1 & \textbf{67.9\%} \\
+         \bottomrule
+    \end{tabular}
+    \caption{Entailment probabilities generated by the DA and syntail v1 models on the input
+             from table~\ref{table:example}.}
+\label{table:pred-example}
+\end{table}
+
+Syntail v1 correctly determines the relationship of this pair of sentences
+while the DA model does not.
+To investigate why, we visualize the attention weights in figures~\ref{fig:da-attention-weights}
+and \ref{fig:sytail-attention-weights}.
+We can see that the attention produced by the DA model is nonsensical and focuses solely on
+``is.'' It seems that by incorporating syntactic information, syntail v1 is forced to learn
+a more reliable attention function.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/da-h2p-attention.png}
+    \caption{Hypothesis to premise attention weights of the DA model when processing
+             the input from tabel~\ref{table:example}.}
+    \label{fig:da-attention-weights}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/syntail-h2p-attention.png}
+    \caption{Hypothesis to premise attention weights of syntail v1 when processing
+             the input from tabel~\ref{table:example}.}
+    \label{fig:sytail-attention-weights}
+\end{figure}
 
@@
 
+Previous works have experimented with incorporating syntactic features for semantic tasks.
+\citet{Chen2016-wl} use tree structures generated by a constituency parser to improve
+their ESIM model. They encode the phrase-structure trees with a Tree-LSTM and use its
+hidden states. \citet{Khot2018-th} incorporate syntactic features by
+proposing a model architecture which can use any graph-based syntactic/semantic structure.
+
+Other works have experimented with incorporating syntactic learning objectives.
+\citet{Strubell2018-qw} achieved state-of-the-art performance
+for a model using predicted predicates and standard word embeddings on
+CoNLL-2005 SRL by performing multi-task training on additional syntactic tasks.
+\citet{Swayamdipta2017-ct} use hard-coded constituency and dependency parse features
+and a syntactic scaffold to
+extend softmax margin segmental RNN (segRNN) model.
+
 \section{Conclusion}
+
+By making simple extensions to the DA model,
+our syntail models outperform ESIM and DA + ELMo model on SciTail.
+Our results demonstrate the importance of syntactic information in semantic models
+and motivate future research into syntactically informed models.
 

### 2019-03-22 cse517/report/main.tex
Minor spelling/syntax changes.

@@
 
-We extend the decomposable attention (DA) model by \citet{Parikh2016-em}
+We extend the decomposable attention (DA) model from  \citet{Parikh2016-em} by
 incorporating syntactic features.
@@
     \caption{Hypothesis to premise attention weights of the DA model when processing
-             the input from tabel~\ref{table:example}.}
+             the input from table~\ref{table:example}.}
     \label{fig:da-attention-weights}
@@
     \caption{Hypothesis to premise attention weights of syntail v1 when processing
-             the input from tabel~\ref{table:example}.}
+             the input from table~\ref{table:example}.}
     \label{fig:sytail-attention-weights}
@@
 and a syntactic scaffold to
-extend softmax margin segmental RNN (segRNN) model.
+extend the softmax margin segmental RNN (segRNN) model.
 

### 2019-03-26 paper/main.tex
Updating paper with 517 report.

--- 2019-02-08 paper/main.tex
@@
 \usepackage{latexsym}
-
 \usepackage{url}
-
-% user packages
 \usepackage{graphicx}
-\graphicspath{{figures/}}
 \usepackage{booktabs}
+\usepackage{bm}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{multirow}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
 \aclfinalcopy % Uncomment this line for the final submission
+%\def\aclpaperid{***} %  Enter the acl Paper ID here
 
@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
-\newcommand\confname{EMNLP 2018}
-\newcommand\conforg{SIGDAT}
 
-\title{Instructions for \confname{} Proceedings}
+\newcommand{\dpcomment}[1]{\textcolor{green}{[#1 --deric]}}
+\newcommand{\jbcomment}[1]{\textcolor{orange}{[#1 --josh]}}
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+\title{Syntactically Informed Natural Language Inference}
+
+\author{
+  Deric Pang \quad
+  Joshua Bean \\
+  Paul G. Allen School of Computer Science \& Engineering \\
+  University of Washington \\
+  Seattle, WA, USA \\
+  {\tt \{dericp, jbean96\}@cs.washington.edu} \\
+}
 
@@
 \begin{abstract}
-  Abstract.
+We demonstrate the importance of syntactic information in semantic models by extending the
+decomposable attention model for natural language inference.
+By pipelining the hidden states of a neural syntax parser into the decomposable
+attention model, we achieve greater performance on the SciTail dataset
+than the ESIM model and DA + ELMo.
 \end{abstract}
@@
 Natural language inference (NLI) is the task of characterizing entailment and
-contradiction relationships between texts.  We seek to improve models which
-perform NLI by adding syntactic features into existing models. In particular,
-we will primarily investigate the well-known decomposable attention (DA) neural
-network \citep{Parikh2016-em} which obtained state of the art results on the
+contradiction relationships between texts.
+In general, most NLI tasks are formulated as characterizing the relationship
+between a pair of sequences---a premise and a hypothesis. An NLI model should
+predict whether the hypothesis is entailed by the premise, contradicts the
+premise, or is neutral to the premise.
+
+We extend the decomposable attention (DA) model from  \citet{Parikh2016-em} by
+incorporating syntactic features.
+The DA model obtained state-of-the-art results on the
 SNLI \citep{Bowman2015-is} dataset at its time of publication while using
 drastically fewer parameters than previous NLI models.
+We primarily
+evaluate on the domain-specific SciTail dataset \citep{Khot2018-th}
+for both its smaller size and lack of annotation artifacts when compared to SNLI
+\citep{Gururangan2018-lj}.
 
-We intend to extend the DA model and evaluate new models on SNLI, MultiNLI
-\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
-\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
-\citep{Khot2018-th}.
+Our model, \texttt{syntail}, achieves 4.8\% better 
+test accuracy than the vanilla
+DA model and 1.9\% better test accuracy than DA with ELMo \citep{Peters2018-fz}
+all while maintaining the core DA architecture.
 
-In general, most NLI tasks are formulated as characterizing the relationship
-between a pair of sequences---a premise and a hypothesis. An NLI model should
-predict whether the hyothesis is entailed by the premise, contradicts the
-premise, or is neutral to the premise.
+\section{Decomposable Attention Model}
 
-\section{Previous Work}
+The DA model is a simple and easily parallelizable approach to NLI.
+We summarize it here so we can build upon it later.
+The model
+decomposes into attend, compare, and aggregate steps.
 
-Our project will build on previous work done by \citet{Pang2018-syntail}.
+Let
+$\bm{p} = \langle p_1, \dots, p_{\ell_p} \rangle$ and
+$\bm{h} = \langle h_1, \dots, h_{\ell_h} \rangle$ where each $p_i, h_j \in \mathbb{R}^d$
+is a $d$-dimensional word embedding vector.
 
-In previous work, we created the syntail-v1 model whose architecture is shown
-in figure~\ref{figure:v1}.  We have obtained mixed results as shown in
-table~\ref{table:v1-accuracies} when naively incorporating syntactic
-information into the DA model.
+\paragraph{Attend.} Compute unnormalized attention weights $e_{ij}$ with
+a feed-forward neural network $F$:
+\begin{align}\label{eq:attend}
+    e_{ij} := F(p_i)^\mathsf{T} F(h_j).
+\end{align}
+Compute the aligned subphrases $\bm{H}i$ and $\bm{P}_j$:
+\begin{align}
+    \bm{H}_i &:= \sum_{j=1}^{\ell_h}\frac{\exp{(e_{ij})}}
+                                        {\sum_{k=1}^{\ell_h}\exp{(e_{ik})}}h_j\,, \notag \\
+    \bm{P}_j &:= \sum_{i=1}^{\ell_p}\frac{\exp{(e_{ij})}}
+                                        {\sum_{k=1}^{\ell_h}\exp{(e_{ik})}}p_i\
+\end{align}
+where $\bm{H}_i$ is the weighted sum over $\bm{h}$ that aligns to $p_i$ and vice versa
+for $\bm{P}_j$.
 
-Without ELMo, syntail-v1 improves an impressive 8.4\% in test accuracy over the
-baseline decomposable attention model on the SciTail dataset. However, once
-ELMo is added to the model, almost the exact opposite occurs. Adding syntactic
-information decreases test accuracy by 6.7\% with ELMo.
+\paragraph{Compare.} Compare each $(p_i, \bm{H}_i)$ and $(h_j, \bm{P_}j)$ pairs
+with another feed-forward neural network $G$:
+\begin{align}
+    \bm{v}^p_i &:= G([p_i, \bm{H}_i])\quad \forall i \in [1,\ldots, \ell_p]\,, \notag \\
+    \bm{v}^h_j &:= G([h_j, \bm{P}_j])\quad \forall j \in [1,\ldots, \ell_h]\,.
+\end{align}
+
+\paragraph{Aggregate.} Aggregate each set of comparison vectors:
+\begin{align}
+\bm{v}^p = \sum_{i=1}^{\ell_p} \bm{v}^p_i \qquad\,, \qquad
+\bm{v}^h = \sum_{j=1}^{\ell_h}  \bm{v}^h_j\,.
+\end{align}
+and make a prediction with a final feed-forward layer $H$:
+\begin{align}\label{eq:predict}
+    \hat{\bm{y}} = H([\bm{v}^p, \bm{v}^h]).
+\end{align}
+
+\section{Our Model}
+
+The motivation for incorporating syntactic information in an NLI model
+can be demonstrated with a simple example. Consider the premise ``Adrian is running
+and Alex is swimming." If we present the DA model trained on SNLI with the
+hypothesis ``Adrian is swimming," it will confidently predict that this
+blatantly incorrect hypothesis is entailed by the premise. Observing
+any syntactic parse of
+the premise will make it obvious that Adrian is in fact running.
+
+We experiment with features produced by two syntax parsers---the
+minimal span-based neural constituency parser \citep{Stern2017-co} and
+the deep biaffine attention model for dependency parsing \citep{Dozat2016-gs}. We also experiment
+with different methods of incorporating the syntactic features extracted
+from these parsers.
+
+\subsection{Extracting Syntactic Information}
+
+The minimal span-based neural constituency parser and the deep biaffine attention
+model for dependency parsing both encode the input sequence with an LSTM. Using
+this LSTM, we obtain
+syntactic features $\bm{s}^p = \langle s^p_1, \dots, s^p_{\ell_p} \rangle$ and
+$\bm{s}^h = \langle s^h_1, \dots, s^h_{\ell_h} \rangle$ from the premise and hypothesis,
+respectively. An $s_i$ is either
+the final hidden state $\bm{r}_i$ of the LSTM at index $i$ or a projected
+representation of $\bm{r}_i$.
+
+\subsection{Syntail Architectures}
+
+We will now describe the different model architectures we experimented with.
+In general, as the version number increases, the complexity of the model increases.
+
+\paragraph{v1: Naive late fusion of syntactic features.}
+The simplest way to incorporate $\bm{s}$ is to concatenate its final representation to
+$\bm{v}^p$ and $\bm{v}^h$ as shown in figure~\ref{fig:v1}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/v1.png}
+    \caption{Syntail v1 architecture.}
+\label{fig:v1}
+\end{figure}
+
+The prediction step in equation~\ref{eq:predict} then becomes:
+\begin{align}
+    \hat{\bm{y}} = H([\bm{v}^p, s^p_{\ell_p}, \bm{v}^h, s^h_{\ell_h}])
+\end{align}
+where we concatenate the final hidden representation of the premise and hypothesis
+when passed through the neural syntax parser with the aggregrated comparision vectors.
+Everything else is identical to the DA model.
+
+\paragraph{v2: Using syntactic features to attend.}
+We wanted to experiment with incorporating syntactic features earlier in the model.
+Instead of learning weights on the syntactic features, it is possible to
+concatenate them to the projected input representations as show in figure~\ref{fig:v2}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/v2.png}
+    \caption{Syntail v2 architecture.}
+\label{fig:v2}
+\end{figure}
+
+Computing the
+unnormalized attention weights in equation~\ref{eq:attend} then becomes:
+\begin{align}
+    e_{ij} := [F(p_i), s^p_i]^\mathsf{T} [F(h_j), s^h_i]
+\end{align}
+where instead of calculating the alignment using only the 
+projected hypothesis and premise vectors, we now also use the final hidden states of
+the premise and hypothesis when passed through the neural syntax parser.
+This seems rather naive since this model will not
+learn any weights on the syntactic features, but in practice this model
+performs very well. Everything else is identical to the DA model.
+
+\paragraph{v3: Using syntactic features to project the premise and hypothesis.}
+We decided to try incorporating the syntactic features even earlier in the model.
+Instead of concatenating the final hidden states of the parsed premise and hypothesis
+with the projected inputs, we concatenate the final hidden states of the parsed
+premise and hypothesis with the inputs immediately before projecting them. This
+architecture is shown in figure~\ref{fig:v3}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/v3.png}
+    \caption{Syntail v3 architecture.}
+\label{fig:v3}
+\end{figure}
+
+Computing the unnormalized attention weights in equation~\ref{eq:attend} then becomes:
+\begin{align}
+    e_{ij} := F([p_i, s^p_i])^\mathsf{T} F([h_j, s^h_j]).
+\end{align}
+Everything else is identical to the DA model.
+
+\paragraph{v4: Projecting the syntactic features before computing attention.}
+After noticing a drop in performance from v2 to v3, we hypothesized that it was
+due to not allowing our model to transform the syntactic features enough before
+calculating attention.
+We decided to learn weights to project the final hidden states of the parsed
+premise and hypothesis by passing them through an additional fully-connected layer before 
+concatenating them to the inputs. This architecture is shown in figure~\ref{fig:v4}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/v4.png}
+    \caption{Syntail v4 architecture.}
+\label{fig:v4}
+\end{figure}
+
+Computing the unnormalized attention weights in equation~\ref{eq:attend} then becomes:
+\begin{align}
+    e_{ij} := F([p_i, J(s^p_i)])^\mathsf{T} F([h_j, J(s^h_j)])
+\end{align}
+where $J$ is a feed-forward neural network.
+Everything else is identical to the DA model.
+
+% \jbcomment{If we're only using data from the dependency parser we should probably 
+% remove the section following this comment}
+% Supplemental variations were done on top of these restructures of the network. One 
+% of the variations that we introduced was a retrained constituency parser. By 
+% retraining the constituency parser on the Penn Treebank dataset \citep{marcus1993building} 
+% we could change the dimensions of the encoded syntax vectors to better fit with our models. 
+% Additionally, we experimented with training our models using the dependency parser model 
+% derived by \citet{Dozat2016-gs} to see if the different types of encoded parses influenced 
+% the performance of the network.
+
+\subsection{Implementation Details}
+
+\subsubsection{Word Embeddings}
+
+Due to resource constraints, we limited our models to only use 300-dimensional
+6B GloVe word embeddings \citep{Pennington2014-uo}.
+Additionally, contextual embeddings are known to capture syntax in some capacity,
+so limiting our models to only use GloVe vectors
+made it easier to experiment with the syntactic features in isolation.
+
+\subsubsection{Neural Syntax Parser}
+
+We initially used a constituency parser in syntail. However,
+after some experimentation, we found that we were achieving better results
+with a dependency parser.
+For this reason, we only report results using the deep biaffine attention
+model for dependency parsing.
+Dependency parsers focus on encoding the
+the relationships between words as opposed to determining constituents.
+Intuitively, if we consider our example sentence, ``Adrian is running and Alex is swimming,''
+the dependency arcs will be more informative of who is doing what.
+
+\subsection{Hyper-parameters}
+
+We use 200-dimensional projections of the word embeddings. Our feed-forward neural
+networks are 2 layered and have hidden dimensions of 200. We train with both
+Adam \citep{kingma2014adam} and Adagrad \citep{duchi2011adaptive} and report the
+better result.
+
+\section{Experiments}
+
+We compare our model's performance to the decomposable attention model
+\citep{Parikh2016-em} and the ESIM model \citep{Chen2016-wl}.
+Early on in our experiments, we noticed that features from a dependency
+parser seemed to perform better than those from a constituency parser.
+Therefore, all of our models use the deep biaffine attention model for
+dependency parsing \citep{Dozat2016-gs}.
+
+\paragraph{Datasets.}
+For practical reasons, we only experiment on the SciTail dataset. SciTail (27k pairs) is
+significantly smaller than SNLI (570k pairs) \citep{Bowman2015-is} or MultiNLI (433k pairs)
+\citep{Williams2017-uh} which makes it feasible to try many different
+architectures given limited resources.
+
+Additionally, \citet{Gururangan2018-lj} showed that SNLI and MultiNLI
+have significant annotation artifacts whereas SciTail is the first entailment set to be
+completely derived from sentences that exist ``in the wild.''
+
+\paragraph{Baselines.}
+We list baseline performance reported by \citet{Khot2018-th} of a majority class predictor,
+n-gram model, and ESIM \citep{Chen2016-wl} in table~\ref{table:experiments}. We reimplemented
+and retrained the DA model and obtained similar test accuracies as reported by \citet{Chen2016-wl}.
+Adding ELMo to the DA model improved test accuracy performance by approximately 3\%.
+
+\subsection{Results}
 
 \begin{table}[h]
-  \resizebox{0.45\textwidth}{!}{
-  \begin{tabular}{c c c c}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{cccccc} 
 \toprule
-    Model & Embedding & Train Acc. & Test Acc. \\
+Model          & Embeddings      & Dev. Acc. & Test Acc.  \\ 
 \midrule
-    DA & GLoVe 6b 300d & 89.4\% & 70.1\% \\
-    \textbf{Syntail-v1} & \textbf{GLoVe 6b 300d} & \textbf{92.1\%}
-                        & \textbf{78.5\%} \\
-    DA & ELMo & 98.4\% & 78.0\% \\
-    \textbf{Syntail-v1} & \textbf{ELMo} & \textbf{88.8\%} & \textbf{71.3\%} \\
+Majority Class & n/a             & 63.3      & 60.3       \\
+N-Gram         & n/a             & 65.0      & 70.6       \\
+ESIM           & GloVe 840B 300d & 70.5      & 70.6       \\
+DA             & GloVe 6B 300d   & 70.4      & 72.6       \\
+DA             & ELMo            & 79.1      & 75.5       \\
+\midrule
+Syntail v1     & GloVe 6B 300d   & 78.4      & \textbf{77.4}       \\
+Syntail v2     & GloVe 6B 300d   & \textbf{82.3}      & \textbf{77.4}       \\
+Syntail v3     & GloVe 6B 300d   & 79.0         & 76.1          \\
+Syntail v4     & GloVe 6B 300d   & 81.3      & 77.0       \\
 \bottomrule
 \end{tabular}}
-  \caption{Syntail-v1 and DA model accuracies on the SciTail dataset.}
-\label{table:v1-accuracies}
+\caption{Dev and test accuracies on SciTail.}
+\label{table:experiments}
 \end{table}
 
-\section{Proposed Methods}
-\label{methods}
+Our experimental results can be found in table~\ref{table:experiments}.
+All of our syntail models
+achieve better test accuracy than the baseline models. This demonstrates
+that the syntax parser is providing features that are both useful for
+determining entailment relationships and difficult for the baseline
+models to learn on their own.
 
-We plan to use state-of-the-art constituency \citep{Stern2017-co} and
-dependency \citep{Dozat2016-gs} parsers to investigate if incorporating
-syntactic features improves the performance of the DA model. Additionally, we
-hope to understand how syntactic features interact with contextual word
-embeddings like ELMo \citep{Peters2018-fz} and BERT \citep{Devlin2018-qc} in a
-task like NLI. It is unclear from previous work whether contextual word
-embeddings benefit from additional syntactic information or if something like
-ELMo can already adequately capture this information.
+We were surprised that the simpler v1 and v2 models outperformed the
+more complicated v3 and v4 models. This is likely due to the syntactic
+information being fused later in v1 and v2. The later the features are
+fused, the closer they are to the loss function and the more the model
+can learn to use them.
 
-We will first investigate different ways of incorporating syntactic
-information. \citet{Pang2018-syntail} use a constituency parser to obtain an
-encoding of the premise and hypothesis that is in the final fully-connected
-layer of the DA model. We believe that incorporating syntactic features earlier
-in the pipeline, especially before the premise and hypothesis are attended over
-one another, should improve performance.
+It is also interesting that adding and additional transformation
+on the syntactic features in v4 decreases performance.
+Again, this is likely due to the early fusion problem.
+The additional power of the model is overwhelmed by the detrimental
+effects of the vanishing gradient problem.
+It is also possible that the randomly initialized weights 
+of the feed-forward neural network struggle to learn how to
+summarize the syntactic features.
 
-We will then investigate different model architectures under a multi-task
-training objective where the jointly learns to both parse and predict
-entailment relationships.
+One downside of using a pretrained syntax parser is that the data SciTail is
+created from (science exam questions) is in a very different domain than
+the data used to create the Penn Treebank (news articles)
+\citep{marcus1993building}.
+This likely significantly reduces the accuracy of the syntax parser on
+SciTail. Retraining the syntax parser on in-domain data
+should produce better syntactic features
+and further improve 
+the performance of our model.
+
+\subsection{Analysis of Syntactic Features}
+
+We discuss a specific in-domain input example shown in table~\ref{table:example}
+to better understand the effects of syntactic features. The predictions on this
+input made by the DA and
+syntail v1 models are shown in table~\ref{table:pred-example}.
+
+\begin{table*}[t]
+    \centering
+    \resizebox{\linewidth}{!}{
+    \begin{tabular}{c c}
+    \toprule
+    Premise & Hypothesis \\
+    \midrule
+    The continental crust is less dense than the mantle but the oceanic crust is not.
+        & The oceanic crust is more dense than the mantle. \\
+    \bottomrule
+    \end{tabular}}
+    \caption{A pair of sentences where syntail performs particularly well. The hypothesis is
+             entailed by the premise.}
+\label{table:example}
+\end{table*}
+
+\begin{table}[h]
+    \centering
+    \begin{tabular}{c c c}
+        \toprule
+         Model & Entails (correct) \\
+         \midrule
+         DA & 29.5\% \\
+         Syntail v1 & \textbf{67.9\%} \\
+         \bottomrule
+    \end{tabular}
+    \caption{Entailment probabilities generated by the DA and syntail v1 models on the input
+             from table~\ref{table:example}.}
+\label{table:pred-example}
+\end{table}
+
+Syntail v1 correctly determines the relationship of this pair of sentences
+while the DA model does not.
+To investigate why, we visualize the attention weights in figures~\ref{fig:da-attention-weights}
+and \ref{fig:sytail-attention-weights}.
+We can see that the attention produced by the DA model is nonsensical and focuses solely on
+``is.'' It seems that by incorporating syntactic information, syntail v1 is forced to learn
+a more reliable attention function.
 
 \begin{figure}[h]
-  \includegraphics[width=0.45\textwidth]{v1}
-  \caption{A simple method of incorporating syntax into the decomposable
-    attention model.}
-\label{figure:v1}
+    \centering
+    \includegraphics[width=\linewidth]{figures/da-h2p-attention.png}
+    \caption{Hypothesis to premise attention weights of the DA model when processing
+             the input from table~\ref{table:example}.}
+    \label{fig:da-attention-weights}
 \end{figure}
 
-\section{Expected Outcomes}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figures/syntail-h2p-attention.png}
+    \caption{Hypothesis to premise attention weights of syntail v1 when processing
+             the input from table~\ref{table:example}.}
+    \label{fig:sytail-attention-weights}
+\end{figure}
 
-We will compare our models to the DA model as well as syntail-v1. We hope to
-evaluate our models on many diverse datasets as stated in section
-~\ref{methods}.
+\section{Related Work}
 
-We expect that one of our modeling ideas will produce results that improve on
-the DA and syntail-v1 models. In the best case, we will show that syntax is
-crucial to building an accurate NLI system.
+Previous works have experimented with incorporating syntactic features for semantic tasks.
+\citet{Chen2016-wl} use tree structures generated by a constituency parser to improve
+their ESIM model. They encode the phrase-structure trees with a Tree-LSTM and use its
+hidden states. \citet{Khot2018-th} incorporate syntactic features by
+proposing a model architecture which can use any graph-based syntactic/semantic structure.
 
-\section{Challenges}
+Other works have experimented with incorporating syntactic learning objectives.
+\citet{Strubell2018-qw} achieved state-of-the-art performance
+for a model using predicted predicates and standard word embeddings on
+CoNLL-2005 SRL by performing multi-task training on additional syntactic tasks.
+\citet{Swayamdipta2017-ct} use hard-coded constituency and dependency parse features
+and a syntactic scaffold to
+extend the softmax margin segmental RNN (segRNN) model.
 
-The first challenge involved in our project will be to modify syntail-v1
-so that syntactic information is incorporated much earlier. It will also take
-significant time to investigate the best parsers to use for our model.
-After, we will write a new model under a multi-task training setup, which we
-anticipate will be a significant implementation challenge.
+\section{Conclusion}
 
-We expect to require significant compute power and time to adequately fine-tune
-and evaluate our models. Contextual word embeddings are especially costly to
-train, and the mixing ratio in a multi-task setup is well-known to be
-difficult to tune.
+By making simple extensions to the DA model,
+our syntail models outperform ESIM and DA + ELMo model on SciTail.
+Our results demonstrate the importance of syntactic information in semantic models
+and motivate future research into syntactically informed models.
 
-\section{Credits}
-
+\bibliographystyle{acl_natbib}
 \bibliography{references}
-\bibliographystyle{acl_natbib_nourl}
 

### 2019-03-26 paper/main.tex
Cleaning up writeup.

@@
 
-\aclfinalcopy % Uncomment this line for the final submission
+%\aclfinalcopy % Uncomment this line for the final submission
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 \begin{abstract}
-We demonstrate the importance of syntactic information in semantic models by extending the
-decomposable attention model for natural language inference.
-By pipelining the hidden states of a neural syntax parser into the decomposable
-attention model, we achieve greater performance on the SciTail dataset
-than the ESIM model and DA + ELMo.
+  We demonstrate the importance of syntactic information in semantic models by
+  extending the decomposable attention model for natural language inference.
+  By pipelining the hidden states of a neural syntax parser into the
+  decomposable attention model, we achieve greater performance on the SciTail
+  dataset than the ESIM model and DA + ELMo.
 \end{abstract}
@@
 Natural language inference (NLI) is the task of characterizing entailment and
-contradiction relationships between texts.
-In general, most NLI tasks are formulated as characterizing the relationship
-between a pair of sequences---a premise and a hypothesis. An NLI model should
-predict whether the hypothesis is entailed by the premise, contradicts the
-premise, or is neutral to the premise.
+contradiction relationships between texts.  In general, most NLI tasks are
+formulated as characterizing the relationship between a pair of sequences---a
+premise and a hypothesis. An NLI model should predict whether the hypothesis is
+entailed by the premise, contradicts the premise, or is neutral to the premise.
 
-We extend the decomposable attention (DA) model from  \citet{Parikh2016-em} by
-incorporating syntactic features.
-The DA model obtained state-of-the-art results on the
-SNLI \citep{Bowman2015-is} dataset at its time of publication while using
-drastically fewer parameters than previous NLI models.
-We primarily
-evaluate on the domain-specific SciTail dataset \citep{Khot2018-th}
-for both its smaller size and lack of annotation artifacts when compared to SNLI
-\citep{Gururangan2018-lj}.
+We extend the decomposable attention (DA) model from
+\citet{parikh2016decomposable} by incorporating syntactic features.  The DA
+model obtained state-of-the-art results on the SNLI \citep{bowman2015large}
+dataset at its time of publication while using drastically fewer parameters
+than previous NLI models.  We primarily evaluate on the domain-specific SciTail
+dataset \citep{Khot2018-th} for both its smaller size and lack of annotation
+artifacts when compared to SNLI \citep{gururangan2018annotation}.
 
-Our model, \texttt{syntail}, achieves 4.8\% better 
-test accuracy than the vanilla
-DA model and 1.9\% better test accuracy than DA with ELMo \citep{Peters2018-fz}
-all while maintaining the core DA architecture.
+Our model, \texttt{syntail}, achieves 4.8\% better test accuracy than the
+vanilla DA model and 1.9\% better test accuracy than DA with ELMo
+\citep{peters2018deep} all while maintaining the core DA architecture.
 
@@
 
-The DA model is a simple and easily parallelizable approach to NLI.
-We summarize it here so we can build upon it later.
-The model
-decomposes into attend, compare, and aggregate steps.
+The DA model is a simple and easily parallelizable approach to NLI.  We
+summarize it here so we can build upon it later.  The model decomposes into
+attend, compare, and aggregate steps.
 
-Let
-$\bm{p} = \langle p_1, \dots, p_{\ell_p} \rangle$ and
-$\bm{h} = \langle h_1, \dots, h_{\ell_h} \rangle$ where each $p_i, h_j \in \mathbb{R}^d$
-is a $d$-dimensional word embedding vector.
+Let $\bm{p} = \langle p_1, \dots, p_{\ell_p} \rangle$ and $\bm{h} = \langle
+h_1, \dots, h_{\ell_h} \rangle$ where each $p_i, h_j \in \mathbb{R}^d$ is a
+$d$-dimensional word embedding vector.
 
@@
 \end{align}
-where $\bm{H}_i$ is the weighted sum over $\bm{h}$ that aligns to $p_i$ and vice versa
-for $\bm{P}_j$.
+where $\bm{H}_i$ is the weighted sum over $\bm{h}$ that aligns to $p_i$ and
+vice versa for $\bm{P}_j$.
 
@@
 \begin{align}
-    \bm{v}^p_i &:= G([p_i, \bm{H}_i])\quad \forall i \in [1,\ldots, \ell_p]\,, \notag \\
+  \bm{v}^p_i &:= G([p_i, \bm{H}_i])\quad \forall i \in [1,\ldots, \ell_p]\,,
+      \notag \\
   \bm{v}^h_j &:= G([h_j, \bm{P}_j])\quad \forall j \in [1,\ldots, \ell_h]\,.
@@
 
-The motivation for incorporating syntactic information in an NLI model
-can be demonstrated with a simple example. Consider the premise ``Adrian is running
+The motivation for incorporating syntactic information in an NLI model can be
+demonstrated with a simple example. Consider the premise ``Adrian is running
 and Alex is swimming." If we present the DA model trained on SNLI with the
 hypothesis ``Adrian is swimming," it will confidently predict that this
-blatantly incorrect hypothesis is entailed by the premise. Observing
-any syntactic parse of
-the premise will make it obvious that Adrian is in fact running.
+blatantly incorrect hypothesis is entailed by the premise. Observing any
+syntactic parse of the premise will make it obvious that Adrian is in fact
+running.
 
-We experiment with features produced by two syntax parsers---the
-minimal span-based neural constituency parser \citep{Stern2017-co} and
-the deep biaffine attention model for dependency parsing \citep{Dozat2016-gs}. We also experiment
-with different methods of incorporating the syntactic features extracted
-from these parsers.
+We experiment with features produced by two syntax parsers---the minimal
+span-based neural constituency parser \citep{stern2017minimal} and the deep
+biaffine attention model for dependency parsing \citep{dozat2016deep}. We also
+experiment with different methods of incorporating the syntactic features
+extracted from these parsers.
 
@@
 
-The minimal span-based neural constituency parser and the deep biaffine attention
-model for dependency parsing both encode the input sequence with an LSTM. Using
-this LSTM, we obtain
-syntactic features $\bm{s}^p = \langle s^p_1, \dots, s^p_{\ell_p} \rangle$ and
-$\bm{s}^h = \langle s^h_1, \dots, s^h_{\ell_h} \rangle$ from the premise and hypothesis,
-respectively. An $s_i$ is either
-the final hidden state $\bm{r}_i$ of the LSTM at index $i$ or a projected
+The minimal span-based neural constituency parser and the deep biaffine
+attention model for dependency parsing both encode the input sequence with an
+LSTM. Using this LSTM, we obtain syntactic features $\bm{s}^p = \langle s^p_1,
+\dots, s^p_{\ell_p} \rangle$ and $\bm{s}^h = \langle s^h_1, \dots, s^h_{\ell_h}
+\rangle$ from the premise and hypothesis, respectively. An $s_i$ is either the
+final hidden state $\bm{r}_i$ of the LSTM at index $i$ or a projected
 representation of $\bm{r}_i$.
@@
 We will now describe the different model architectures we experimented with.
-In general, as the version number increases, the complexity of the model increases.
+In general, as the version number increases, the complexity of the model
+increases.
 
-\paragraph{v1: Naive late fusion of syntactic features.}
-The simplest way to incorporate $\bm{s}$ is to concatenate its final representation to
-$\bm{v}^p$ and $\bm{v}^h$ as shown in figure~\ref{fig:v1}.
+\paragraph{v1: Naive late fusion of syntactic features.} The simplest way to
+incorporate $\bm{s}$ is to concatenate its final representation to $\bm{v}^p$
+and $\bm{v}^h$ as shown in figure~\ref{fig:v1}.
 
-\begin{figure}[h]
+\begin{figure}[htb]
     \centering
@@
 \end{align}
-where we concatenate the final hidden representation of the premise and hypothesis
-when passed through the neural syntax parser with the aggregrated comparision vectors.
-Everything else is identical to the DA model.
+where we concatenate the final hidden representation of the premise and
+hypothesis when passed through the neural syntax parser with the aggregrated
+comparision vectors.  Everything else is identical to the DA model.
 
-\paragraph{v2: Using syntactic features to attend.}
-We wanted to experiment with incorporating syntactic features earlier in the model.
-Instead of learning weights on the syntactic features, it is possible to
-concatenate them to the projected input representations as show in figure~\ref{fig:v2}.
+\paragraph{v2: Using syntactic features to attend.} We wanted to experiment
+with incorporating syntactic features earlier in the model.  Instead of
+learning weights on the syntactic features, it is possible to concatenate them
+to the projected input representations as show in figure~\ref{fig:v2}.
 
-\begin{figure}[h]
+\begin{figure}[htb]
   \centering
@@
 
-Computing the
-unnormalized attention weights in equation~\ref{eq:attend} then becomes:
-\begin{align}
-    e_{ij} := [F(p_i), s^p_i]^\mathsf{T} [F(h_j), s^h_i]
-\end{align}
-where instead of calculating the alignment using only the 
-projected hypothesis and premise vectors, we now also use the final hidden states of
-the premise and hypothesis when passed through the neural syntax parser.
-This seems rather naive since this model will not
-learn any weights on the syntactic features, but in practice this model
-performs very well. Everything else is identical to the DA model.
+Computing the unnormalized attention weights in equation~\ref{eq:attend} then
+becomes: \begin{align} e_{ij} := [F(p_i), s^p_i]^\mathsf{T} [F(h_j), s^h_i]
+\end{align} where instead of calculating the alignment using only the projected
+hypothesis and premise vectors, we now also use the final hidden states of the
+premise and hypothesis when passed through the neural syntax parser.  This
+seems rather naive since this model will not learn any weights on the syntactic
+features, but in practice this model performs very well. Everything else is
+identical to the DA model.
 
 \paragraph{v3: Using syntactic features to project the premise and hypothesis.}
-We decided to try incorporating the syntactic features even earlier in the model.
-Instead of concatenating the final hidden states of the parsed premise and hypothesis
-with the projected inputs, we concatenate the final hidden states of the parsed
-premise and hypothesis with the inputs immediately before projecting them. This
-architecture is shown in figure~\ref{fig:v3}.
+We decided to try incorporating the syntactic features even earlier in the
+model.  Instead of concatenating the final hidden states of the parsed premise
+and hypothesis with the projected inputs, we concatenate the final hidden
+states of the parsed premise and hypothesis with the inputs immediately before
+projecting them. This architecture is shown in figure~\ref{fig:v3}.
 
-\begin{figure}[h]
+\begin{figure}[htb]
   \centering
@@
 
-Computing the unnormalized attention weights in equation~\ref{eq:attend} then becomes:
+Computing the unnormalized attention weights in equation~\ref{eq:attend} then
+becomes:
 \begin{align}
@@
 due to not allowing our model to transform the syntactic features enough before
-calculating attention.
-We decided to learn weights to project the final hidden states of the parsed
-premise and hypothesis by passing them through an additional fully-connected layer before 
-concatenating them to the inputs. This architecture is shown in figure~\ref{fig:v4}
+calculating attention.  We decided to learn weights to project the final hidden
+states of the parsed premise and hypothesis by passing them through an
+additional fully-connected layer before concatenating them to the inputs. This
+architecture is shown in figure~\ref{fig:v4}
 
-\begin{figure}[h]
+\begin{figure}[htb]
     \centering
@@
 \end{align}
-where $J$ is a feed-forward neural network.
-Everything else is identical to the DA model.
-
-% \jbcomment{If we're only using data from the dependency parser we should probably 
-% remove the section following this comment}
-% Supplemental variations were done on top of these restructures of the network. One 
-% of the variations that we introduced was a retrained constituency parser. By 
-% retraining the constituency parser on the Penn Treebank dataset \citep{marcus1993building} 
-% we could change the dimensions of the encoded syntax vectors to better fit with our models. 
-% Additionally, we experimented with training our models using the dependency parser model 
-% derived by \citet{Dozat2016-gs} to see if the different types of encoded parses influenced 
-% the performance of the network.
+where $J$ is a feed-forward neural network. Everything else is identical to
+the DA model.
 
@@
 Due to resource constraints, we limited our models to only use 300-dimensional
-6B GloVe word embeddings \citep{Pennington2014-uo}.
-Additionally, contextual embeddings are known to capture syntax in some capacity,
-so limiting our models to only use GloVe vectors
-made it easier to experiment with the syntactic features in isolation.
+6B GloVe word embeddings \citep{pennington2014glove}.  Additionally, contextual
+embeddings are known to capture syntax in some capacity, so limiting our models
+to only use GloVe vectors made it easier to experiment with the syntactic
+features in isolation.
 
@@
 
-We initially used a constituency parser in syntail. However,
-after some experimentation, we found that we were achieving better results
-with a dependency parser.
-For this reason, we only report results using the deep biaffine attention
-model for dependency parsing.
-Dependency parsers focus on encoding the
-the relationships between words as opposed to determining constituents.
-Intuitively, if we consider our example sentence, ``Adrian is running and Alex is swimming,''
-the dependency arcs will be more informative of who is doing what.
+We initially used a constituency parser in syntail. However, after some
+experimentation, we found that we were achieving better results with a
+dependency parser.  For this reason, we only report results using the deep
+biaffine attention model for dependency parsing.  Dependency parsers focus on
+encoding the the relationships between words as opposed to determining
+constituents.  Intuitively, if we consider our example sentence, ``Adrian is
+running and Alex is swimming,'' the dependency arcs will be more informative of
+who is doing what.
 
@@
 
-We use 200-dimensional projections of the word embeddings. Our feed-forward neural
-networks are 2 layered and have hidden dimensions of 200. We train with both
-Adam \citep{kingma2014adam} and Adagrad \citep{duchi2011adaptive} and report the
-better result.
+We use 200-dimensional projections of the word embeddings. Our feed-forward
+neural networks are 2 layered and have hidden dimensions of 200. We train with
+both Adam \citep{kingma2014adam} and Adagrad \citep{duchi2011adaptive} and
+report the better result.
 
@@
 We compare our model's performance to the decomposable attention model
-\citep{Parikh2016-em} and the ESIM model \citep{Chen2016-wl}.
-Early on in our experiments, we noticed that features from a dependency
-parser seemed to perform better than those from a constituency parser.
-Therefore, all of our models use the deep biaffine attention model for
-dependency parsing \citep{Dozat2016-gs}.
+\citep{parikh2016decomposable} and the ESIM model \citep{chen2016enhanced}.
+Early on in our experiments, we noticed that features from a dependency parser
+seemed to perform better than those from a constituency parser.  Therefore, all
+of our models use the deep biaffine attention model for dependency parsing
+\citep{dozat2016deep}.
 
-\paragraph{Datasets.}
-For practical reasons, we only experiment on the SciTail dataset. SciTail (27k pairs) is
-significantly smaller than SNLI (570k pairs) \citep{Bowman2015-is} or MultiNLI (433k pairs)
-\citep{Williams2017-uh} which makes it feasible to try many different
-architectures given limited resources.
+\paragraph{Datasets.} For practical reasons, we only experiment on the SciTail
+dataset. SciTail (27k pairs) is significantly smaller than SNLI (570k pairs)
+\citep{bowman2015large} or MultiNLI (433k pairs) \citep{williams2017broad}
+which makes it feasible to try many different architectures given limited
+resources.
 
-Additionally, \citet{Gururangan2018-lj} showed that SNLI and MultiNLI
-have significant annotation artifacts whereas SciTail is the first entailment set to be
-completely derived from sentences that exist ``in the wild.''
+Additionally, \citet{gururangan2018annotation} showed that SNLI and MultiNLI
+have significant annotation artifacts whereas SciTail is the first entailment
+set to be completely derived from sentences that exist ``in the wild.''
 
 \paragraph{Baselines.}
-We list baseline performance reported by \citet{Khot2018-th} of a majority class predictor,
-n-gram model, and ESIM \citep{Chen2016-wl} in table~\ref{table:experiments}. We reimplemented
-and retrained the DA model and obtained similar test accuracies as reported by \citet{Chen2016-wl}.
-Adding ELMo to the DA model improved test accuracy performance by approximately 3\%.
+We list baseline performance reported by \citet{Khot2018-th} of a majority
+class predictor, n-gram model, and ESIM \citep{chen2016enhanced} in
+table~\ref{table:experiments}. We reimplemented and retrained the DA model and
+obtained similar test accuracies as reported by \citet{chen2016enhanced}.
+Adding ELMo to the DA model improved test accuracy performance by approximately
+3\%.
 
@@
 
-\begin{table}[h]
+\begin{table}[htb]
 \centering
@@
 
-Our experimental results can be found in table~\ref{table:experiments}.
-All of our syntail models
-achieve better test accuracy than the baseline models. This demonstrates
-that the syntax parser is providing features that are both useful for
-determining entailment relationships and difficult for the baseline
-models to learn on their own.
+Our experimental results can be found in table~\ref{table:experiments}. All of
+our syntail models achieve better test accuracy than the baseline models. This
+demonstrates that the syntax parser is providing features that are both useful
+for determining entailment relationships and difficult for the baseline models
+to learn on their own.
 
-We were surprised that the simpler v1 and v2 models outperformed the
-more complicated v3 and v4 models. This is likely due to the syntactic
-information being fused later in v1 and v2. The later the features are
-fused, the closer they are to the loss function and the more the model
-can learn to use them.
+We were surprised that the simpler v1 and v2 models outperformed the more
+complicated v3 and v4 models. This is likely due to the syntactic information
+being fused later in v1 and v2. The later the features are fused, the closer
+they are to the loss function and the more the model can learn to use them.
 
-It is also interesting that adding and additional transformation
-on the syntactic features in v4 decreases performance.
-Again, this is likely due to the early fusion problem.
-The additional power of the model is overwhelmed by the detrimental
-effects of the vanishing gradient problem.
-It is also possible that the randomly initialized weights 
-of the feed-forward neural network struggle to learn how to
-summarize the syntactic features.
+It is also interesting that adding and additional transformation on the
+syntactic features in v4 decreases performance.  Again, this is likely due to
+the early fusion problem.  The additional power of the model is overwhelmed by
+the detrimental effects of the vanishing gradient problem.  It is also possible
+that the randomly initialized weights of the feed-forward neural network
+struggle to learn how to summarize the syntactic features.
 
 One downside of using a pretrained syntax parser is that the data SciTail is
-created from (science exam questions) is in a very different domain than
-the data used to create the Penn Treebank (news articles)
-\citep{marcus1993building}.
-This likely significantly reduces the accuracy of the syntax parser on
-SciTail. Retraining the syntax parser on in-domain data
-should produce better syntactic features
-and further improve 
-the performance of our model.
+created from (science exam questions) is in a very different domain than the
+data used to create the Penn Treebank (news articles)
+\citep{marcus1993building}.  This likely significantly reduces the accuracy of
+the syntax parser on SciTail. Retraining the syntax parser on in-domain data
+should produce better syntactic features and further improve the performance of
+our model.
 
@@
 
-We discuss a specific in-domain input example shown in table~\ref{table:example}
-to better understand the effects of syntactic features. The predictions on this
-input made by the DA and
-syntail v1 models are shown in table~\ref{table:pred-example}.
+We discuss a specific in-domain input example shown in
+table~\ref{table:example} to better understand the effects of syntactic
+features. The predictions on this input made by the DA and syntail v1 models
+are shown in table~\ref{table:pred-example}.
 
@@
     \midrule
-    The continental crust is less dense than the mantle but the oceanic crust is not.
-        & The oceanic crust is more dense than the mantle. \\
+    The continental crust is less dense than the mantle but the oceanic crust
+        is not. & The oceanic crust is more dense than the mantle. \\
     \bottomrule
   \end{tabular}}
-    \caption{A pair of sentences where syntail performs particularly well. The hypothesis is
-             entailed by the premise.}
+  \caption{A pair of sentences where syntail performs particularly well. The
+      hypothesis is entailed by the premise.}
 \label{table:example}
@@
 
-\begin{table}[h]
+\begin{table}[htb]
   \centering
@@
   \end{tabular}
-    \caption{Entailment probabilities generated by the DA and syntail v1 models on the input
-             from table~\ref{table:example}.}
+  \caption{Entailment probabilities generated by the DA and syntail v1 models
+      on the input from table~\ref{table:example}.}
 \label{table:pred-example}
@@
 Syntail v1 correctly determines the relationship of this pair of sentences
-while the DA model does not.
-To investigate why, we visualize the attention weights in figures~\ref{fig:da-attention-weights}
-and \ref{fig:sytail-attention-weights}.
-We can see that the attention produced by the DA model is nonsensical and focuses solely on
-``is.'' It seems that by incorporating syntactic information, syntail v1 is forced to learn
-a more reliable attention function.
+while the DA model does not.  To investigate why, we visualize the attention
+weights in figures~\ref{fig:da-attention-weights} and
+\ref{fig:sytail-attention-weights}.  We can see that the attention produced by
+the DA model is nonsensical and focuses solely on ``is.'' It seems that by
+incorporating syntactic information, syntail v1 is forced to learn a more
+reliable attention function.
 
-\begin{figure}[h]
+\begin{figure}[htb]
   \centering
   \includegraphics[width=\linewidth]{figures/da-h2p-attention.png}
-    \caption{Hypothesis to premise attention weights of the DA model when processing
-             the input from table~\ref{table:example}.}
+  \caption{Hypothesis to premise attention weights of the DA model when
+      processing the input from table~\ref{table:example}.}
 \label{fig:da-attention-weights}
@@
 
-\begin{figure}[h]
+\begin{figure}[htb]
   \centering
   \includegraphics[width=\linewidth]{figures/syntail-h2p-attention.png}
-    \caption{Hypothesis to premise attention weights of syntail v1 when processing
-             the input from table~\ref{table:example}.}
+  \caption{Hypothesis to premise attention weights of syntail v1 when
+      processing the input from table~\ref{table:example}.}
 \label{fig:sytail-attention-weights}
@@
 
-Previous works have experimented with incorporating syntactic features for semantic tasks.
-\citet{Chen2016-wl} use tree structures generated by a constituency parser to improve
-their ESIM model. They encode the phrase-structure trees with a Tree-LSTM and use its
-hidden states. \citet{Khot2018-th} incorporate syntactic features by
-proposing a model architecture which can use any graph-based syntactic/semantic structure.
+Previous works have experimented with incorporating syntactic features for
+semantic tasks.  \citet{chen2016enhanced} use tree structures generated by a
+constituency parser to improve their ESIM model. They encode the
+phrase-structure trees with a Tree-LSTM and use its hidden states.
+\citet{Khot2018-th} incorporate syntactic features by proposing a model
+architecture which can use any graph-based syntactic/semantic structure.
 
 Other works have experimented with incorporating syntactic learning objectives.
-\citet{Strubell2018-qw} achieved state-of-the-art performance
-for a model using predicted predicates and standard word embeddings on
-CoNLL-2005 SRL by performing multi-task training on additional syntactic tasks.
-\citet{Swayamdipta2017-ct} use hard-coded constituency and dependency parse features
-and a syntactic scaffold to
-extend the softmax margin segmental RNN (segRNN) model.
+\citet{strubell2018linguistically} achieved state-of-the-art performance for a
+model using predicted predicates and standard word embeddings on CoNLL-2005 SRL
+by performing multi-task training on additional syntactic tasks.
+\citet{swayamdipta2017frame} use hard-coded constituency and dependency parse
+features and a syntactic scaffold to extend the softmax margin segmental RNN
+(segRNN) model.
 
@@
 
-By making simple extensions to the DA model,
-our syntail models outperform ESIM and DA + ELMo model on SciTail.
-Our results demonstrate the importance of syntactic information in semantic models
-and motivate future research into syntactically informed models.
+By making simple extensions to the DA model, our syntail models outperform ESIM
+and DA + ELMo model on SciTail.  Our results demonstrate the importance of
+syntactic information in semantic models and motivate future research into
+syntactically informed models.
 
-\bibliographystyle{acl_natbib}
+\bibliographystyle{acl_natbib_nourl}
 \bibliography{references}

### 2019-03-26 syntactic_entailment/models/constituency_parser_v4.py
Making naming consistent with paper.

@@ -1,409 +1,0 @@
-from typing import Dict, Tuple, List, Optional, NamedTuple, Any
-from overrides import overrides
-
-import torch
-from torch.nn.modules.linear import Linear
-from nltk import Tree
-
-from allennlp.common.checks import check_dimensions_match
-from allennlp.data import Vocabulary
-from allennlp.modules import Seq2SeqEncoder, TimeDistributed, TextFieldEmbedder, FeedForward
-from allennlp.modules.token_embedders import Embedding
-from allennlp.modules.span_extractors.span_extractor import SpanExtractor
-from allennlp.models.model import Model
-from allennlp.nn import InitializerApplicator, RegularizerApplicator
-from allennlp.nn.util import get_text_field_mask, sequence_cross_entropy_with_logits
-from allennlp.nn.util import masked_softmax, get_lengths_from_binary_sequence_mask
-from allennlp.nn.util import get_final_encoder_states
-from allennlp.training.metrics import CategoricalAccuracy
-from allennlp.training.metrics import EvalbBracketingScorer, DEFAULT_EVALB_DIR
-from allennlp.common.checks import ConfigurationError
-
-from allennlp.models.constituency_parser import SpanConstituencyParser
-from allennlp.models.constituency_parser import SpanInformation
-
-@Model.register("syntactic-entailment-constituency-parser-v4")
-class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
-    """
-    This ``SpanConstituencyParser`` simply encodes a sequence of text
-    with a stacked ``Seq2SeqEncoder``, extracts span representations using a
-    ``SpanExtractor``, and then predicts a label for each span in the sequence.
-    These labels are non-terminal nodes in a constituency parse tree, which we then
-    greedily reconstruct.
-
-    Parameters
-    ----------
-    vocab : ``Vocabulary``, required
-        A Vocabulary, required in order to compute sizes for input/output projections.
-    text_field_embedder : ``TextFieldEmbedder``, required
-        Used to embed the ``tokens`` ``TextField`` we get as input to the model.
-    span_extractor : ``SpanExtractor``, required.
-        The method used to extract the spans from the encoded sequence.
-    encoder : ``Seq2SeqEncoder``, required.
-        The encoder that we will use in between embedding tokens and
-        generating span representations.
-    feedforward : ``FeedForward``, required.
-        The FeedForward layer that we will use in between the encoder and the linear
[…]

### 2019-03-26 syntactic_entailment/models/dependency_parser_v6.py

@@ -1,567 +1,0 @@
-from typing import Dict, Optional, Tuple, Any, List
-import logging
-import copy
-
-from overrides import overrides
-import torch
-import torch.nn.functional as F
-from torch.nn.modules import Dropout
-import numpy
-
-from allennlp.common.checks import check_dimensions_match, ConfigurationError
-from allennlp.data import Vocabulary
-from allennlp.modules import Seq2SeqEncoder, TextFieldEmbedder, Embedding, InputVariationalDropout
-from allennlp.modules.matrix_attention.bilinear_matrix_attention import BilinearMatrixAttention
-from allennlp.modules import FeedForward
-from allennlp.models.model import Model
-from allennlp.nn import InitializerApplicator, RegularizerApplicator, Activation
-from allennlp.nn.util import get_text_field_mask, get_range_vector
-from allennlp.nn.util import get_device_of, masked_log_softmax, get_lengths_from_binary_sequence_mask
-from allennlp.nn.chu_liu_edmonds import decode_mst
-from allennlp.training.metrics import AttachmentScores
-
-from allennlp.models.biaffine_dependency_parser import BiaffineDependencyParser
-
-logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
-
-POS_TO_IGNORE = {'``', "''", ':', ',', '.', 'PU', 'PUNCT', 'SYM'}
-
-@Model.register("syntactic-entailment-dependency-parser-v6")
-class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
-    """
-    This dependency parser follows the model of
-    ` Deep Biaffine Attention for Neural Dependency Parsing (Dozat and Manning, 2016)
-    <https://arxiv.org/abs/1611.01734>`_ .
-
-    Word representations are generated using a bidirectional LSTM,
-    followed by separate biaffine classifiers for pairs of words,
-    predicting whether a directed arc exists between the two words
-    and the dependency label the arc should have. Decoding can either
-    be done greedily, or the optimal Minimum Spanning Tree can be
-    decoded using Edmond's algorithm by viewing the dependency tree as
-    a MST on a fully connected graph, where nodes are words and edges
-    are scored dependency arcs.
-
-    Parameters
-    ----------
-    vocab : ``Vocabulary``, required
-        A Vocabulary, required in order to compute sizes for input/output projections.
-    text_field_embedder : ``TextFieldEmbedder``, required
-        Used to embed the ``tokens`` ``TextField`` we get as input to the model.
[…]

### 2019-03-26 syntactic_entailment/models/constituency_parser_v1.py
Making naming consistent with paper.

@@ -1,0 +1,411 @@
+from typing import Dict, Tuple, List, Optional, NamedTuple, Any
+from overrides import overrides
+
+import torch
+from torch.nn.modules.linear import Linear
+from nltk import Tree
+
+from allennlp.common.checks import check_dimensions_match
+from allennlp.data import Vocabulary
+from allennlp.modules import Seq2SeqEncoder, TimeDistributed, TextFieldEmbedder, FeedForward
+from allennlp.modules.token_embedders import Embedding
+from allennlp.modules.span_extractors.span_extractor import SpanExtractor
+from allennlp.models.model import Model
+from allennlp.nn import InitializerApplicator, RegularizerApplicator
+from allennlp.nn.util import get_text_field_mask, sequence_cross_entropy_with_logits
+from allennlp.nn.util import masked_softmax, get_lengths_from_binary_sequence_mask
+from allennlp.nn.util import get_final_encoder_states
+from allennlp.training.metrics import CategoricalAccuracy
+from allennlp.training.metrics import EvalbBracketingScorer, DEFAULT_EVALB_DIR
+from allennlp.common.checks import ConfigurationError
+
+from allennlp.models.constituency_parser import SpanConstituencyParser
+from allennlp.models.constituency_parser import SpanInformation
+
+@Model.register("syntactic-entailment-constituency-parser-v1")
+class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
+    """
+    This ``SpanConstituencyParser`` simply encodes a sequence of text
+    with a stacked ``Seq2SeqEncoder``, extracts span representations using a
+    ``SpanExtractor``, and then predicts a label for each span in the sequence.
+    These labels are non-terminal nodes in a constituency parse tree, which we then
+    greedily reconstruct.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``, required
+        A Vocabulary, required in order to compute sizes for input/output projections.
+    text_field_embedder : ``TextFieldEmbedder``, required
+        Used to embed the ``tokens`` ``TextField`` we get as input to the model.
+    span_extractor : ``SpanExtractor``, required.
+        The method used to extract the spans from the encoded sequence.
+    encoder : ``Seq2SeqEncoder``, required.
+        The encoder that we will use in between embedding tokens and
+        generating span representations.
+    feedforward : ``FeedForward``, required.
+        The FeedForward layer that we will use in between the encoder and the linear
[…]

### 2019-03-26 syntactic_entailment/models/constituency_parser_v2.py

@@ -154,7 +154,6 @@ class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
         num_spans = get_lengths_from_binary_sequence_mask(span_mask)
 
         encoded_text = self.encoder(embedded_text_input, mask)
-        encoder_final_state = get_final_encoder_states(encoded_text, mask)
 
         span_representations = self.span_extractor(encoded_text, spans, mask, span_mask)
 
@@ -165,8 +164,7 @@ class SyntacticEntailmentSpanConstituencyParser(SpanConstituencyParser):
         class_probabilities = masked_softmax(logits, span_mask.unsqueeze(-1))
 
         output_dict = {
-                "encoder_final_state": encoder_final_state,
-                #"encoded_text": encoded_text,
+                "encoded_text": encoded_text,
                 "class_probabilities": class_probabilities,
                 "spans": spans,
                 "tokens": [meta["tokens"] for meta in metadata],

### 2019-03-26 syntactic_entailment/models/dependency_parser_v1.py

@@ -1,0 +1,569 @@
+from typing import Dict, Optional, Tuple, Any, List
+import logging
+import copy
+
+from overrides import overrides
+import torch
+import torch.nn.functional as F
+from torch.nn.modules import Dropout
+import numpy
+
+from allennlp.common.checks import check_dimensions_match, ConfigurationError
+from allennlp.data import Vocabulary
+from allennlp.modules import Seq2SeqEncoder, TextFieldEmbedder, Embedding, InputVariationalDropout
+from allennlp.modules.matrix_attention.bilinear_matrix_attention import BilinearMatrixAttention
+from allennlp.modules import FeedForward
+from allennlp.models.model import Model
+from allennlp.nn import InitializerApplicator, RegularizerApplicator, Activation
+from allennlp.nn.util import get_text_field_mask, get_range_vector, get_final_encoder_states
+from allennlp.nn.util import get_device_of, masked_log_softmax, get_lengths_from_binary_sequence_mask
+from allennlp.nn.chu_liu_edmonds import decode_mst
+from allennlp.training.metrics import AttachmentScores
+
+from allennlp.models.biaffine_dependency_parser import BiaffineDependencyParser
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+POS_TO_IGNORE = {'``', "''", ':', ',', '.', 'PU', 'PUNCT', 'SYM'}
+
+@Model.register("syntactic-entailment-dependency-parser-v1")
+class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
+    """
+    This dependency parser follows the model of
+    ` Deep Biaffine Attention for Neural Dependency Parsing (Dozat and Manning, 2016)
+    <https://arxiv.org/abs/1611.01734>`_ .
+
+    Word representations are generated using a bidirectional LSTM,
+    followed by separate biaffine classifiers for pairs of words,
+    predicting whether a directed arc exists between the two words
+    and the dependency label the arc should have. Decoding can either
+    be done greedily, or the optimal Minimum Spanning Tree can be
+    decoded using Edmond's algorithm by viewing the dependency tree as
+    a MST on a fully connected graph, where nodes are words and edges
+    are scored dependency arcs.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``, required
+        A Vocabulary, required in order to compute sizes for input/output projections.
+    text_field_embedder : ``TextFieldEmbedder``, required
[…]

### 2019-03-26 syntactic_entailment/models/dependency_parser_v2.py

@@ -15,7 +15,7 @@ from allennlp.modules.matrix_attention.bilinear_matrix_attention import Bilinear
 from allennlp.modules import FeedForward
 from allennlp.models.model import Model
 from allennlp.nn import InitializerApplicator, RegularizerApplicator, Activation
-from allennlp.nn.util import get_text_field_mask, get_range_vector, get_final_encoder_states
+from allennlp.nn.util import get_text_field_mask, get_range_vector
 from allennlp.nn.util import get_device_of, masked_log_softmax, get_lengths_from_binary_sequence_mask
 from allennlp.nn.chu_liu_edmonds import decode_mst
 from allennlp.training.metrics import AttachmentScores
@@ -165,8 +165,6 @@ class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
         embedded_text_input = self._input_dropout(embedded_text_input)
         encoded_text_orig = self.encoder(embedded_text_input, mask)
 
-        encoder_final_state = get_final_encoder_states(encoded_text_orig, mask)
-
         batch_size, _, encoding_dim = encoded_text_orig.size()
 
         head_sentinel = self._head_sentinel.expand(batch_size, 1, encoding_dim)
@@ -234,7 +232,7 @@ class SyntacticEntailmentDependencyParser(BiaffineDependencyParser):
             loss = arc_nll + tag_nll
 
         output_dict = {
-                "encoder_final_state": encoder_final_state,
+                "encoded_text" : encoded_text_orig,
                 "heads": predicted_heads,
                 "head_tags": predicted_head_tags,
                 "arc_loss": arc_nll,

### 2019-03-26 syntactic_entailment/models/syntactic_entailment_v1.py

@@ -1,0 +1,222 @@
+from typing import Dict, Optional, List, Any
+
+import torch
+
+from allennlp.predictors.predictor import Predictor
+from allennlp.common.checks import check_dimensions_match
+from allennlp.data import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import FeedForward
+from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
+from allennlp.modules.matrix_attention.legacy_matrix_attention import LegacyMatrixAttention
+from allennlp.nn import InitializerApplicator, RegularizerApplicator
+from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
+from allennlp.training.metrics import CategoricalAccuracy
+
+
+@Model.register("syntactic-entailment-v1")
+class SyntacticEntailment(Model):
+    """
+    This ``Model`` implements the Decomposable Attention model described in `"A Decomposable
+    Attention Model for Natural Language Inference"
+    <https://www.semanticscholar.org/paper/A-Decomposable-Attention-Model-for-Natural-Languag-Parikh-T%C3%A4ckstr%C3%B6m/07a9478e87a8304fc3267fa16e83e9f3bbd98b27>`_
+    by Parikh et al., 2016, with some optional enhancements before the decomposable attention
+    actually happens.  Parikh's original model allowed for computing an "intra-sentence" attention
+    before doing the decomposable entailment step.  We generalize this to any
+    :class:`Seq2SeqEncoder` that can be applied to the premise and/or the hypothesis before
+    computing entailment.
+
+    The basic outline of this model is to get an embedded representation of each word in the
+    premise and hypothesis, align words between the two, compare the aligned phrases, and make a
+    final entailment decision based on this aggregated comparison.  Each step in this process uses
+    a feedforward network to modify the representation.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``
+    text_field_embedder : ``TextFieldEmbedder``
+        Used to embed the ``premise`` and ``hypothesis`` ``TextFields`` we get as input to the
+        model.
+    attend_feedforward : ``FeedForward``
+        This feedforward network is applied to the encoded sentence representations before the
+        similarity matrix is computed between words in the premise and words in the hypothesis.
+    similarity_function : ``SimilarityFunction``
+        This is the similarity function used when computing the similarity matrix between words in
[…]

### 2019-03-26 syntactic_entailment/models/syntactic_entailment_v4.py

@@ -1,0 +1,225 @@
+from typing import Dict, Optional, List, Any
+
+import torch
+
+from allennlp.predictors.predictor import Predictor
+from allennlp.common.checks import check_dimensions_match
+from allennlp.data import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import FeedForward
+from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
+from allennlp.nn import InitializerApplicator, RegularizerApplicator
+from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
+from allennlp.training.metrics import CategoricalAccuracy
+
+from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
+
+
+@Model.register("syntactic-entailment-v4")
+class SyntacticEntailment(Model):
+    """
+    This ``Model`` implements the Decomposable Attention model described in `"A Decomposable
+    Attention Model for Natural Language Inference"
+    <https://www.semanticscholar.org/paper/A-Decomposable-Attention-Model-for-Natural-Languag-Parikh-T%C3%A4ckstr%C3%B6m/07a9478e87a8304fc3267fa16e83e9f3bbd98b27>`_
+    by Parikh et al., 2016, with some optional enhancements before the decomposable attention
+    actually happens.  Parikh's original model allowed for computing an "intra-sentence" attention
+    before doing the decomposable entailment step.  We generalize this to any
+    :class:`Seq2SeqEncoder` that can be applied to the premise and/or the hypothesis before
+    computing entailment.
+
+    The basic outline of this model is to get an embedded representation of each word in the
+    premise and hypothesis, align words between the two, compare the aligned phrases, and make a
+    final entailment decision based on this aggregated comparison.  Each step in this process uses
+    a feedforward network to modify the representation.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``
+    text_field_embedder : ``TextFieldEmbedder``
+        Used to embed the ``premise`` and ``hypothesis`` ``TextFields`` we get as input to the
+        model.
+    attend_feedforward : ``FeedForward``
+        This feedforward network is applied to the encoded sentence representations before the
+        similarity matrix is computed between words in the premise and words in the hypothesis.
+    similarity_function : ``SimilarityFunction``
+        This is the similarity function used when computing the similarity matrix between words in
[…]

### 2019-03-26 syntactic_entailment/models/syntactic_entailment_v5.py

@@ -13,8 +13,6 @@ from allennlp.nn import InitializerApplicator, RegularizerApplicator
 from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
 from allennlp.training.metrics import CategoricalAccuracy
 
-from syntactic_entailment.predictors.constituency_parser import SyntacticEntailmentConstituencyParserPredictor
-
 
 @Model.register("syntactic-entailment-v5")
 class SyntacticEntailment(Model):
@@ -66,6 +64,7 @@ class SyntacticEntailment(Model):
     def __init__(self, vocab: Vocabulary,
                  text_field_embedder: TextFieldEmbedder,
                  attend_feedforward: FeedForward,
+                 project_syntax: FeedForward,
                  similarity_function: SimilarityFunction,
                  compare_feedforward: FeedForward,
                  aggregate_feedforward: FeedForward,
@@ -79,7 +78,8 @@ class SyntacticEntailment(Model):
 
         self._text_field_embedder = text_field_embedder
         self._attend_feedforward = TimeDistributed(attend_feedforward)
-        self._matrix_attention = LegacyMatrixAttention(similarity_function)
+        self._project_syntax = project_syntax
+        self._attention = LegacyMatrixAttention(similarity_function)
         self._compare_feedforward = TimeDistributed(compare_feedforward)
         self._aggregate_feedforward = aggregate_feedforward
         self._premise_encoder = premise_encoder
@@ -87,11 +87,10 @@ class SyntacticEntailment(Model):
 
         self._num_labels = vocab.get_vocab_size(namespace="labels")
 
-        # this check doesn't work anymore since we attend w/ syntax
-        #check_dimensions_match(text_field_embedder.get_output_dim(),
-        #                       attend_feedforward.get_input_dim(),
-        #                       "text field embedding dim",
-        #                       "attend feedforward input dim")
+        check_dimensions_match(text_field_embedder.get_output_dim(),
+                               attend_feedforward.get_input_dim(),
+                               "text field embedding dim",
+                               "attend feedforward input dim")
         check_dimensions_match(aggregate_feedforward.get_output_dim(),
                                self._num_labels,
                                "final output dimension",
@@ -147,14 +146,15 @@ class SyntacticEntailment(Model):
         h_tokens = [metadata[idx]['hypothesis_tokens'] for idx in range(len(metadata))]
[…]

### 2019-03-26 syntactic_entailment/models/syntactic_entailment_v7.py

@@ -1,225 +1,0 @@
-from typing import Dict, Optional, List, Any
-
-import torch
-
-from allennlp.predictors.predictor import Predictor
-from allennlp.common.checks import check_dimensions_match
-from allennlp.data import Vocabulary
-from allennlp.models.model import Model
-from allennlp.modules import FeedForward
-from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
-from allennlp.nn import InitializerApplicator, RegularizerApplicator
-from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
-from allennlp.training.metrics import CategoricalAccuracy
-
-from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
-
-
-@Model.register("syntactic-entailment-v7")
-class SyntacticEntailment(Model):
-    """
-    This ``Model`` implements the Decomposable Attention model described in `"A Decomposable
-    Attention Model for Natural Language Inference"
-    <https://www.semanticscholar.org/paper/A-Decomposable-Attention-Model-for-Natural-Languag-Parikh-T%C3%A4ckstr%C3%B6m/07a9478e87a8304fc3267fa16e83e9f3bbd98b27>`_
-    by Parikh et al., 2016, with some optional enhancements before the decomposable attention
-    actually happens.  Parikh's original model allowed for computing an "intra-sentence" attention
-    before doing the decomposable entailment step.  We generalize this to any
-    :class:`Seq2SeqEncoder` that can be applied to the premise and/or the hypothesis before
-    computing entailment.
-
-    The basic outline of this model is to get an embedded representation of each word in the
-    premise and hypothesis, align words between the two, compare the aligned phrases, and make a
-    final entailment decision based on this aggregated comparison.  Each step in this process uses
-    a feedforward network to modify the representation.
-
-    Parameters
-    ----------
-    vocab : ``Vocabulary``
-    text_field_embedder : ``TextFieldEmbedder``
-        Used to embed the ``premise`` and ``hypothesis`` ``TextFields`` we get as input to the
-        model.
-    attend_feedforward : ``FeedForward``
-        This feedforward network is applied to the encoded sentence representations before the
-        similarity matrix is computed between words in the premise and words in the hypothesis.
-    similarity_function : ``SimilarityFunction``
-        This is the similarity function used when computing the similarity matrix between words in
[…]

### 2019-03-26 syntactic_entailment/models/syntactic_entailment_v2.py
Making naming consistent with paper.

@@ -8,10 +8,11 @@ from allennlp.data import Vocabulary
 from allennlp.models.model import Model
 from allennlp.modules import FeedForward
 from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
-from allennlp.modules.matrix_attention.legacy_matrix_attention import LegacyMatrixAttention
 from allennlp.nn import InitializerApplicator, RegularizerApplicator
 from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
 from allennlp.training.metrics import CategoricalAccuracy
+
+from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
 
 
 @Model.register("syntactic-entailment-v2")
@@ -77,7 +78,7 @@ class SyntacticEntailment(Model):
 
         self._text_field_embedder = text_field_embedder
         self._attend_feedforward = TimeDistributed(attend_feedforward)
-        self._attention = LegacyMatrixAttention(similarity_function)
+        self._attention = SyntacticMatrixAttention(similarity_function)
         self._compare_feedforward = TimeDistributed(compare_feedforward)
         self._aggregate_feedforward = aggregate_feedforward
         self._premise_encoder = premise_encoder
@@ -144,15 +145,14 @@ class SyntacticEntailment(Model):
         h_tokens = [metadata[idx]['hypothesis_tokens'] for idx in range(len(metadata))]
         h_tags = [metadata[idx]['hypothesis_tags'] for idx in range(len(metadata))]
         h_jsons = [{'sentence' : h_tokens[idx], 'tags' : h_tags[idx]} for idx in range(len(metadata))]
-
         p_encoded_parse = torch.tensor(
-            [output['encoder_final_state']
-             for output in self._predictor.predict_batch_json(p_jsons)]
-            ).to(self._device)
+                [output['encoded_text']
+                        for output in self._predictor.predict_batch_json(p_jsons)]
+                ).to(self._device)
         h_encoded_parse = torch.tensor(
-            [output['encoder_final_state']
-             for output in self._predictor.predict_batch_json(h_jsons)]
-            ).to(self._device)
+                [output['encoded_text']
+                        for output in self._predictor.predict_batch_json(h_jsons)]
+                ).to(self._device)
 
         embedded_premise = self._text_field_embedder(premise)
         embedded_hypothesis = self._text_field_embedder(hypothesis)
[…]

### 2019-03-26 syntactic_entailment/models/syntactic_entailment_v3.py

@@ -8,11 +8,12 @@ from allennlp.data import Vocabulary
 from allennlp.models.model import Model
 from allennlp.modules import FeedForward
 from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
+from allennlp.modules.matrix_attention.legacy_matrix_attention import LegacyMatrixAttention
 from allennlp.nn import InitializerApplicator, RegularizerApplicator
 from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
 from allennlp.training.metrics import CategoricalAccuracy
 
-from syntactic_entailment.modules.matrix_attention.syntactic_matrix_attention import SyntacticMatrixAttention
+from syntactic_entailment.predictors.constituency_parser import SyntacticEntailmentConstituencyParserPredictor
 
 
 @Model.register("syntactic-entailment-v3")
@@ -78,7 +79,7 @@ class SyntacticEntailment(Model):
 
         self._text_field_embedder = text_field_embedder
         self._attend_feedforward = TimeDistributed(attend_feedforward)
-        self._attention = SyntacticMatrixAttention(similarity_function)
+        self._matrix_attention = LegacyMatrixAttention(similarity_function)
         self._compare_feedforward = TimeDistributed(compare_feedforward)
         self._aggregate_feedforward = aggregate_feedforward
         self._premise_encoder = premise_encoder
@@ -86,10 +87,11 @@ class SyntacticEntailment(Model):
 
         self._num_labels = vocab.get_vocab_size(namespace="labels")
 
-        check_dimensions_match(text_field_embedder.get_output_dim(),
-                               attend_feedforward.get_input_dim(),
-                               "text field embedding dim",
-                               "attend feedforward input dim")
+        # this check doesn't work anymore since we attend w/ syntax
+        #check_dimensions_match(text_field_embedder.get_output_dim(),
+        #                       attend_feedforward.get_input_dim(),
+        #                       "text field embedding dim",
+        #                       "attend feedforward input dim")
         check_dimensions_match(aggregate_feedforward.get_output_dim(),
                                self._num_labels,
                                "final output dimension",
@@ -164,13 +166,17 @@ class SyntacticEntailment(Model):
         if self._hypothesis_encoder:
             embedded_hypothesis = self._hypothesis_encoder(embedded_hypothesis, hypothesis_mask)
 
-        projected_premise = self._attend_feedforward(embedded_premise)
[…]

### 2019-03-26 syntactic_entailment/models/syntactic_entailment_v8.py

@@ -1,227 +1,0 @@
-from typing import Dict, Optional, List, Any
-
-import torch
-
-from allennlp.predictors.predictor import Predictor
-from allennlp.common.checks import check_dimensions_match
-from allennlp.data import Vocabulary
-from allennlp.models.model import Model
-from allennlp.modules import FeedForward
-from allennlp.modules import Seq2SeqEncoder, SimilarityFunction, TimeDistributed, TextFieldEmbedder
-from allennlp.modules.matrix_attention.legacy_matrix_attention import LegacyMatrixAttention
-from allennlp.nn import InitializerApplicator, RegularizerApplicator
-from allennlp.nn.util import get_text_field_mask, masked_softmax, weighted_sum
-from allennlp.training.metrics import CategoricalAccuracy
-
-
-@Model.register("syntactic-entailment-v8")
-class SyntacticEntailment(Model):
-    """
-    This ``Model`` implements the Decomposable Attention model described in `"A Decomposable
-    Attention Model for Natural Language Inference"
-    <https://www.semanticscholar.org/paper/A-Decomposable-Attention-Model-for-Natural-Languag-Parikh-T%C3%A4ckstr%C3%B6m/07a9478e87a8304fc3267fa16e83e9f3bbd98b27>`_
-    by Parikh et al., 2016, with some optional enhancements before the decomposable attention
-    actually happens.  Parikh's original model allowed for computing an "intra-sentence" attention
-    before doing the decomposable entailment step.  We generalize this to any
-    :class:`Seq2SeqEncoder` that can be applied to the premise and/or the hypothesis before
-    computing entailment.
-
-    The basic outline of this model is to get an embedded representation of each word in the
-    premise and hypothesis, align words between the two, compare the aligned phrases, and make a
-    final entailment decision based on this aggregated comparison.  Each step in this process uses
-    a feedforward network to modify the representation.
-
-    Parameters
-    ----------
-    vocab : ``Vocabulary``
-    text_field_embedder : ``TextFieldEmbedder``
-        Used to embed the ``premise`` and ``hypothesis`` ``TextFields`` we get as input to the
-        model.
-    attend_feedforward : ``FeedForward``
-        This feedforward network is applied to the encoded sentence representations before the
-        similarity matrix is computed between words in the premise and words in the hypothesis.
-    similarity_function : ``SimilarityFunction``
-        This is the similarity function used when computing the similarity matrix between words in
[…]
